---
title: "DMKN_PhosphoR"
author: "Vahap Canbay"
date: "2024-02-13"
output: pdf_document
---




#Packages
```{r Packages, message=FALSE, warning=FALSE}
  gc()
  load_or_install_packages <- function(packages) {
    if (!requireNamespace("BiocManager", quietly = TRUE)) {
      install.packages("BiocManager")
    }
  
    for (pkg in packages) {
      if (!requireNamespace(pkg, quietly = TRUE)) {
        if (pkg %in% rownames(installed.packages())) {
          warning(pkg, " is not available")
        } else {
          BiocManager::install(pkg, ask = FALSE)
        }
      }
      require(pkg, character.only = TRUE, quietly = TRUE)
    }
  }
  packages <- c("ggplot2", "dplyr", "tidyverse", "tidyr", "ggupset", "corrplot", "ggvenn", "limma", "graphics", "directPA", "reactome.db", "org.Hs.eg.db", "SummarizedExperiment", "PhosR", "calibrate", "ggpubr", "GGally", "network", "annotate", "stats4", "methods", "datasets", "gridExtra", "venn", "UpSetR", "grid", "reshape2", "extrafont", "PerformanceAnalytics", "xts", "zoo", "ClueR", "parallel", "e1071", "lubridate", "forcats", "stringr", "purrr", "readr", "tibble", "GenomicRanges", "GenomeInfoDb", "MatrixGenerics", "matrixStats", "XML", "AnnotationDbi", "IRanges", "S4Vectors", "Biobase", "BiocGenerics", "stats4", "calibrate", "MASS", "svglite", "pheatmap", "ggplotify","doParallel", "enrichplot" ,"clusterProfiler", "ggrepel", "devtools", "volcano3D","edgeR","RColorBrewer","readxl","ggVennDiagram", "ggbeeswarm", "rlang", "xtable")
  load_or_install_packages(packages)
  
  data(PhosphoSitePlus)
  Sys.setenv(LANG = "en")
```


First Import the data table. The data is a quant file from Spectronaut with no localization filter and in long format
#Import
```{r eval=FALSE, include=FALSE}

uniprot.proteome_Human <- read.delim("uniprot-proteome_UP000005640+reviewed_yes.fasta", header=FALSE)



phos_peptides_DMKN_noLOCFilter_Qvalue0_01 = read.delim2("20221127_HRMS1_DIA_DMKN_KO_ENDO_RESCUE_Rstudio_Vcan_report.tsv")

phos_quant_prePerseus_filtered_Qvalue0_01 = phos_peptides_DMKN_noLOCFilter_Qvalue0_01[phos_peptides_DMKN_noLOCFilter_Qvalue0_01$FG.ShapeQualityScore..MS1. > 0.6, ]

write.table(phos_quant_prePerseus_filtered_Qvalue0_01, file = "20221127_HRMS1_DIA_DMKN_KO_ENDO_RESCUE_Rstudio_Vcan_report_PeakShape_prePerseus.tsv", sep = "\t", row.names = FALSE, col.names = TRUE, quote=FALSE)

phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4 <- read_delim("20221127_HRMS1_DIA_DMKN_KO_ENDO_RESCUE_Rstudio_Vcan_report_PeakShape_PeptideCollapse.tsv", 
    delim = "\t", escape_double = FALSE, 
    comment = "#", trim_ws = TRUE,show_col_types = FALSE)
final_phos_locFILTER_shapeFILTER = phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4

Keratinocyte_Phosphoproteome_2024 = phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4

global_PG_QUANT_V2<- read.csv2("20221215_HRMS1_DIA_DMKN_KO_ENDO_RESCUE_global_Report.csv")
```

reformat_fasta_df <- function(fasta_df) {
  reformatted_lines <- c()
  current_sequence <- ""
  
  for (i in 1:nrow(fasta_df)) {
    line <- as.character(fasta_df[i, 1])
    if (!is.na(line)) {
      if (startsWith(line, ">")) {
        if (nchar(current_sequence) > 0) {
          reformatted_lines <- c(reformatted_lines, current_sequence)
          current_sequence <- ""
        }
        reformatted_lines <- c(reformatted_lines, line)
      } else {
        current_sequence <- paste0(current_sequence, line)
      }
    }
  }} 
  

fasta_to_named_list <- function(fasta_lines) {
  named_list <- list()
  current_header <- ""

  for (line in fasta_lines) {
    if (startsWith(line, ">")) {
      uniprot_id <- sub("^.*\\|(.+?)\\|.*$", "\\1", line)
      gene_id <- sub("^.*GN=(\\S+).*?$", "\\1", line)
      current_header <- paste(uniprot_id, gene_id, sep = ";")
    } else {
      named_list[[current_header]] <- line
    }
  }

  return(named_list)
}

extract_flanking_seq <- function(named_FASTA, rownames_ppe) {
  updated_rownames <- c()

  for (rowname in rownames_ppe) {
    split_name <- strsplit(rowname, ";")[[1]]
    
    # Remove the first and third terms if there are more than 4 terms
    if (length(split_name) > 4) {
      split_name <- split_name[-c(1, 3)]
    }
    # Remove any terms after the third semicolon
    split_name <- split_name[1:4]
    
    rowname <- remove_terms_after_third_semicolon(rowname)
    gene_id <- split_name[2]
    position <- as.integer(gsub("\\D", "", split_name[3]))
    matches <- grep(paste0(".*;", gene_id, "$"), names(named_FASTA), value = TRUE)

    if (length(matches) > 0) {
      protein_seq <- named_FASTA[matches[1]]

      # Correct the position indexing
      start <- max(1, position - 7)
      stop <- min(nchar(protein_seq), position + 7)

      flanking_seq <- substr(protein_seq, start, stop)
      new_name <- paste(split_name[1], split_name[2], split_name[3], flanking_seq, sep = ";")
      updated_rownames <- c(updated_rownames, new_name)
    } else {
      updated_rownames <- c(updated_rownames, rowname)
    }
  }

  return(updated_rownames)
}

remove_terms_after_third_semicolon <- function(rowname) {
  split_name <- strsplit(rowname, ";")[[1]]
  new_name <- paste(split_name[1:4], collapse = ";")
  return(new_name)
}


#Functions
```{r message=FALSE, warning=FALSE, include=FALSE}
generate_volcano_plot <- function(df) {
  # Extract the name of the data frame
  df_name <- deparse(substitute(df))

  # Define the title based on the name of the data frame
  title <- switch(df_name,
                  "results_df_CS_Rescue_sorted" = "DMKN\U03B1\U03B2-/- Rescue vs DMKN\U03B1\U03B2-/- Endogenous",
                  "results_df_CS_Endogenous_sorted" = "WT vs DMKN\U03B1\U03B2-/-",
                  "results_df_DTU_Rescue_sorted" = "DMKN\U03B2\U03B3-/- Rescue vs DMKN\U03B2\U03B3-/- Endogenous",
                  "results_df_DTU_Endogenous_sorted" = "WT vs DMKN\U03B2\U03B3-/-",
                  "results_df_WT_Endogenous_sorted" = "WT Rescue vs WT endogenous",
                  "Unknown data frame")

    log2FC_threshold = log2(1.5)
    point_color = "black"
    hl.col.down = "blue"
    hl.col.up = "red"
  # Generate the volcano plot
  volcano_plot <- ggplot(df, aes(x = diff_coeff, y = -log10(phos_pvals_significant), label = phos_ID)) +
    geom_vline(xintercept = log2FC_threshold, linetype = 3) + geom_vline(xintercept = -log2FC_threshold, linetype = 3) +
    geom_point(aes(color = ifelse(diff_coeff >= log2FC_threshold, hl.col.up, ifelse(diff_coeff <= -log2FC_threshold, hl.col.down, point_color)))) +
    scale_alpha_identity(guide=FALSE) +
    scale_color_identity(guide = FALSE) +
    ylim(0, 3) + xlim(-3, 3) +
    labs(x = "Difference in Coefficients (Log2 fold change)", y = "-Log10(limma moderated p value)") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = 'transparent'),
          panel.border = element_rect(colour = "black", fill = NA, size = 1),
          text = element_text(size = 12) ,
          legend.position = "none") +
    geom_label_repel(aes(label = phos_ID, fill = ifelse(startsWith(phos_ID, "CTNND1"), "orange", "black")), 
                 nudge_y = 0.25, nudge_x = .15, segment.curvature = -1e-20,
                 arrow = arrow(length = unit(0.015, "npc")),
                 box.padding   = 0.35, max.overlaps = Inf,
                 point.padding = 0.5,
                 segment.color = 'grey50', size  = 2)+
    ggtitle(paste("Difference in Log2 Fold Change of \nPhosphorylated Peptide and Protein \nAbundance", title))

  return(volcano_plot)
}


volcano_plot_ggplot_multicol_overlay <- function(fit, coefs = 1L, style = "p-value", 
                                                 highlight = 0L, names = rownames(fit$coef), 
                                                 hl.col.up = "red", hl.col.down = "blue", 
                                                 point_color = "darkgray", xlab = "Log2 Fold Change",
                                                 ylab = NULL, pch = 16, cex = 0.5, 
                                                 p_value_threshold = 0.05, log2FC_threshold = 1, ...) {
  if (!is(fit, "MArrayLM")) 
    stop("fit must be an MArrayLM")
  
  style <- match.arg(tolower(style), c("p-value", "b-statistic"))
  
  data_list <- list()
  
  for (coef in coefs) {
    x <- as.matrix(fit$coef)[, coef]
    
    if (style == "p-value") {
      if (is.null(fit$p.value)) 
        stop("No p-values found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$p.value)[, coef]
      y <- -log10(y)
      if (is.null(ylab)) 
        ylab = "-log10(limma moderated p value)"
    }
    else {
      if (is.null(fit$lods)) 
        stop("No B-statistics found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$lods)[, coef]
      if (is.null(ylab)) 
        ylab = "Log Odds of Differential Expression"
    }
    
    if (is.null(names)) {
      names <- 1:length(x)
    }
    
    coef_data <- data.frame(x = x, y = y, names = names, coef = factor(coef))
    data_list[[as.character(coef)]] <- coef_data
  }
  
    # ... (rest of your function) ...
  
  data <- do.call(rbind, data_list)
  
  p <- ggplot(data, aes(x, y)) + labs(x = xlab, y = ylab)
  
  # Manually specify each comparison
  coef1_data <- data[data$coef == coefs[1],]
  coef2_data <- data[data$coef == coefs[2],]
  
  # Determine labels based on the coefficients provided
labels <- c()
for (coef in coefs) {
    coef_name <- colnames(fit$coef)[coef]
    labels <- c(labels, paste0(coef_name, " up"))
}
labels <- c(labels, "Not significant")
for (coef in coefs) {
    coef_name <- colnames(fit$coef)[coef]
    labels <- c(labels, paste0(coef_name, " down"))
}
  
  
  
  p <- p + geom_point(data = coef1_data, aes(color = ifelse(x >= log2FC_threshold, "blue", 
                                                            ifelse(x <= -log2FC_threshold, "darkred",
                                                                   point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >=-log10(p_value_threshold), 1, 0.01)), 
                      shape = pch, size = cex)
  p <- p + geom_point(data = coef2_data, aes(color = ifelse(x >= log2FC_threshold, "cyan", 
                                                            ifelse(x <= -log2FC_threshold, "pink", 
                                                                   point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >= -log10(p_value_threshold), 1, 0.01)), 
                      shape = 18, size = cex)
  # Getting 2 colors from each palette
red_spectrum <- brewer.pal(9, "YlOrRd")[c(8, 5)]  # Choosing darker and somewhat lighter reds
blue_spectrum <- brewer.pal(9, "GnBu")[c(8, 5)]  # Choosing darker and somewhat lighter blues


  # ... (rest of your function) ...
  color_order <- c(red_spectrum[1], red_spectrum[2], "darkgrey", blue_spectrum[1], blue_spectrum[2])
  shape_order  <- c("pch", 18, "pch", "pch", 18)
  p = p + scale_alpha_identity(guide="none") + scale_color_manual(values = color_order, labels =labels,  name = "Comparisons")  + scale_shape_manual(values = shape_order, labels = labels) +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_rect(fill='transparent'),
          panel.border = element_rect(colour = "black", fill = NA, size = 1),legend.text=element_text(size=10),
          text = element_text(size = 12),legend.position="bottom") + 
    guides(colour = guide_legend(ncol = 2,title.position="top", title.hjust = 0.5)) + ggtitle("Comparison of phosphorylation \nsite abundances") 
nudge_directions <- c(0.3, -0.3)  # replace these with your preferred values


  print(p)
  invisible()
  return(p)
}

volcano_plot_ggplot_multicol_overlay_CS <- function(fit, coefs = 1L, style = "p-value", 
                                                 highlight = 0L, names = rownames(fit$coef), 
                                                 hl.col.up = "red", hl.col.down = "blue", 
                                                 point_color = "darkgray", xlab = "Log2 Fold Change",
                                                 ylab = NULL, pch = 16, cex = 0.5, 
                                                 p_value_threshold = 0.05, log2FC_threshold = 1, ...) {
  if (!is(fit, "MArrayLM")) 
    stop("fit must be an MArrayLM")
  
  style <- match.arg(tolower(style), c("p-value", "b-statistic"))
  
  data_list <- list()
  
  for (coef in coefs) {
    x <- as.matrix(fit$coef)[, coef]
    
    if (style == "p-value") {
      if (is.null(fit$p.value)) 
        stop("No p-values found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$p.value)[, coef]
      y <- -log10(y)
      if (is.null(ylab)) 
        ylab = "-log10(limma moderated p value)"
    }
    else {
      if (is.null(fit$lods)) 
        stop("No B-statistics found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$lods)[, coef]
      if (is.null(ylab)) 
        ylab = "Log Odds of Differential Expression"
    }
    
    if (is.null(names)) {
      names <- 1:length(x)
    }
    
    coef_data <- data.frame(x = x, y = y, names = names, coef = factor(coef))
    data_list[[as.character(coef)]] <- coef_data
  }
  
    # ... (rest of your function) ...
  
  data <- do.call(rbind, data_list)
  
  p <- ggplot(data, aes(x, y)) + labs(x = xlab, y = ylab)
  
  # Manually specify each comparison
  coef1_data <- data[data$coef == coefs[1],]
  coef2_data <- data[data$coef == coefs[2],]
  
  # Determine labels based on the coefficients provided
labels <- c()
for (coef in coefs) {
    coef_name <- colnames(fit$coef)[coef]
    labels <- c(labels, paste0(coef_name, " up"))
}
labels <- c(labels, "Not significant")
for (coef in coefs) {
    coef_name <- colnames(fit$coef)[coef]
    labels <- c(labels, paste0(coef_name, " down"))
}
  
  
  
  p <- p + geom_point(data = coef1_data, aes(color = ifelse(x >= log2FC_threshold, "blue", 
                                                            ifelse(x <= -log2FC_threshold, "darkred",
                                                                   point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >=-log10(p_value_threshold), 1, 0.01)), 
                      shape = pch, size = cex)
  p <- p + geom_point(data = coef2_data, aes(color = ifelse(x >= log2FC_threshold, "cyan", 
                                                            ifelse(x <= -log2FC_threshold, "pink", 
                                                                   point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >= -log10(p_value_threshold), 1, 0.01)), 
                      shape = 18, size = cex)
  # Getting 2 colors from each palette
red_spectrum <- brewer.pal(9, "YlOrRd")[c(8, 5)]  # Choosing darker and somewhat lighter reds
blue_spectrum <- brewer.pal(9, "GnBu")[c(8, 5)]  # Choosing darker and somewhat lighter blues


  # ... (rest of your function) ...
  color_order <- c(red_spectrum[1],"darkgrey", blue_spectrum[1])
  shape_order  <- c("pch", "pch", "pch")
  p = p + scale_alpha_identity(guide="none") + scale_color_manual(values = color_order, labels =labels,  name = "Comparisons")  + scale_shape_manual(values = shape_order, labels = labels) +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_rect(fill='transparent'),
          panel.border = element_rect(colour = "black", fill = NA, size = 1),legend.text=element_text(size=10),
          text = element_text(size = 12),legend.position="bottom") + 
    guides(colour = guide_legend(ncol = 2,title.position="top", title.hjust = 0.5)) + ggtitle("Comparison of endogenous phosphorylation site \nabundances") 
nudge_directions <- c(0.3, -0.3)  # replace these with your preferred values


  print(p)
  invisible()
  return(p)
}

volcano_plot_ggplot_multicol_overlay_DTU <- function(fit, coefs = 1L, style = "p-value", 
                                                 highlight = 0L, names = rownames(fit$coef), 
                                                 hl.col.up = "red", hl.col.down = "blue", 
                                                 point_color = "darkgray", xlab = "Log2 Fold Change",
                                                 ylab = NULL, pch = 16, cex = 0.5, 
                                                 p_value_threshold = 0.05, log2FC_threshold = 1, ...) {
  if (!is(fit, "MArrayLM")) 
    stop("fit must be an MArrayLM")
  
  style <- match.arg(tolower(style), c("p-value", "b-statistic"))
  
  data_list <- list()
  
  for (coef in coefs) {
    x <- as.matrix(fit$coef)[, coef]
    
    if (style == "p-value") {
      if (is.null(fit$p.value)) 
        stop("No p-values found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$p.value)[, coef]
      y <- -log10(y)
      if (is.null(ylab)) 
        ylab = "-log10(limma moderated p value)"
    }
    else {
      if (is.null(fit$lods)) 
        stop("No B-statistics found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$lods)[, coef]
      if (is.null(ylab)) 
        ylab = "Log Odds of Differential Expression"
    }
    
    if (is.null(names)) {
      names <- 1:length(x)
    }
    
    coef_data <- data.frame(x = x, y = y, names = names, coef = factor(coef))
    data_list[[as.character(coef)]] <- coef_data
  }
  
    # ... (rest of your function) ...
  
  data <- do.call(rbind, data_list)
  
  p <- ggplot(data, aes(x, y)) + labs(x = xlab, y = ylab)
  
  # Manually specify each comparison
  coef1_data <- data[data$coef == coefs[1],]
  coef2_data <- data[data$coef == coefs[2],]
  
  # Determine labels based on the coefficients provided
labels <- c()
for (coef in coefs) {
    coef_name <- colnames(fit$coef)[coef]
    labels <- c(labels, paste0(coef_name, " up"))
}
labels <- c(labels, "Not significant")
for (coef in coefs) {
    coef_name <- colnames(fit$coef)[coef]
    labels <- c(labels, paste0(coef_name, " down"))
}
  
  
  
  p <- p + geom_point(data = coef1_data, aes(color = ifelse(x >= log2FC_threshold, "blue", 
                                                            ifelse(x <= -log2FC_threshold, "darkred",
                                                                   point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >=-log10(p_value_threshold), 1, 0.01)), 
                      shape = pch, size = cex)
  p <- p + geom_point(data = coef2_data, aes(color = ifelse(x >= log2FC_threshold, "cyan", 
                                                            ifelse(x <= -log2FC_threshold, "pink", 
                                                                   point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >= -log10(p_value_threshold), 1, 0.01)), 
                      shape = 18, size = cex)
  # Getting 2 colors from each palette
red_spectrum <- brewer.pal(9, "YlOrRd")[c(8, 5)]  # Choosing darker and somewhat lighter reds
blue_spectrum <- brewer.pal(9, "GnBu")[c(8, 5)]  # Choosing darker and somewhat lighter blues


  # ... (rest of your function) ...
  color_order <- c(red_spectrum[2], "darkgrey", blue_spectrum[2])
  shape_order  <- c(18, "pch", 18)
  p = p + scale_alpha_identity(guide="none") + scale_color_manual(values = color_order, labels =labels,  name = "Comparisons")  + scale_shape_manual(values = shape_order, labels = labels) +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_rect(fill='transparent'),
          panel.border = element_rect(colour = "black", fill = NA, size = 1),legend.text=element_text(size=10),
          text = element_text(size = 12),legend.position="bottom") + 
    guides(colour = guide_legend(ncol = 2,title.position="top", title.hjust = 0.5)) + ggtitle("Comparison of phosphorylation \nsite abundances") 
nudge_directions <- c(0.3, -0.3)  # replace these with your preferred values


  print(p)
  invisible()
  return(p)
}
volcano_plot_ggplot_multicol <- function(fit, coefs = 1L, style = "p-value", 
                                         highlight = 0L, names = rownames(fit$coef), 
                                         hl.col.up = "red", hl.col.down = "blue", 
                                         point_color = "darkgray", xlab = "Log2 Fold Change",
                                         ylab = NULL, pch = 16, cex = 0.5, facet = "grid", 
                                         p_value_threshold = 0.05, log2FC_threshold = 1, ...) {
  if (!is(fit, "MArrayLM")) 
    stop("fit must be an MArrayLM")
  
  style <- match.arg(tolower(style), c("p-value", "b-statistic"))
  
  data_list <- list()
  
  for (coef in coefs) {
    x <- as.matrix(fit$coef)[, coef]
    
    if (style == "p-value") {
      if (is.null(fit$p.value)) 
        stop("No p-values found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$p.value)[, coef]
      y <- -log10(y)
      if (is.null(ylab)) 
        ylab = "-log10(limma moderated p value)"
    }
    else {
      if (is.null(fit$lods)) 
        stop("No B-statistics found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$lods)[, coef]
      if (is.null(ylab)) 
        ylab = "Log Odds of Differential Expression"
    }
    
    if (is.null(names)) {
      names <- 1:length(x)
    }
    
    coef_data <- data.frame(x = x, y = y, names = names, coef = factor(coef))
    data_list[[as.character(coef)]] <- coef_data
  }
  
  data <- do.call(rbind, data_list)
  
     p <- ggplot(data, aes(x, y)) + 
    geom_point(aes(color = ifelse(x >= log2FC_threshold, hl.col.up, ifelse(x <= -log2FC_threshold, hl.col.down, point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >= -log10(p_value_threshold), 1, 0.01)),
               shape = pch, size = cex) +
    scale_color_identity(guide = FALSE) + scale_alpha_identity(guide=FALSE) +
    #theme_classic() + 
    labs(x = xlab, y = ylab) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_rect(fill='transparent'),
          panel.border = element_rect(colour = "black", fill = NA, size = 1),
          text = element_text(size = 12))

  # ... (rest of the function remains the same) ...

  if (highlight > 0) {
    for (coef in coefs) {
      coef_data <- data[data$coef == coef,]
      o <- order(coef_data$y, decreasing = TRUE)
      i <- o[1:highlight]
      p <- p + ggrepel::geom_text_repel(data = coef_data[i,], aes(label = names, 
                                                                  color = ifelse(x >= log2FC_threshold, hl.col.up, ifelse(x <= -log2FC_threshold, hl.col.down, point_color)),
                                                                  alpha = ifelse(abs(x) >= log2FC_threshold & y >= -log10(p_value_threshold), 1, 0.5)),
                                        size = 2, nudge_y = 0.3)
    }
  }
panel_labels <- vector(mode = "character", length = length(coefs))
  names(panel_labels) <- as.character(coefs)

  for (i in seq_along(coefs)) {
    panel_labels[as.character(coefs[i])] <- colnames(fit$coef)[coefs[i]]
  }

  
    p <- p + facet_wrap(. ~ coef, ncol =2,labeller = as_labeller(panel_labels))
  
     
  print(p)
  invisible()
  return(p)
}

volcano_plot_ggplot_multicol_phosSites <- function(fit, coefs = 1L, style = "p-value", 
                                         highlight = 20, names = rownames(fit$coef), 
                                         hl.col.up = "red", hl.col.down = "blue", 
                                         point_color = "black", xlab = "Log2 (WT vs KO) ratio",
                                         ylab = NULL, pch = 16, cex = 0.5, facet = "grid", 
                                         p_value_threshold = 0.05, log2FC_threshold = 1,title, ...) {
  if (!is(fit, "MArrayLM")) 
    stop("fit must be an MArrayLM")
  
  style <- match.arg(tolower(style), c("p-value", "b-statistic"))
  
  data_list <- list()
  
  for (coef in coefs) {
    x <- as.matrix(fit$coef)[, coef]
    
    if (style == "p-value") {
      if (is.null(fit$p.value)) 
        stop("No p-values found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$p.value)[, coef]
      y <- -log10(y)
      if (is.null(ylab)) 
        ylab = "-log10(limma moderated p value)"
    }
    else {
      if (is.null(fit$lods)) 
        stop("No B-statistics found in linear model fit object. Please run eBayes.")
      y <- as.matrix(fit$lods)[, coef]
      if (is.null(ylab)) 
        ylab = "Log Odds of Differential Expression"
    }
    
    if (is.null(names)) {
      names <- 1:length(x)
    }
    
    coef_data <- data.frame(x = x, y = y, names = names, coef = factor(coef))
    data_list[[as.character(coef)]] <- coef_data
  }
  
  data <- do.call(rbind, data_list)
  
     p <- ggplot(data, aes(x, y,label=phos_Site       )) + geom_vline(xintercept=log2(1.5),linetype=3) +
    geom_point(aes(color = ifelse(x >= log2FC_threshold, hl.col.up, ifelse(x <= -log2FC_threshold, hl.col.down, point_color)), alpha = ifelse(abs(x) >= log2FC_threshold & y >= -log10(p_value_threshold), 1, 1)),
               shape = pch, size = cex) +
    scale_color_identity(guide = FALSE) + scale_alpha_identity(guide=FALSE) + ylim(0,5) + xlim(-1.0,2)+
    #theme_classic() + 
    labs(x = xlab, y = ylab) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_rect(fill='transparent'),
          panel.border = element_rect(colour = "black", fill = NA, size = 1),
          text = element_text(size = 12))

  # ... (rest of the function remains the same) ...

    p <- p + geom_label_repel(aes(label = phos_Site), nudge_y = 0.25,nudge_x = .15,segment.curvature = -1e-20,
    arrow = arrow(length = unit(0.015, "npc")),
                  box.padding   = 0.35, max.overlaps = Inf,
                  point.padding = 0.5,
                  segment.color = 'grey50', size  = 2) + ggtitle(title)
    
  #print(p)
  invisible()
  return(p)
}

combine_GOplots_with_shared_legend <- function(plot1, plot2) {
  # Remove the legend from both plots
  plot1_no_legend <- plot1 + theme(legend.position = "none")
  plot2_no_legend <- plot2 + theme(legend.position = "none")

  # Combine the plots using ggarrange without legends
  combined_plots <- ggarrange(plot1_no_legend, plot2_no_legend, ncol = 2)

  # Extract the legend from the first plot
  plot1_legend <- get_legend(plot1)
  plot2_legend <- get_legend(plot2)

   # Get the number of legend elements in both plots
  n_legend_elements_plot1 <- max(plot1$data$n)
  n_legend_elements_plot2 <- max(plot2$data$n)
    # Choose the legend with more elements
  selected_legend <- if (n_legend_elements_plot1 >= n_legend_elements_plot2) plot1_legend else plot2_legend

# Combine the plots and the shared legend using the cowplot package
  final_plot <- cowplot::plot_grid(combined_plots, selected_legend, ncol = 1, rel_heights = c(1, 0.4))

  return(final_plot)
}

combine_plots_with_shared_legend <- function(plot1, plot2) {
  # Remove the legend from both plots
  plot1_no_legend <- plot1 + theme(legend.position = "none")
  plot2_no_legend <- plot2 + theme(legend.position = "none")

  # Combine the plots using ggarrange without legends
  combined_plots <- ggarrange(plot1_no_legend, plot2_no_legend, ncol = 2)

  # Extract the legend from the first plot
  plot1_legend <- get_legend(plot1)
  plot2_legend <- get_legend(plot2)

   # Get the number of legend elements in both plots
  n_legend_elements_plot1 <- max(plot1$data$n)
  n_legend_elements_plot2 <- max(plot2$data$n)
    # Choose the legend with more elements
  selected_legend <- if (n_legend_elements_plot1 >= n_legend_elements_plot2) plot1_legend else plot2_legend

# Combine the plots and the shared legend using the cowplot package
  final_plot <- cowplot::plot_grid(combined_plots, selected_legend, ncol = 1, rel_heights = c(0.9, 0.1))

  return(final_plot)
}
process_signalomes_results <- function(Signalomes_results_DTU_Up) {

  # Convert the character vector into a data frame
  signalomes_results_DTU_Up_df <- data.frame(gene_and_phos_site = names(Signalomes_results_DTU_Up$proteinModules),
                                             module_number = as.numeric(Signalomes_results_DTU_Up$proteinModules),
                                             stringsAsFactors = FALSE)
  
  # Create a list to store the new data frames
  module_dfs <- list()
  
  # Iterate through the unique module numbers and create a data frame for each module
  for (module_number in unique(signalomes_results_DTU_Up_df$module_number)) {
    module_subset <- signalomes_results_DTU_Up_df[signalomes_results_DTU_Up_df$module_number == module_number, "gene_and_phos_site"]
    module_dfs[[paste0("module_", module_number)]] <- data.frame(gene_and_phos_site = module_subset)
  }
  
  convert_to_entrez <- function(gene_and_phos_site) {
    # Extract gene names
    gene_names <- gsub(" .*", "", gene_and_phos_site)
  
    # Convert gene names to Entrez IDs
    entrez_ids <- mapIds(org.Hs.eg.db,
                         keys = gene_names,
                         column = "ENTREZID",
                         keytype = "SYMBOL",
                         multiVals = "first")
  
    # Remove NA values
    entrez_ids <- entrez_ids[!is.na(entrez_ids)]
  
    return(entrez_ids)
}
  
  # Create a new list to store the Entrez IDs as character vectors
  module_entrez_ids_chr <- list()
  
  # Iterate through each module and convert gene names to Entrez IDs
  for (module_name in names(module_dfs)) {
    module_entrez_ids_chr[[module_name]] <- as.character(convert_to_entrez(module_dfs[[module_name]]$gene_and_phos_site))
  }
  
  return(module_entrez_ids_chr)
}
#Remove irregular sequences
short_fourth_term <- function(row_name) {
  terms <- unlist(strsplit(row_name, ";"))
  if (length(terms) >= 4) {
    return (nchar(terms[4]) < 4)
  }
  return (FALSE)
}
remove_nonunique_rownames_matrix <- function(mat) {
  # Convert the matrix to a data frame
  df <- as.data.frame(mat)
  
  # Create a new column 'rownames' with the current row names
  df$rownames <- rownames(mat)
  
  # Count the occurrences of each row name
  rowname_counts <- table(df$rownames)
  
  # Find the row names that occur only once
  unique_rownames <- names(rowname_counts[rowname_counts == 1])
  
  # Keep only the rows with unique row names
  df_unique <- df[df$rownames %in% unique_rownames, ]
  
  # Reset the row names
  rownames(df_unique) <- df_unique$rownames
  
  # Remove the 'rownames' column
  df_unique$rownames <- NULL
  
  # Convert the data frame back to a matrix
  mat_unique <- as.matrix(df_unique)
  
  return(mat_unique)
}

kinaseSubstrateHeatmap_modified = function (phosScoringMatrices, top = 3, printPlot = NULL, filePath = "./kinaseSubstrateHeatmap.pdf", 
    width = 10, height = 10) 
{
    utils::data("KinaseFamily", envir = environment())
    sites <- c()
    for (i in seq_len(ncol(phosScoringMatrices$combinedScoreMatrix))) {
        sites <- union(sites, names(sort(phosScoringMatrices$combinedScoreMatrix[, 
            i], decreasing = TRUE)[seq_len(top)]))
    }
    o <- intersect(colnames(phosScoringMatrices$combinedScoreMatrix), 
        rownames(KinaseFamily))
    annotation_col = data.frame(group = KinaseFamily[o, "kinase_group"], 
        family = KinaseFamily[o, "kinase_family"])
    rownames(annotation_col) <- o
    if (is.null(printPlot) == TRUE) {
      
        pheatmap(phosScoringMatrices$combinedScoreMatrix[sites, 
            ], annotation_col = annotation_col, cluster_rows = TRUE, 
            cluster_cols = TRUE, fontsize = 7)
      
    }
    else {
        pdf(file = filePath, width = width, height = height)
      
        pheatmap(phosScoringMatrices$combinedScoreMatrix[sites, 
            ], annotation_col = annotation_col, cluster_rows = TRUE, 
            cluster_cols = TRUE, fontsize = 7)
        
        dev.off()
    }
}
siteAnnotate_modified <- function(site, phosScoringMatrices, predMatrix) {
  od <- order(predMatrix[site, ], decreasing = FALSE)
  kinases <- colnames(predMatrix)[od]
  
  par(mfrow = c(1, 4), mar = c(1, 5, 5, 1))
  
  barplot(predMatrix[site, kinases], las = 1, xlab = "Prediction score", 
          col = "red3", main = "Prediction score", xlim = c(0, 1), horiz = TRUE, xaxt= "n")
  axis(3)
  barplot(phosScoringMatrices$combinedScoreMatrix[site, kinases], 
          las = 1, main = "Combined score", col = "orange2", xlim = c(0, 1), horiz = TRUE,xaxt= "n")
   axis(3)
  barplot(phosScoringMatrices$motifScoreMatrix[site, kinases], 
          las = 1, main = "Motif score", col = "green4", xlim = c(0, 1), horiz = TRUE,xaxt= "n")
   axis(3)
  barplot(phosScoringMatrices$profileScoreMatrix[site, kinases], 
          las = 1, main = "Profile score", col = "lightblue3", 
          xlim = c(0, 1), horiz = TRUE,xaxt= "n")
   axis(3)
  mtext(paste("Site =", site),                   # Add main title
      side = 3,
      line = - 2,
      outer = TRUE)
}

siteAnnotate_modified_ggplot <- function(site, phosScoringMatrices, predMatrix) {
  od <- order(predMatrix[site, ], decreasing = FALSE)
  kinases <- colnames(predMatrix)[od]
  
  plot_data <- list(predMatrix[site, kinases], phosScoringMatrices$combinedScoreMatrix[site, kinases],
                   phosScoringMatrices$motifScoreMatrix[site, kinases], phosScoringMatrices$profileScoreMatrix[site, kinases])
  plot_types <- c("Prediction score", "Combined score", "Motif score", "Profile score")
  plot_colors <- c("red3", "orange2", "green4", "lightblue3")
  
  plots <- list()
  
  for (i in 1:4) {
    df <- data.frame(Kinase = factor(kinases, levels = kinases), Value = plot_data[[i]])
    
    p <- ggplot(df, aes(x = Kinase, y = Value, fill = factor(plot_types[i]))) +
      geom_col() +
      coord_flip() +
      scale_fill_manual(values = plot_colors[i], guide = "none") +
      theme_classic() +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_text(size = 7),
            axis.title.x = element_text(size = 0),
            plot.title = element_text(hjust = 0.5, size = 8),
            axis.text.x.top = element_text(angle = 45, hjust = 1)) +
      labs(title = plot_types[i], x = NULL) +
      scale_x_discrete(position = "top") +
      scale_y_continuous(expand = expansion(mult = c(0.1, 0)), limits = c(0, 1),breaks = c(0,1))
    
    plots[[i]] <- p
  }
  title1=text_grob(paste(site), size = 9, face = "bold")   #### this worked for me

  grid.arrange(grobs = plots, ncol = 4, top = title1)
}


plotSignalomeMap_modified <- function(signalomes, color,module_colors, max_percent = 100,size =10) {
    df <- stack(signalomes$kinaseSubstrates)
    modules <- signalomes$proteinModule
    names(modules) <- unlist(lapply(strsplit(as.character(names(signalomes$proteinModules)), ";"), "[[", 1))
    df$cluster <- modules[df$values]
    df_balloon <- df
    df_balloon <- na.omit(df_balloon) %>% dplyr::count(.data$cluster, .data$ind)
    df_balloon$ind <- as.factor(df_balloon$ind)
    df_balloon$cluster <- as.factor(df_balloon$cluster)
    df_balloon <- tidyr::spread(df_balloon, .data$ind, .data$n)[, -1]
    df_balloon[is.na(df_balloon)] <- 0
    df_balloon <- do.call(rbind, lapply(seq(nrow(df_balloon)), function(x) {
        res <- unlist(lapply(df_balloon[x, ], function(y) y/sum(df_balloon[x, ]) * 100))
    }))
    df_balloon <- reshape2::melt(as.matrix(df_balloon))
    colnames(df_balloon) <- c("cluster", "ind", "n")
    df_balloon <- df_balloon[df_balloon$n > 0, ]
    
     # Normalize the n column based on the max_percent value
  max_percentage <- max(df_balloon$n)
  normalized_n <- (df_balloon$n / max_percentage) * max_percent
  df_balloon$normalized_n <- normalized_n
  
    # Function to find the last balloon for each group
last_balloon_y <- function(group_data) {
  max(group_data$y[group_data$x == max(group_data$x)])
}

# Add a new column to the dataframe containing the last balloon's y value for each group
df_balloon$last_y <- sapply(unique(df_balloon$cluster), function(cluster) {
  last_balloon_y(df_balloon[df_balloon$cluster == cluster, ])
})[df_balloon$cluster]


# Function to find the first balloon for each group
first_balloon_y <- function(group_data) {
  min(group_data$y[group_data$x == min(group_data$x)])
}

# Add a new column to the dataframe containing the first balloon's y value for each group
df_balloon$first_y <- sapply(unique(df_balloon$cluster), function(cluster) {
  first_balloon_y(df_balloon[df_balloon$cluster == cluster, ])
})[df_balloon$cluster]  

    g <- ggplot2::ggplot(df_balloon, aes(y = .data$ind, x = .data$cluster)) + 
      
        
         #geom_text(aes(label = .data$cluster, x = .data$cluster, y = 0), angle = 90, hjust = 1, size = 3) +  # Show x-axis labels using geom_text
         
        theme_classic() + 
        theme(legend.position = "bottom", legend.direction = "horizontal", legend.title = element_text(angle = 0),
              plot.margin = margin(, 0.5, , , "cm"),aspect.ratio = 1,
              axis.line = element_blank(), 
              axis.title = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(),
              axis.text.y = element_text(size = 14),
              panel.grid.major.x = element_blank(), 
              panel.grid.minor.x = element_blank()) +
        guides(col = FALSE)  # Remove the legend for the kinases
    # Add rectangles and text labels for module names on the x-axis
    
    
    g <- g + geom_line(aes(group = .data$cluster, col = .data$ind), size = 0.5, linetype = "solid", color = "grey") +  # Connect the balloons within the horizontal line
      geom_segment(data = df_balloon, aes(x = .data$cluster, xend = .data$cluster, y = .data$first_y, yend = .data$last_y, col = .data$ind), size = 0.5, linetype = "solid", show.legend = FALSE, color = "grey") 
    
    rectangle_height <- 30
# Add rectangles for module names on the x-axis
    for (i in unique(df_balloon$cluster)) {
    g <- g + annotate("rect", xmin = as.numeric(i) - 0.45, xmax = as.numeric(i) + 0.45, ymin = -1.5, ymax = 0, alpha = 0.7, fill = module_colors[i]) + annotate("text", x = i, y = -0.025 * rectangle_height, label = i, size = 4, fontface = "bold")
}
g= g + scale_color_manual(values = color) +
    scale_size_continuous(name = "% of phosphosites regulated by a kinase", range = c(1, size),
                          guide = guide_legend(title.position = "top", title.hjust = 0.5),
                          limits = c(0, max_percent))
    g = g + geom_point(aes(col = .data$ind, size = .data$normalized_n))
  
     #Set the limits using the y_axis_limits argument
  #g <- g + scale_y_discrete(limits = y_axis_limits)
# Use geom_segment() to draw lines from the x-axis to the last balloon for each group
#g <- g + 
    g
}

plot_kinase_activity_NoSerum <- function(input_data, group,title) {
  if (group == "DTU") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("WT_NoSerum|DTU", colnames(input_data))]
    label <- "DMKN \U03B2\U03B3-/-"
  } else if (group == "CS") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("WT_NoSerum|CS", colnames(input_data))]
    label <- "DMKN \U03B1\U03B2-/-"
  } else {
    stop("Invalid group. Please specify either 'DTU' or 'CS'")
  }
  
  long_data <- melt(filtered_data, variable.name = "Condition", value.name = "Score")
  
  long_data$Genotype <- ifelse(str_detect(long_data$Var2, group), label, "WT")
  long_data$Treatment <- ifelse(str_detect(long_data$Var2, "Treated"), "Treated", "Control")
  long_data$Genotype_Treatment <- paste(long_data$Genotype, long_data$Treatment, sep = " ")
  
   # Define the list of comparisons based on the input group
  if (group == "DTU") {
    my_comparisons <- list(c("WT Control", "WT Treated"),
                           c("DMKN \U03B2\U03B3-/- Control", "DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control","DMKN \U03B2\U03B3-/- Control"),
                           c("WT Treated","DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control", "DMKN \U03B2\U03B3-/- Treated")
                           )
        
    long_data$Genotype_Treatment <- factor(long_data$Genotype_Treatment,
                                       levels = c("WT Control", "WT Treated",
                                                  "DMKN \U03B2\U03B3-/- Control", 
                                                  "DMKN \U03B2\U03B3-/- Treated"))
  } else if (group == "CS") {
    my_comparisons <- list(c("WT Control", "WT Treated"),
                           c("DMKN \U03B1\U03B2-/- Control", "DMKN \U03B1\U03B2-/- Treated"),
                           c("WT Control","DMKN \U03B1\U03B2-/- Control"),
                           c("WT Treated","DMKN \U03B1\U03B2-/- Treated"),
                           c("WT Control", "DMKN \U03B1\U03B2-/- Treated")
                           )
    
    long_data$Genotype_Treatment <- factor(long_data$Genotype_Treatment,
                                       levels = c("WT Control", "WT Treated", 
                                                  "DMKN \U03B1\U03B2-/- Control", 
                                                  "DMKN \U03B1\U03B2-/- Treated"))
  } else {
    stop("Invalid group specified. Please use either 'DTU' or 'CS'.")
  }
  
  plot <- ggplot(long_data, aes(x = Genotype_Treatment, y = Score, fill = Genotype)) +
    geom_boxplot(position = position_dodge(0.8), width = 0.7) + 
    #geom_errorbar(aes(ymin = Score - sd(Score), ymax = Score + sd(Score)), position = position_dodge(0.8), width = 0.3) +
    facet_wrap(~Var1, scales = "free_x", ncol = 5) +
    labs(x = "Comparison", y = "Kinase Activity Score") +
    theme_bw()+ ylim(-3,4.5)+ theme(
      legend.position = "bottom", 
      axis.text.x = element_text(size = 3),
      axis.text.y = element_text(size = 7), 
      axis.title = element_text(size=9, face = "bold"),
      strip.text = element_text(size = 8),
      plot.margin = margin(, 0.5, , , "cm"),
      strip.text.x = element_text(margin = margin(.05, 0, .05, 0, "cm")))+
    stat_compare_means(comparisons = my_comparisons, tip.length = 0.01, vjust = 0.55,
                       symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), 
                                          symbols = c("****", "***", "**", "*", "ns")), 
                       label = "p.signif", method = "t.test", label.y = max(long_data$Score) * 1.0,
                       step.increase = 0.08, hide.ns	= TRUE) + scale_x_discrete(guide = guide_axis(n.dodge = 2))
   plot = plot + ggtitle(title)
  return(plot)
}
plot_kinase_activity_NoSerum_all_combos <- function(input_data, group) {
  if (group == "DTU") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("", colnames(input_data))]
    labelA <- "DMKN \U03B2\U03B3-/-"
    labelB <- "DMKN \U03B1\U03B2-/-"
  } else if (group == "CS") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("", colnames(input_data))]
    labelA <- "DMKN \U03B2\U03B3-/-"
    labelB <- "DMKN \U03B1\U03B2-/-"
  } else {
    stop("Invalid group. Please specify either 'DTU' or 'CS'")
  }
  
  long_data <- melt(filtered_data, variable.name = "Condition", value.name = "Score")
  
  long_data$Genotype <- ifelse(str_detect(long_data$Var2, "DTU"), "DMKN βγ-/-",
                             ifelse(str_detect(long_data$Var2, "CS"), "DMKN \U03B1\U03B2-/-", "WT"))
  long_data$Treatment <- ifelse(str_detect(long_data$Var2, "Treated"), "Treated", "Control")
  long_data$Genotype_Treatment <- paste(long_data$Genotype, long_data$Treatment, sep = " ")
  
   # Define the list of comparisons based on the input group
  if (group == "DTU") {
    my_comparisons <- list(c("WT Control", "WT Treated"),
                           c("DMKN \U03B2\U03B3-/- Control", "DMKN \U03B2\U03B3-/- Treated"),
                           c("DMKN \U03B1\U03B2-/- Control", "DMKN \U03B1\U03B2-/- Treated"),
                           c("DMKN \U03B1\U03B2-/- Control", "DMKN \U03B2\U03B3-/- Control"),
                           c("DMKN \U03B1\U03B2-/- Treated", "DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control","DMKN \U03B2\U03B3-/- Control"),
                           c("WT Treated","DMKN \U03B1\U03B2-/- Treated"),
                           c("WT Treated","DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control", "DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control","DMKN \U03B1\U03B2-/- Treated")
                           )
        
    long_data$Genotype_Treatment <- factor(long_data$Genotype_Treatment,
                                       levels = c("WT Control", "WT Treated",
                                                  "DMKN \U03B2\U03B3-/- Control", 
                                                  "DMKN \U03B2\U03B3-/- Treated",
                                                  "DMKN \U03B1\U03B2-/- Control", 
                                                  "DMKN \U03B1\U03B2-/- Treated"))
  } else if (group == "CS") {
    my_comparisons <- list(c("WT Control", "WT Treated"),
                           c("DMKN \U03B2\U03B3-/- Control", "DMKN \U03B2\U03B3-/- Treated"),
                           c("DMKN \U03B1\U03B2-/- Control", "DMKN \U03B1\U03B2-/- Treated"),
                           c("DMKN \U03B1\U03B2-/- Control", "DMKN \U03B2\U03B3-/- Control"),
                           c("DMKN \U03B1\U03B2-/- Treated", "DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control","DMKN \U03B2\U03B3-/- Control"),
                           c("WT Treated","DMKN \U03B1\U03B2-/- Treated"),
                           c("WT Treated","DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control", "DMKN \U03B2\U03B3-/- Treated"),
                           c("WT Control","DMKN \U03B1\U03B2-/- Treated")
                           )
    
    long_data$Genotype_Treatment <- factor(long_data$Genotype_Treatment,
                                       levels = c("WT Control", "WT Treated",
                                                  "DMKN \U03B2\U03B3-/- Control", 
                                                  "DMKN \U03B2\U03B3-/- Treated",
                                                  "DMKN \U03B1\U03B2-/- Control", 
                                                  "DMKN \U03B1\U03B2-/- Treated"))
  } else {
    stop("Invalid group specified. Please use either 'DTU' or 'CS'.")
  }
  
  plot <- ggplot(long_data, aes(x = Genotype_Treatment, y = Score, fill = Genotype)) +
    geom_boxplot(position = position_dodge(0.8), width = 0.7) + 
    #geom_errorbar(aes(ymin = Score - sd(Score), ymax = Score + sd(Score)), position = position_dodge(0.8), width = 0.3) +
    facet_wrap(~Var1, scales = "free_x", ncol = 5) +
    labs(x = "Comparison", y = "Kinase Activity Score") +
    theme_bw()+ ylim(-3,4.5)+ theme(
      legend.position = "bottom", 
      axis.text.x = element_text(size = 3),
      axis.text.y = element_text(size = 7), 
      axis.title = element_text(size=9, face = "bold"),
      strip.text = element_text(size = 8),
      plot.margin = margin(, 0.5, , , "cm"),
      strip.text.x = element_text(margin = margin(.05, 0, .05, 0, "cm")))+
    stat_compare_means(comparisons = my_comparisons, tip.length = 0.01, vjust = 0.55,
                       symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), 
                                          symbols = c("****", "***", "**", "*", "ns")), 
                       label = "p.signif", method = "t.test", label.y = max(long_data$Score) * 1.0,
                       step.increase = 0.08, hide.ns	= TRUE) + scale_x_discrete(guide = guide_axis(n.dodge = 2))
  
  return(plot)
}
plot_kinase_activity_NoSerum_Genotypes <- function(input_data, group, title) {
  if (group == "DTU") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("_control|_Control", colnames(input_data))]
    label1 <- "DMKN \U03B2\U03B3-/-"
  } else if (group == "CS") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("_control|_Control", colnames(input_data))]
    label2 <- "DMKN \U03B1\U03B2-/-"
  } else {
    stop("Invalid group. Please specify either 'DTU' or 'CS'")
  }
  
  long_data <- melt(filtered_data, variable.name = "Condition", value.name = "Score")
  
  long_data$Genotype <- ifelse(str_detect(long_data$Var2, "DTU"), "DMKN βγ-/-",
                             ifelse(str_detect(long_data$Var2, "CS"), "DMKN \U03B1\U03B2-/-", "WT"))
  long_data$Treatment <- ifelse(str_detect(long_data$Var2, "Treated"), "Treated", "Control")
  long_data$Genotype_Treatment <- paste(long_data$Genotype, long_data$Treatment, sep = " ")
  
   # Define the list of comparisons based on the input group
  if (group == "DTU") {
    my_comparisons <- list(c("WT", "DMKN \U03B2\U03B3-/-"),
                           c("WT","DMKN \U03B1\U03B2-/-"),
                           c("DMKN \U03B2\U03B3-/-", "DMKN \U03B2\U03B3-/-")
                           )
        
    long_data$Genotype_Treatment <- factor(long_data$Genotype,
                                       levels = c("WT", "DMKN \U03B2\U03B3-/-",
                                                  "DMKN \U03B1\U03B2-/-"))
  } else if (group == "CS") {
    my_comparisons <- list(c("WT", "DMKN \U03B2\U03B3-/-"),
                           c("WT","DMKN \U03B1\U03B2-/-"),
                           c("DMKN \U03B2\U03B3-/-", "DMKN \U03B2\U03B3-/-")
                           
                           )
    
    long_data$Genotype_Treatment <- factor(long_data$Genotype_Treatment,
                                       levels = c("WT", "DMKN \U03B2\U03B3-/-",
                                                  "DMKN \U03B1\U03B2-/-"))
  } else {
    stop("Invalid group specified. Please use either 'DTU' or 'CS'.")
  }
  
  plot <- ggplot(long_data, aes(x = Genotype, y = Score, fill = Genotype)) +
    geom_boxplot(position = position_dodge(0.8), width = 0.7) + 
    #geom_errorbar(aes(ymin = Score - sd(Score), ymax = Score + sd(Score)), position = position_dodge(0.8), width = 0.3) +
    facet_wrap(~Var1, scales = "free_x", ncol = 5) +
    labs(x = "Comparison", y = "Kinase Activity Score") +
    theme_bw()+ ylim(-3,6)+ theme(
      legend.position = "bottom", 
      axis.text.x = element_text(size = 7),
      axis.text.y = element_text(size = 7), 
      axis.title = element_text(size=9, face = "bold"),
      strip.text = element_text(size = 8),
      plot.margin = margin(, 0.5, , , "cm"),
      strip.text.x = element_text(margin = margin(.05, 0, .05, 0, "cm")))+
    stat_compare_means(comparisons = my_comparisons, tip.length = 0.01, vjust = 0.55,
                       symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 2), 
                                          symbols = c("****", "***", "**", "*", "ns")), 
                       label = "p.signif", method = "t.test", label.y = max(long_data$Score) * 1.0,
                       step.increase = 0.25, hide.ns	= TRUE) + scale_x_discrete(guide = guide_axis(n.dodge = 2))
   plot = plot + ggtitle(title)
  return(plot)
}
plot_kinase_activity_NoSerum_Genotypes_forFIT2 <- function(input_data, group,title) {
  if (group == "DTU") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("_control|_Control", colnames(input_data))]
    label1 <- "DMKN \U03B2\U03B3-/-"
  } else if (group == "CS") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("_control|_Control", colnames(input_data))]
    label2 <- "DMKN \U03B1\U03B2-/-"
  } else {
    stop("Invalid group. Please specify either 'DTU' or 'CS'")
  }
  
  long_data <- melt(filtered_data, variable.name = "Condition", value.name = "Score")
  
  long_data$Genotype <- ifelse(str_detect(long_data$Var2, "DTU"), "DMKN βγ-/-",
                             ifelse(str_detect(long_data$Var2, "CS"), "DMKN \U03B1\U03B2-/-", "WT"))
  long_data$Treatment <- ifelse(str_detect(long_data$Var2, "Treated"), "Treated", "Control")
  long_data$Genotype_Treatment <- paste(long_data$Genotype, long_data$Treatment, sep = " ")
  
   # Define the list of comparisons based on the input group
  if (group == "DTU") {
    my_comparisons <- list(c("WT", "DMKN \U03B2\U03B3-/-"),
                           c("WT","DMKN \U03B1\U03B2-/-"),
                           c("DMKN \U03B2\U03B3-/-", "DMKN \U03B2\U03B3-/-")
                           )
        
    long_data$Genotype_Treatment <- factor(long_data$Genotype,
                                       levels = c("WT", "DMKN \U03B2\U03B3-/-",
                                                  "DMKN \U03B1\U03B2-/-"))
  } else if (group == "CS") {
    my_comparisons <- list(c("WT", "DMKN \U03B2\U03B3-/-"),
                           c("WT","DMKN \U03B1\U03B2-/-"),
                           c("DMKN \U03B2\U03B3-/-", "DMKN \U03B2\U03B3-/-")
                           
                           )
    
    long_data$Genotype_Treatment <- factor(long_data$Genotype_Treatment,
                                       levels = c("WT", "DMKN \U03B2\U03B3-/-",
                                                  "DMKN \U03B1\U03B2-/-"))
  } else {
    stop("Invalid group specified. Please use either 'DTU' or 'CS'.")
  }
  
  plot <- ggplot(long_data, aes(x = Genotype, y = Score, fill = Genotype)) +
    geom_boxplot(position = position_dodge(0.8), width = 0.7) + 
    #geom_errorbar(aes(ymin = Score - sd(Score), ymax = Score + sd(Score)), position = position_dodge(0.8), width = 0.3) +
    facet_wrap(~Var1, scales = "free_x", ncol = 5) +
    labs(x = "Comparison", y = "Kinase Activity Score") +
    theme_bw()+ ylim(-3,6)+ theme(
      legend.position = "bottom", 
      axis.text.x = element_text(size = 7),
      axis.text.y = element_text(size = 7), 
      axis.title = element_text(size=9, face = "bold"),
      strip.text = element_text(size = 8),
      plot.margin = margin(, 0.5, , , "cm"),
      strip.text.x = element_text(margin = margin(.05, 0, .05, 0, "cm")))+
    stat_compare_means(comparisons = my_comparisons, tip.length = 0.01, vjust = 0.55,
                       symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 2), 
                                          symbols = c("****", "***", "**", "*", "ns")), 
                       label = "p.signif", method = "t.test", label.y = max(long_data$Score) * 1.0,
                       step.increase = 0.25, hide.ns	= TRUE) + scale_x_discrete(guide = guide_axis(n.dodge = 2))
  plot = plot + ggtitle(title)
  return(plot)
}
plot_kinase_activity_NoSerum_Genotypes_forFIT3 <- function(input_data, group,title) {
  if (group == "DTU") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("WT_NoSerum_Control|DTU_NoSerum_Control", colnames(input_data))]
    label <- "DMKN \U03B2\U03B3-/-"
  } else if (group == "CS") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("WT_NoSerum_Control|CS_NoSerum_Control", colnames(input_data))]
    label <- "DMKN \U03B1\U03B2-/-"
  } else {
    stop("Invalid group. Please specify either 'DTU' or 'CS'")
  }
  
  long_data <- melt(filtered_data, variable.name = "Condition", value.name = "Score")
  
  long_data$Genotype <- ifelse(str_detect(long_data$Var2, "DTU"), "DMKN βγ-/-",
                           ifelse(str_detect(long_data$Var2, "CS"), "DMKN αβ-/-", "WT"))

long_data$Genotype <- factor(long_data$Genotype,
                           levels = c("WT", "DMKN βγ-/-", "DMKN αβ-/-"))

  long_data$Treatment <- ifelse(str_detect(long_data$Var2, "Treated"), "Treated", "Control")
  long_data$Genotype_Treatment <- paste(long_data$Genotype, long_data$Treatment, sep = " ")
  
   # Define the list of comparisons based on the input group
  if (group == "DTU") {
     my_comparisons <- list(c("DMKN βγ-/-", "WT"))
} else if (group == "CS") {
     my_comparisons <- list(c("DMKN αβ-/-","WT"))
}
 else {
    stop("Invalid group specified. Please use either 'DTU' or 'CS'.")
  }
  
  plot <- ggplot(long_data, aes(x = Genotype, y = Score, fill = Genotype)) +
    geom_boxplot(position = position_dodge(0.8), width = 0.7) + 
    #geom_errorbar(aes(ymin = Score - sd(Score), ymax = Score + sd(Score)), position = position_dodge(0.8), width = 0.3) +
    facet_wrap(~Var1, scales = "free_x", ncol = 5) +
    labs(x = "Comparison", y = "Kinase Activity Score") +
    theme_bw()+ ylim(-3,5)+ theme(
      legend.position = "bottom", 
      axis.text.x=element_blank(),
      axis.text.y = element_text(size = 7), 
      axis.title = element_text(size=9, face = "bold"),
      strip.text = element_text(size = 8),
      plot.margin = margin(, 0.5, , , "cm"),
      legend.key.size = unit(1, 'cm'),
      legend.title = element_text(size=14), 
        legend.text = element_text(size=14),
      strip.text.x = element_text(margin = margin(.05, 0, .05, 0, "cm")))+
    stat_compare_means(comparisons = my_comparisons, tip.length = 0.01, vjust = 0.55,
                       symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 2), 
                                          symbols = c("****", "***", "**", "*", "ns")), 
                       label = "p.signif", method = "t.test", label.y = max(long_data$Score) * 1.0,
                       step.increase = 0.25, hide.ns	= TRUE) + scale_x_discrete(guide = guide_axis(n.dodge = 2))
  
  if (group == "DTU") {
    plot <- plot + scale_fill_manual(values = c("DMKN βγ-/-" = "#1b9e77", "WT" = "#d95f02"))
  } else if (group == "CS") {
    plot <- plot + scale_fill_manual(values = c("DMKN αβ-/-" = "#7570b3", "WT" = "#d95f02"))
  }
  plot = plot + ggtitle(title)
  return(plot)
}

plot_kinase_activity_Serum_Genotypes_forFIT4 <- function(input_data, group,title) {
  if (group == "DTU") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("WT_Serum_Control|DTU_Serum_Control", colnames(input_data))]
    label <- "DMKN \U03B2\U03B3-/-"
  } else if (group == "CS") {
    #Change to WT_NoSerum_Control if I dont want to show treated
    filtered_data <- input_data[, grep("WT_Serum_Serum_Control|CS_Serum_Control", colnames(input_data))]
    label <- "DMKN \U03B1\U03B2-/-"
  } else {
    stop("Invalid group. Please specify either 'DTU' or 'CS'")
  }
  
  long_data <- melt(filtered_data, variable.name = "Condition", value.name = "Score")
  
  long_data$Genotype <- ifelse(str_detect(long_data$Var2, "DTU"), "DMKN βγ-/-",
                           ifelse(str_detect(long_data$Var2, "CS"), "DMKN αβ-/-", "WT"))

long_data$Genotype <- factor(long_data$Genotype,
                           levels = c("WT", "DMKN βγ-/-", "DMKN αβ-/-"))

  long_data$Treatment <- ifelse(str_detect(long_data$Var2, "Treated"), "Treated", "Control")
  long_data$Genotype_Treatment <- paste(long_data$Genotype, long_data$Treatment, sep = " ")
  
   # Define the list of comparisons based on the input group
  if (group == "DTU") {
     my_comparisons <- list(c("DMKN βγ-/-", "WT"))
} else if (group == "CS") {
     my_comparisons <- list(c("DMKN αβ-/-","WT"))
}
 else {
    stop("Invalid group specified. Please use either 'DTU' or 'CS'.")
  }
  
  plot <- ggplot(long_data, aes(x = Genotype, y = Score, fill = Genotype)) +
    geom_boxplot(position = position_dodge(0.8), width = 0.7) + 
    #geom_errorbar(aes(ymin = Score - sd(Score), ymax = Score + sd(Score)), position = position_dodge(0.8), width = 0.3) +
    facet_wrap(~Var1, scales = "free_x") +
    labs(x = "Comparison", y = "Kinase Activity Score") +
    theme_bw()+ ylim(-3,5)+ theme(
      legend.position = "bottom", 
      axis.text.x=element_blank(),
      axis.text.y = element_text(size = 7), 
      axis.title = element_text(size=9, face = "bold"),
      strip.text = element_text(size = 8),
      plot.margin = margin(, 0.5, , , "cm"),
      legend.key.size = unit(1, 'cm'),
      legend.title = element_text(size=14), 
        legend.text = element_text(size=14),
      strip.text.x = element_text(margin = margin(.05, 0, .05, 0, "cm")))+
    stat_compare_means(comparisons = my_comparisons, tip.length = 0.01, vjust = 0.55,
                       symnum.args = list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 2), 
                                          symbols = c("****", "***", "**", "*", "ns")), 
                       label = "p.signif", method = "t.test", label.y = max(long_data$Score) * 1.0,
                       step.increase = 0.25, hide.ns	= TRUE) + scale_x_discrete(guide = guide_axis(n.dodge = 2))
  
  if (group == "DTU") {
    plot <- plot + scale_fill_manual(values = c("DMKN βγ-/-" = "#1b9e77", "WT" = "#d95f02"))
  } else if (group == "CS") {
    plot <- plot + scale_fill_manual(values = c("DMKN αβ-/-" = "#7570b3", "WT" = "#d95f02"))
  }
  plot = plot + ggtitle(title)
  return(plot)
}


remove_terms_after_third_semicolon <- function(rowname) {
  split_name <- strsplit(rowname, ";")[[1]]
  new_name <- paste(split_name[1:4], collapse = ";")
  return(new_name)
}
extract_flanking_seq <- function(named_FASTA, rownames_ppe) {
  updated_rownames <- c()

  for (rowname in rownames_ppe) {
    split_name <- strsplit(rowname, ";")[[1]]
    
    # Remove the first and third terms if there are more than 4 terms
    if (length(split_name) > 4) {
      split_name <- split_name[-c(1, 3)]
    }
    # Remove any terms after the third semicolon
    split_name <- split_name[1:4]
    
    rowname <- remove_terms_after_third_semicolon(rowname)
    gene_id <- split_name[2]
    position <- as.integer(gsub("\\D", "", split_name[3]))
    matches <- grep(paste0(".*;", gene_id, "$"), names(named_FASTA), value = TRUE)

    if (length(matches) > 0) {
      protein_seq <- named_FASTA[matches[1]]

      # Correct the position indexing
      start <- max(1, position - 7)
      stop <- min(nchar(protein_seq), position + 7)

      flanking_seq <- substr(protein_seq, start, stop)
      new_name <- paste(split_name[1], split_name[2], split_name[3], flanking_seq, sep = ";")
      updated_rownames <- c(updated_rownames, new_name)
    } else {
      updated_rownames <- c(updated_rownames, rowname)
    }
  }

  return(updated_rownames)
}



fasta_to_named_list <- function(fasta_lines) {
  named_list <- list()
  current_header <- ""

  for (line in fasta_lines) {
    if (startsWith(line, ">")) {
      uniprot_id <- sub("^.*\\|(.+?)\\|.*$", "\\1", line)
      gene_id <- sub("^.*GN=(\\S+).*?$", "\\1", line)
      current_header <- paste(uniprot_id, gene_id, sep = ";")
    } else {
      named_list[[current_header]] <- line
    }
  }

  return(named_list)
}


reformat_fasta_df <- function(fasta_df) {
  reformatted_lines <- c()
  current_sequence <- ""
  
  for (i in 1:nrow(fasta_df)) {
    line <- as.character(fasta_df[i, 1])
    if (!is.na(line)) {
      if (startsWith(line, ">")) {
        if (nchar(current_sequence) > 0) {
          reformatted_lines <- c(reformatted_lines, current_sequence)
          current_sequence <- ""
        }
        reformatted_lines <- c(reformatted_lines, line)
      } else {
        current_sequence <- paste0(current_sequence, line)
      }
    }
  }
  
  if (nchar(current_sequence) > 0) {
    reformatted_lines <- c(reformatted_lines, current_sequence)
  }
  
  return(reformatted_lines)
}
rename_columns <- function(df) { new_colnames <- c("WT_NoSerum_Control", "WT_NoSerum_Treated", "WT_Serum_Control", "WT_Serum_Treated", "KO_DTU_NoSerum_Control", "KO_DTU_NoSerum_Treated", "KO_DTU_Serum_Control", "KO_DTU_Serum_Treated", "KO_CS_NoSerum_Control", "KO_CS_NoSerum_Treated", "KO_CS_Serum_Control", "KO_CS_Serum_Treated") 
for (i in 1:length(new_colnames)) 
  { 
    start_col <- (i - 1) * 3 + 1 
    end_col <- start_col + 2 
    colnames(df)[start_col:end_col] <- paste(new_colnames[i], rep(1:3, 1), sep = "_Rep") } 
  return(df) }


rename_columns_2 <- function(df) {
  new_colnames <- c("WT_NoSerum_Control", "WT_NoSerum_Treated",
                    "KO_DTU_NoSerum_Control", "KO_DTU_NoSerum_Treated",
                    "KO_CS_NoSerum_Control", "KO_CS_NoSerum_Treated")
  for (i in 1:length(new_colnames)) {
    start_col <- (i - 1) * 3 + 1
    end_col <- start_col + 2
    colnames(df)[start_col:end_col] <- paste(new_colnames[i], rep(1:3, 1), sep = "_Rep")
  }
  return(df)
}

calculate_log2fc_combined <- function(df) {
    log2fc_df <- data.frame(matrix(ncol = 14, nrow = nrow(df)))
  colnames(log2fc_df) <- c("WT_NoSerum", "WT_Serum", "KO_DTU_NoSerum", "KO_DTU_Serum", "KO_CS_NoSerum", "KO_CS_Serum",
                            "KO_DTU_NoSerum_treated_WT_NoSerum_control", "KO_DTU_Serum_treated_WT_Serum_control",
                            "KO_CS_NoSerum_treated_WT_NoSerum_control", "KO_CS_Serum_treated_WT_Serum_control",
                            "KO_DTU_NoSerum_control_WT_NoSerum_control", "KO_DTU_Serum_control_WT_Serum_control",
                            "KO_CS_NoSerum_control_WT_NoSerum_control", "KO_CS_Serum_control_WT_Serum_control")


   # Define control and treated columns for each group
  WT_NoSerum_control <- c(1, 2, 3)
  WT_NoSerum_treated <- c(4, 5, 6)
  
  WT_Serum_control <- c(7, 8, 9)
  WT_Serum_treated <- c(10, 11, 12)
  
  KO_DTU_NoSerum_control <- c(13, 14, 15)
  KO_DTU_NoSerum_treated <- c(16, 17, 18)
  
  KO_DTU_Serum_control <- c(19, 20, 21)
  KO_DTU_Serum_treated <- c(22, 23, 24)
  
  KO_CS_NoSerum_control <- c(25, 26, 27)
  KO_CS_NoSerum_treated <- c(28, 29, 30)
  
  KO_CS_Serum_control <- c(31, 32, 33)
  KO_CS_Serum_treated <- c(34, 35, 36)

group_list <- list(WT_NoSerum = list(control = WT_NoSerum_control, treated = WT_NoSerum_treated),
                   WT_Serum = list(control = WT_Serum_control, treated = WT_Serum_treated),
                   KO_DTU_NoSerum = list(control = KO_DTU_NoSerum_control, treated = KO_DTU_NoSerum_treated),
                   KO_DTU_Serum = list(control = KO_DTU_Serum_control, treated = KO_DTU_Serum_treated),
                   KO_CS_NoSerum = list(control = KO_CS_NoSerum_control, treated = KO_CS_NoSerum_treated),
                   KO_CS_Serum = list(control = KO_CS_Serum_control, treated = KO_CS_Serum_treated),
                   KO_DTU_NoSerum_treated_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_DTU_NoSerum_treated),
                   KO_DTU_Serum_treated_WT_Serum_control = list(control = WT_Serum_control, treated = KO_DTU_Serum_treated),
                   KO_CS_NoSerum_treated_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_CS_NoSerum_treated),
                   KO_CS_Serum_treated_WT_Serum_control = list(control = WT_Serum_control, treated = KO_CS_Serum_treated),
                   KO_DTU_NoSerum_control_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_DTU_NoSerum_control),
                   KO_DTU_Serum_control_WT_Serum_control = list(control = WT_Serum_control, treated = KO_DTU_Serum_control),
                   KO_CS_NoSerum_control_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_CS_NoSerum_control),
                   KO_CS_Serum_control_WT_Serum_control = list(control = WT_Serum_control, treated = KO_CS_Serum_control))

for (i in seq(1, length(group_list))) {
  treated_cols <- group_list[[names(group_list)[i]]][["treated"]]
  control_cols <- group_list[[names(group_list)[i]]][["control"]]
  # Filter out rows with NA values in either control or treated groups
  no_na_rows <- !rowSums(is.na(df[, c(control_cols, treated_cols)]))
  filtered_df <- df[no_na_rows, ]
  
  log2fc_df[no_na_rows, i] <- log2(rowMeans(filtered_df[, treated_cols]) / rowMeans(filtered_df[, control_cols]))
}
return(log2fc_df)
}

calculate_log2fc_combined_2 <- function(df) {
  log2fc_df <- data.frame(matrix(ncol = 6, nrow = nrow(df)))
  colnames(log2fc_df) <- c("WT_NoSerum", "KO_DTU_NoSerum", "KO_CS_NoSerum",
                            "KO_DTU_NoSerum_treated_WT_NoSerum_control",
                            "KO_CS_NoSerum_treated_WT_NoSerum_control",
                            "KO_DTU_NoSerum_control_WT_NoSerum_control",
                            "KO_CS_NoSerum_control_WT_NoSerum_control")

  # Define control and treated columns for each group
  WT_NoSerum_control <- c(1, 2, 3)
  WT_NoSerum_treated <- c(4, 5, 6)
  
  KO_DTU_NoSerum_control <- c(7, 8, 9)
  KO_DTU_NoSerum_treated <- c(10, 11, 12)
  
  KO_CS_NoSerum_control <- c(13, 14, 15)
  KO_CS_NoSerum_treated <- c(16, 17, 18)

  group_list <- list(WT_NoSerum = list(control = WT_NoSerum_control, treated = WT_NoSerum_treated),
                     KO_DTU_NoSerum = list(control = KO_DTU_NoSerum_control, treated = KO_DTU_NoSerum_treated),
                     KO_CS_NoSerum = list(control = KO_CS_NoSerum_control, treated = KO_CS_NoSerum_treated),
                     KO_DTU_NoSerum_treated_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_DTU_NoSerum_treated),
                     KO_CS_NoSerum_treated_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_CS_NoSerum_treated),
                     KO_DTU_NoSerum_control_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_DTU_NoSerum_control),
                     KO_CS_NoSerum_control_WT_NoSerum_control = list(control = WT_NoSerum_control, treated = KO_CS_NoSerum_control))

  for (i in seq(1, length(group_list))) {
    treated_cols <- group_list[[names(group_list)[i]]][["treated"]]
    control_cols <- group_list[[names(group_list)[i]]][["control"]]
    # Filter out rows with NA values in either control or treated groups
    no_na_rows <- !rowSums(is.na(df[, c(control_cols, treated_cols)]))
    filtered_df <- df[no_na_rows, ]
    
    log2fc_df[no_na_rows, i] <- log2(rowMeans(filtered_df[, treated_cols]) / rowMeans(filtered_df[, control_cols]))
  }
  return(log2fc_df)
}
create_histogram_subplots <- function(df) {
  plot_list <- list()
  for (i in 1:ncol(df)) {
    p <- ggplot(df, aes_string(x = colnames(df)[i])) +
      geom_histogram(binwidth = 0.1, fill = "blue", alpha = 0.7) +
      theme_minimal() + annotate("text", x = max(3), y =max(10), 
                                 label = print(nrow(na.omit(df)))) +
      labs(x = colnames(df)[i], y = "Frequency", title = colnames(df)[i]) +
      theme(plot.title = element_text(hjust = 0.5))
    plot_list[[i]] <- p
  }
  grid.arrange(grobs = plot_list, ncol = 2)
}

display_min_max_values <- function(df) {
  for (i in 1:ncol(df)) {
    col_name <- colnames(df)[i]
    min_value <- min(df[[col_name]], na.rm = TRUE)
    max_value <- max(df[[col_name]], na.rm = TRUE)
    cat(sprintf("Column: %s\nMin value: %f\nMax value: %f\n\n", col_name, min_value, max_value))
  }
}


  
create_group_plot <- function(data, group_mean_col, group_fc_col, title) {
  
  group_fc_values <- data[[group_fc_col]]
  not_significant_count <- sum(group_fc_values >= -0.5849 & group_fc_values <= 0.5849, na.rm = TRUE)
  downregulated_count  <- sum(group_fc_values < -0.5849, na.rm = TRUE)
  upregulated_count <- sum(group_fc_values > 0.5849, na.rm = TRUE)
  
  ggplot(data, aes_string(x = group_fc_col, y = group_mean_col)) +
    geom_point(aes_string(color = paste("ifelse(", group_fc_col, " > 0.5849, 'red', ifelse(", group_fc_col, " < -0.5849, 'blue', 'black'))")), alpha = 0.3, shape =16, size = 1) +
    scale_color_identity() +
    theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        axis.title=element_text(size=8)) +
    labs(x = title, y = "Log10 XIC", size =1.0) +
    geom_point(aes(x = -6.75, y = log10(10^(10.0)), color = 'black'), size = 1.0, shape = 16) +
    geom_point(aes(x = -6.75, y = log10(10^(9.5)), color = 'blue'), size = 1.0, shape = 16) +
    geom_point(aes(x = -6.75, y = log10(10^(9.00)), color = 'red'), size = 1.0, shape = 16) +
    annotate("text", x = -6.5, y = log10(10^(10.0)),
             label = paste("Not significant: n=", not_significant_count),
             hjust = 0, size = 1.75) +
    annotate("text", x = -6.5, y = log10(10^(9.5)),
             label = paste("Sig. down-regulated: n=", downregulated_count),
             hjust = 0, size = 1.75) +
    annotate("text", x = -6.5, y = log10(10^(9.00)),
             label = paste("Sig. up-regulated: n=", upregulated_count),
             hjust = 0, size = 1.75) +
    annotate("text", x = 4.0, y = log10(10^(9.8)),
             label = paste("N = 3"),
             hjust = 0, size = 2.5) +
    coord_cartesian(xlim = c(-6.5, 5), ylim = c(log10(10^(4.00)), log10(10^(10.00))))
}

  # Combine subplots into a grid
  library(gridExtra)
#grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, plot7, plot8, plot9, plot10, plot11, plot12, plot13, plot14, ncol = 3)
#  options(repr.plot.width = 14, repr.plot.height =16)
NoSerum_plot = grid.arrange(plot11, plot13, plot7, plot9, plot2, plot3, ncol = 2)
Serum_plot = grid.arrange(plot12, plot14, plot8, plot10, plot5, plot6, ncol = 2)
NoSerum_plot ; Serum_plot ; ggsave(filename=paste("NoSerum_plot", ".pdf"), plot = NoSerum_plot, device = "pdf") ; ggsave(filename=paste("Serum_plot", ".pdf"), plot = Serum_plot, device = "pdf")
}

fuzzPlot <- function (Tc, clustObj, mfrow = c(1, 1), cols, min.mem = 0, new.window = FALSE, llwd = 3, x_labels) {
    clusterindex <- clustObj$cluster
    memship <- clustObj$membership
    memship[memship < min.mem] <- -1
    
    colorindex <- integer(dim(Tc)[[1]])
    if (missing(cols)) {
      cols <- c("#FF8F00", "#FFA700", "#FFBF00", "#FFD700", "#FFEF00", "#F7FF00", "#DFFF00", "#C7FF00", "#AFFF00", "#97FF00", "#80FF00", "#68FF00", "#50FF00", "#38FF00", "#20FF00", "#08FF00", "#00FF10", "#00FF28", "#00FF40", "#00FF58", "#00FF70", "#00FF87", "#00FF9F", "#00FFB7", "#00FFCF", "#00FFE7", "#00FFFF", "#00E7FF", "#00CFFF", "#00B7FF", "#009FFF", "#0087FF", "#0070FF", "#0058FF", "#0040FF", "#0028FF", "#0010FF", "#0800FF", "#2000FF", "#3800FF", "#5000FF", "#6800FF", "#8000FF", "#9700FF", "#AF00FF", "#C700FF", "#DF00FF", "#F700FF", "#FF00EF", "#FF0030", "#FF0018")
    }
    colorseq <- seq(0, 1, length = length(cols))
    for (j in 1:max(clusterindex)) {
      tmp <- Tc[clusterindex == j, ]
      tmpmem <- memship[clusterindex == j, j]
      if (((j - 1) %% (mfrow[1] * mfrow[2])) == 0) {
        if (new.window) 
          dev.new()
        par(mfrow = mfrow)
        if (sum(clusterindex == j) == 0) {
          ymin <- -1
          ymax <- +1
        }
        else {
          ymin <- min(tmp)
          ymax <- max(tmp)
        }
        plot(x = NA, xlim = c(1, dim(Tc)[[2]]), ylim = c(ymin, ymax), xaxt = "n", xlab = "", ylab = "Standardized Profile", main = paste("Cluster", j, "; size=", nrow(tmp)))
        axis(1, at = 1:ncol(Tc), labels = x_labels)
        
       mean_tmp <- apply(tmp, 2, mean)

      # Fit a linear model
      fit <- lm(mean_tmp ~ log(1:ncol(Tc)))

      
      # Add the linear trend line to the plot
      lines(predict(fit), col = 'black')
      }
      else {
        if (sum(clusterindex == j) == 0) {
          ymin <- -1
          ymax <- +1
        }
        else {
          ymin <- min(tmp)
          ymax <- max(tmp)
        }
        
        plot(x = NA, xlim = c(1, dim(Tc)[[2]]), ylim = c(ymin, ymax), xaxt = "n", xlab = "", ylab = "Standardized Profile", main = paste("Cluster", j, "; size=", nrow(tmp)))
             axis(1, at = 1:ncol(Tc), labels = x_labels, las = 2, cex.axis = 1, tck = -0.01)
             # Add the angled labels with custom size
             
        # Calculate the overall trend line
        y_all <- c(tmp)
        x_all <- c(rep(1:ncol(Tc), nrow(tmp)))
        loess_fit <- loess(y_all ~ x_all)
        # Add the overall trend line to the plot
        lines(1:ncol(Tc), predict(loess_fit, data.frame(x_all = 1:ncol(Tc))), col = "black", lwd = 2, lty = 2)

      }
      if (!(sum(clusterindex == j) == 0)) {
        for (jj in 1:(length(colorseq) - 1)) {
          tmpcol <- (tmpmem >= colorseq[jj] & tmpmem <= colorseq[jj + 1])
          if (sum(tmpcol) > 0) {
            tmpind <- which(tmpcol)
            for (k in 1:length(tmpind)) {
              lines(tmp[tmpind[k], ], col = cols[jj], lwd = llwd)
            }
          }
        }
      }
    }
  }

custom_clustOptimal <- function  (clueObj, rep = 5, user.maxK = NULL, visualize = TRUE, x_labels,...) {
    bstPvalue <- 1
    bst.clustObj <- c()
    bst.evaluation <- c()
    for (i in 1:rep) {
        clustObj <- c()
        if (clueObj$clustAlg == "cmeans") {
            if (is.null(user.maxK)) {
                clustObj <- cmeans(clueObj$Tc, centers = clueObj$maxK, 
                  iter.max = 50, m = 1.25)
            }
            else {
                clustObj <- cmeans(clueObj$Tc, centers = user.maxK, 
                  iter.max = 50, m = 1.25)
            }
        }
        else {
            if (is.null(user.maxK)) {
                clustObj <- kmeans(clueObj$Tc, centers = clueObj$maxK, 
                  iter.max = 50)
                clustObj$membership <- matrix(1, nrow = nrow(clueObj$Tc), 
                  ncol = nrow(clustObj$centers))
                rownames(clustObj$membership) <- names(clustObj$cluster)
            }
            else {
                clustObj <- kmeans(clueObj$Tc, centers = user.maxK, 
                  iter.max = 50)
                clustObj$membership <- matrix(1, nrow = nrow(clueObj$Tc), 
                  ncol = nrow(clustObj$centers))
                rownames(clustObj$membership) <- names(clustObj$cluster)
            }
        }
        evaluation <- clustEnrichment(clustObj, clueObj$annotation, 
            clueObj$effectiveSize, clueObj$pvalueCutoff)
        currentPvalue <- evaluation$fisher.pvalue
        if (currentPvalue < bstPvalue) {
            bstPvalue <- currentPvalue
            bst.clustObj <- clustObj
            bst.enrichList <- evaluation$enrich.list
        }
    }
    if (visualize) {
        fuzzPlot(clueObj$Tc, clustObj = bst.clustObj, x_labels = x_labels,...)
    }
    results <- list()
    results$clustObj <- bst.clustObj
    results$enrichList <- bst.enrichList
    return(results)
}

custom_runClue = function (Tc, annotation, rep = 5, kRange = 2:10, clustAlg = "cmeans", 
    effectiveSize = c(5, 100), pvalueCutoff = 0.05, alpha = 0.5) 
{
    means <- apply(Tc, 1, mean)
    stds <- apply(Tc, 1, sd)
    tmp <- sweep(Tc, 1, means, FUN = "-")
    Tc <- sweep(tmp, 1, stds, FUN = "/")
    annotation.intersect <- lapply(annotation, intersect, rownames(Tc))
    annotation.filtered <- annotation.intersect[lapply(annotation.intersect, 
        length) > 0]
     # ... (same code as before, up to the repeat.list)

  repeat.list <- mclapply(1:rep, function(rp) {
    cat("repeat", rp, "\n")
    enrichment <- c()
    for (k in kRange) {
      clustered <- c()
      
      # Perform na.omit on Tc before clustering
      Tc_no_na <- na.omit(Tc)

      if (clustAlg == "cmeans") {
        clustered <- cmeans(Tc_no_na, centers = k, iter.max = 50, m = 1.25)
      } else if (clustAlg == "kmeans") {
        clustered <- kmeans(Tc_no_na, centers = k, iter.max = 50)
      } else {
        print("Unknown clustering algorithm specified. Using cmeans clustering instead")
        clustered <- cmeans(Tc_no_na, centers = k, iter.max = 50, m = 1.25)
      }
      evaluate <- clustEnrichment(clustered, annotation.filtered, effectiveSize, pvalueCutoff)
      fisher.pvalue <- evaluate$fisher.pvalue
      escore <- -log10(fisher.pvalue) - alpha * nrow(clustered$centers)
      enrichment <- c(enrichment, escore)
    }
    enrichment
  })

  # ... (same code as before, after the repeat.list)
    x <- do.call(rbind, repeat.list)
    x.normalize <- (x - min(x))/(max(x) - min(x))
    rownames(x.normalize) <- paste("repeat", 1:rep, sep = "")
    colnames(x.normalize) <- paste("k", kRange, sep = "=")
    maxK <- which.max(apply(x.normalize, 2, median)) + (kRange[1] - 
        1)
    result <- list()
    result$Tc <- Tc
    result$annotation <- annotation.filtered
    result$clustAlg <- clustAlg
    result$effectiveSize <- effectiveSize
    result$pvalueCutoff <- pvalueCutoff
    result$evlMat <- x.normalize
    result$maxK <- maxK
    return(result)
}


custom_kinaseSubstratePred = function (phosScoringMatrices, ensembleSize = 10, top = 50, cs = 0.8, 
    inclusion = 20, iter = 5, verbose = TRUE) 
{
    substrate.list = substrateList(phosScoringMatrices, top, 
        cs, inclusion)
    if (verbose) 
        message("Predicting kinases for phosphosites:")
    featureMat <- phosScoringMatrices$combinedScoreMatrix
    predMatrix <- matrix(0, nrow = nrow(featureMat), ncol = length(substrate.list))
    colnames(predMatrix) <- names(substrate.list)
    rownames(predMatrix) <- rownames(featureMat)
    tmp.list = lapply(seq(length(substrate.list)), function(i) {
        positive.train <- featureMat[substrate.list[[i]], ]
        positive.cls <- rep(1, length(substrate.list[[i]]))
        negative.pool <- featureMat[!(rownames(featureMat) %in% 
            substrate.list[[i]]), ]
        if (verbose) 
            message(paste(i, ".", sep = ""))
        tmp_col = predMatrix[, i]
        for (e in seq_len(ensembleSize)) {
            negativeSize <- length(substrate.list[[i]])
            idx <- sample(seq_len(nrow(negative.pool)), size = negativeSize, 
                replace = TRUE)
            negative.samples <- rownames(negative.pool)[idx]
            negative.train <- featureMat[negative.samples, ]
            negative.cls <- rep(2, length(negative.samples))
            train.mat <- rbind(positive.train, negative.train)
            cls <- as.factor(c(positive.cls, negative.cls))
            names(cls) <- rownames(train.mat)
            pred <- multiAdaSampling(train.mat, test.mat = featureMat, 
                label = cls, kernelType = "radial", iter = iter)
            tmp_col <- tmp_col[names(pred[, 1])] + pred[, 1]
        }
        tmp_col
    })
    predMatrix = matrix(unlist(tmp.list), ncol = ncol(predMatrix))
    colnames(predMatrix) = names(substrate.list)
    rownames(predMatrix) = rownames(featureMat)
    predMatrix <- predMatrix/ensembleSize
    if (verbose) 
        message("done")
    return(predMatrix)
}

multiAdaSampling <- function(train.mat, test.mat,
    label, kernelType, iter = 5) {

    X <- train.mat
    Y <- label

    model <- c()
    prob.mat <- c()

    for (i in seq_len(iter)) {
        tmp <- X
        rownames(tmp) <- NULL
        model <- e1071::svm(tmp, factor(Y),
            kernel = kernelType, probability = TRUE)
        prob.mat <- attr(predict(model, train.mat,
            decision.values = FALSE, probability = TRUE),
            "probabilities")

        X <- c()
        Y <- c()
        for (j in seq_len(ncol(prob.mat))) {
            voteClass <- prob.mat[label == colnames(prob.mat)[j], ]
            idx <- c()
            idx <- sample(seq_len(nrow(voteClass)),
                size = nrow(voteClass), replace = TRUE,
                prob = voteClass[, j])
            X <- rbind(X, train.mat[rownames(voteClass)[idx],])
            Y <- c(Y, label[rownames(voteClass)[idx]])
        }
    }

    pred <- attr(predict(model, newdata = test.mat,
        probability = TRUE), "prob")
    return(pred)
}

kinaseSubstrateHeatmap_modified <- function (phosScoringMatrices, top = 3, printPlot = NULL, filePath = "./kinaseSubstrateHeatmap.pdf", 
    width = 10, height = 10) 
{
    utils::data("KinaseFamily", envir = environment())
    sites <- c()
    for (i in seq_len(ncol(phosScoringMatrices$combinedScoreMatrix))) {
        sites <- union(sites, names(sort(phosScoringMatrices$combinedScoreMatrix[, 
            i], decreasing = TRUE)[seq_len(top)]))
    }
    o <- intersect(colnames(phosScoringMatrices$combinedScoreMatrix), 
        rownames(KinaseFamily))
    annotation_col = data.frame(group = KinaseFamily[o, "kinase_group"], 
        family = KinaseFamily[o, "kinase_family"])
    rownames(annotation_col) <- o
    if (is.null(printPlot) == TRUE) {
      
        pheatmap::pheatmap(phosScoringMatrices$combinedScoreMatrix[sites, 
            ], annotation_col = annotation_col, cluster_rows = TRUE, 
            cluster_cols = TRUE, fontsize = 6, show_row_dendrogram = FALSE, show_col_dendrogram = FALSE)
      
    }
    else {
        pdf(file = filePath, width = width, height = height)
      
        pheatmap::pheatmap(phosScoringMatrices$combinedScoreMatrix[sites, 
            ], annotation_col = annotation_col, cluster_rows = TRUE, 
            cluster_cols = TRUE, fontsize = 6, show_row_dendrogram = FALSE, show_col_dendrogram = FALSE)
        
        dev.off()
    }
}
kinaseSubstrateHeatmap_modified <- function (phosScoringMatrices, top = 3, printPlot = NULL, filePath = "./kinaseSubstrateHeatmap.pdf", 
    width = 10, height = 10) 
{
    utils::data("KinaseFamily", envir = environment())
    sites <- c()
    for (i in seq_len(ncol(phosScoringMatrices$combinedScoreMatrix))) {
        sites <- union(sites, names(sort(phosScoringMatrices$combinedScoreMatrix[, 
            i], decreasing = TRUE)[seq_len(top)]))
    }
    if (is.null(printPlot) == TRUE) {
        pheatmap::pheatmap(phosScoringMatrices$combinedScoreMatrix[sites, 
            ], cluster_rows = TRUE, 
            cluster_cols = TRUE, fontsize = 6, show_row_dendrogram = FALSE, show_col_dendrogram = FALSE, show_rownames = FALSE, legend = FALSE)
    }
    else {
        pdf(file = filePath, width = width, height = height)
        pheatmap::pheatmap(phosScoringMatrices$combinedScoreMatrix[sites, 
            ], cluster_rows = TRUE, 
            cluster_cols = TRUE, fontsize = 6, show_row_dendrogram = FALSE, show_col_dendrogram = FALSE, show_rownames = FALSE, legend = FALSE)
        dev.off()
    }
}
siteAnnotate_modified <- function(site, phosScoringMatrices, predMatrix) {
  od <- order(predMatrix[site, ], decreasing = FALSE)
  kinases <- colnames(predMatrix)[od]
  
  par(mfrow = c(1, 4), mar = c(1, 5, 5, 1))
  
  barplot(predMatrix[site, kinases], las = 1, xlab = "Prediction score", 
          col = "red3", main = "Prediction score", xlim = c(0, 1), horiz = TRUE, xaxt= "n")
  axis(3)
  barplot(phosScoringMatrices$combinedScoreMatrix[site, kinases], 
          las = 1, main = "Combined score", col = "orange2", xlim = c(0, 1), horiz = TRUE,xaxt= "n")
   axis(3)
  barplot(phosScoringMatrices$motifScoreMatrix[site, kinases], 
          las = 1, main = "Motif score", col = "green4", xlim = c(0, 1), horiz = TRUE,xaxt= "n")
   axis(3)
  barplot(phosScoringMatrices$profileScoreMatrix[site, kinases], 
          las = 1, main = "Profile score", col = "lightblue3", 
          xlim = c(0, 1), horiz = TRUE,xaxt= "n")
   axis(3)
  mtext(paste("Site =", site),                   # Add main title
      side = 3,
      line = - 2,
      outer = TRUE)
}

siteAnnotate_modified_ggplot <- function(site, phosScoringMatrices, predMatrix) {
  od <- order(predMatrix[site, ], decreasing = FALSE)
  kinases <- colnames(predMatrix)[od]
  
  plot_data <- list(predMatrix[site, kinases], phosScoringMatrices$combinedScoreMatrix[site, kinases],
                   phosScoringMatrices$motifScoreMatrix[site, kinases], phosScoringMatrices$profileScoreMatrix[site, kinases])
  plot_types <- c("Prediction score", "Combined score", "Motif score", "Profile score")
  plot_colors <- c("red3", "orange2", "green4", "lightblue3")
  
  plots <- list()
  
  for (i in 1:4) {
    df <- data.frame(Kinase = factor(kinases, levels = kinases), Value = plot_data[[i]])
    
    p <- ggplot(df, aes(x = Kinase, y = Value, fill = factor(plot_types[i]))) +
      geom_col() +
      coord_flip() +
      scale_fill_manual(values = plot_colors[i], guide = "none") +
      theme_classic() +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_text(size = 4),
            axis.title.x = element_text(size = 0),
            plot.title = element_text(hjust = 0.5, size = 7),
            axis.text.x.top = element_text(angle = 45, hjust = 1)) +
      labs(title = plot_types[i], x = NULL) +
      scale_x_discrete(position = "top") +
      scale_y_continuous(expand = expansion(mult = c(0.1, 0)), limits = c(0, 1),breaks = c(0,1))
    
    plots[[i]] <- p
  }
  title1=text_grob(paste(site), size = 9, face = "bold")   #### this worked for me

  grid.arrange(grobs = plots, ncol = 4, top = title1)
}


plotSignalomeMap_modified <- function(signalomes, color) {
    df <- stack(signalomes$kinaseSubstrates)
    modules <- signalomes$proteinModule
    names(modules) <- unlist(lapply(strsplit(as.character(names(signalomes$proteinModules)), ";"), "[[", 1))
    df$cluster <- modules[df$values]
    df_balloon <- df
    df_balloon <- na.omit(df_balloon) %>% dplyr::count(.data$cluster, .data$ind)
    df_balloon$ind <- as.factor(df_balloon$ind)
    df_balloon$cluster <- as.factor(df_balloon$cluster)
    df_balloon <- tidyr::spread(df_balloon, .data$ind, .data$n)[, -1]
    df_balloon[is.na(df_balloon)] <- 0
    df_balloon <- do.call(rbind, lapply(seq(nrow(df_balloon)), function(x) {
        res <- unlist(lapply(df_balloon[x, ], function(y) y/sum(df_balloon[x, ]) * 100))
    }))
    df_balloon <- reshape2::melt(as.matrix(df_balloon))
    colnames(df_balloon) <- c("cluster", "ind", "n")
    df_balloon <- df_balloon[df_balloon$n >= 0, ]
    
    # Function to find the last balloon for each group
last_balloon_y <- function(group_data) {
  max(group_data$y[group_data$x == max(group_data$x)])
}

# Add a new column to the dataframe containing the last balloon's y value for each group
df_balloon$last_y <- sapply(unique(df_balloon$cluster), function(cluster) {
  last_balloon_y(df_balloon[df_balloon$cluster == cluster, ])
})[df_balloon$cluster]


# Function to find the first balloon for each group
first_balloon_y <- function(group_data) {
  min(group_data$y[group_data$x == min(group_data$x)])
}

# Add a new column to the dataframe containing the first balloon's y value for each group
df_balloon$first_y <- sapply(unique(df_balloon$cluster), function(cluster) {
  first_balloon_y(df_balloon[df_balloon$cluster == cluster, ])
})[df_balloon$cluster]  

    g <- ggplot2::ggplot(df_balloon, aes(y = .data$ind, x = .data$cluster)) + 
      
        
         #geom_text(aes(label = .data$cluster, x = .data$cluster, y = 0), angle = 90, hjust = 1, size = 3) +  # Show x-axis labels using geom_text
        scale_color_manual(values = color) + 
        scale_size_continuous(name = "% of phosphosites regulated by a kinase", range = c(2, 17)) + 
        theme_classic() + 
        theme(legend.position = "right", legend.direction = "vertical", legend.title = element_text(angle = 90),
              axis.line = element_blank(), 
              axis.title = element_blank(), 
              axis.text.x = element_blank(),
              axis.text.y = element_text(size = 14),
              panel.grid.major.x = element_blank(), 
              panel.grid.minor.x = element_blank()) +
        guides(col = FALSE)  # Remove the legend for the kinases
    # Add rectangles and text labels for module names on the x-axis
    
    
    g <- g + geom_line(aes(group = .data$cluster, col = .data$ind), size = 0.5, linetype = "solid", color = "grey") +  # Connect the balloons within the horizontal line
      geom_segment(data = df_balloon, aes(x = .data$cluster, xend = .data$cluster, y = .data$first_y, yend = .data$last_y, col = .data$ind), size = 0.5, linetype = "solid", show.legend = FALSE, color = "grey") 
    
# Add rectangles for module names on the x-axis
for (i in unique(df_balloon$cluster)) {
    g <- g + annotate("rect", xmin = as.numeric(i) - 0.45, xmax = as.numeric(i) + 0.45, ymin = -0.05 * max(df_balloon$n), ymax = 0, alpha = 0.7, fill = color[i])
}

    g = g +geom_point(aes(col = .data$ind, size = .data$n)) 
  
    
# Use geom_segment() to draw lines from the x-axis to the last balloon for each group
#g <- g + 
    g
}



```
#Figure 3
## Signalome Formatting
```{r Kinase-Substrate Relationship Analysis, eval=FALSE, include=FALSE, warning=FALSE, message=FALSE}


names_map <- c("20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_1_phospho" = "WT_Endogenous_Rep1",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_2_phospho" = "WT_Endogenous_Rep2",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_3_phospho" = "WT_Endogenous_Rep3",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_4_phospho" = "WT_Rescue_Rep1",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_5_phospho" = "WT_Rescue_Rep2",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_6_phospho" = "WT_Rescue_Rep3",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_13_phospho" = "DTU_Endogenous_Rep1",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_14_phospho" = "DTU_Endogenous_Rep2",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_15_phospho" = "DTU_Endogenous_Rep3",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_16_phospho" = "DTU_Rescue_Rep1",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_17_phospho" = "DTU_Rescue_Rep2",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_18_phospho" = "DTU_Rescue_Rep3",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_25_phospho" = "CS_Endogenous_Rep1",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_26_phospho" = "CS_Endogenous_Rep2",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_27_phospho" = "CS_Endogenous_Rep3",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_28_phospho" = "CS_Rescue_Rep1",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_29_phospho" = "CS_Rescue_Rep2",
               "20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_30_phospho" = "CS_Rescue_Rep3")
old_colnames <- colnames(Keratinocyte_Phosphoproteome_2024)[1:18]
names_map <- c(names_map, setdiff(old_colnames, names(names_map)))
# Use the names_map to rename the columns
colnames(Keratinocyte_Phosphoproteome_2024)[1:18] <- names_map[old_colnames]
renamed_df = Keratinocyte_Phosphoproteome_2024
your_dataframe <- renamed_df %>%
  mutate(Column_3 = str_extract(PTM_collapse_key, "(?<=_).*?(?=_)"),
         Combined_Column = paste(PG.UniProtIds, PG.Genes, Column_3, PEP.StrippedSequence, sep=";"))
your_dataframe <- your_dataframe %>%
  distinct(Combined_Column, .keep_all = TRUE)

ppe <- your_dataframe 
class(ppe)
dim((ppe))
ppe_matrix <- as.matrix(ppe)
grps = gsub("_Rep[0-9]", "", colnames(ppe_matrix[,c(1:18)]))


rownames(ppe_matrix) = unique(ppe_matrix[,"Combined_Column"])


ppe_matrix = ppe_matrix[,c(1:18)]
ppe_filtered <- selectGrps(ppe_matrix, grps, 0.7, n=1) 
rownames_original <- rownames(ppe_filtered)

ppe_filtered <- apply(ppe_filtered, 2, as.numeric)


rownames(ppe_filtered) <- rownames_original


ppe_filter_log = na.omit(((log2(ppe_filtered))))
dim(ppe_filter_log)


FASTA = reformat_fasta_df(uniprot.proteome_Human)

named_FASTA <- fasta_to_named_list(FASTA)

strip_phos_site <- function(GOI) {
     gene_IDs <- gsub("_.*", "", GOI)
    return(gene_IDs)
}
#Assign flanking sequence to phos site instead of tryptic peptide
rownames(ppe_filter_log) = extract_flanking_seq(named_FASTA,rownames(ppe_filter_log))

ppe_filter_log = as.data.frame(ppe_filter_log)

# Create a data.frame with the rownames as a new column
ppe_filter_log_with_id <- ppe_filter_log %>%
  rownames_to_column(var = "ID")

# Modify the ID column to remove the ".1" at the end of the ID if it exists
ppe_filter_log_with_id$ID <- gsub("(\\.1)$", "", ppe_filter_log_with_id$ID)

# Group by the modified ID column and calculate the mean for each group
ppe_filter_log_mean <- ppe_filter_log_with_id %>%
  group_by(ID) %>%
  summarise_all(mean)
# Restore the rownames from the ID column
ppe_filter_log_mean_matrix <- as.matrix(ppe_filter_log_mean)
rownames(ppe_filter_log_mean_matrix) <- ppe_filter_log_mean_matrix[,1]

# Convert columns to numeric using apply()
numeric_columns <- apply(ppe_filter_log_mean_matrix, 2, as.numeric)
# Create a new data frame or matrix with the numeric columns and original rownames
numeric_ppe_filter_log <- as.matrix(numeric_columns)
rownames(numeric_ppe_filter_log) <- rownames(ppe_filter_log_mean_matrix)

ppe_filter_log_mean_matrix = numeric_ppe_filter_log
ppe_filter_log_mean_matrix <- ppe_filter_log_mean_matrix[,-1,drop=FALSE]
# Convert the data frame to a matrix
ppe_filter_log = ppe_filter_log_mean_matrix
rownames(ppe_filter_log) <- gsub(pattern = "\\.", replacement = ";", x = rownames(ppe_filter_log))

#Re iterate to get the flanking sequence of doubles and tryptic peptides
rownames(ppe_filter_log) = extract_flanking_seq(named_FASTA,rownames(ppe_filter_log))

ppe_filter_log = as.data.frame(ppe_filter_log)

# Create a data.frame with the rownames as a new column
ppe_filter_log_with_id <- ppe_filter_log %>%
  rownames_to_column(var = "ID")

# Modify the ID column to remove the ".1" at the end of the ID if it exists
ppe_filter_log_with_id$ID <- gsub("(\\.1)$", "", ppe_filter_log_with_id$ID)

# Group by the modified ID column and calculate the mean for each group
ppe_filter_log_mean <- ppe_filter_log_with_id %>%
  group_by(ID) %>%
  summarise_all(mean)
# Restore the rownames from the ID column
ppe_filter_log_mean_matrix <- as.matrix(ppe_filter_log_mean)
rownames(ppe_filter_log_mean_matrix) <- ppe_filter_log_mean_matrix[,1]

# Convert columns to numeric using apply()
numeric_columns <- apply(ppe_filter_log_mean_matrix, 2, as.numeric)
# Create a new data frame or matrix with the numeric columns and original rownames
numeric_ppe_filter_log <- as.matrix(numeric_columns)
rownames(numeric_ppe_filter_log) <- rownames(ppe_filter_log_mean_matrix)

ppe_filter_log_mean_matrix = numeric_ppe_filter_log
ppe_filter_log_mean_matrix <- ppe_filter_log_mean_matrix[,-1,drop=FALSE]
# Convert the data frame to a matrix
ppe_filter_log = ppe_filter_log_mean_matrix
rownames(ppe_filter_log) <- gsub(pattern = "\\.", replacement = ";", x = rownames(ppe_filter_log))

rownames_split <- strsplit(rownames(ppe_filter_log), ";")
uniprot <- sapply(rownames_split, "[", 1)
gene_symbols <- sapply(rownames_split, "[", 2)
sites <- gsub("[STY]", "", sapply(rownames_split, "[", 3))
sequences <- sapply(rownames_split, "[", 4)
residues <- gsub("[0-9]", "", sapply(rownames_split, "[", 3))
# Create PhosphoExperiment object

ppe_noSerum <- PhosphoExperiment(assays = list(Quantification = ppe_filter_log),UniprotID = uniprot, Site = sites, GeneSymbol = gene_symbols, Residue = residues, Sequence = sequences)


ppe = ppe_noSerum

```

##QC 
###CorrPlot
Quality control 1. Corrplot phos 2. Corrplot proteome
```{r}

# Read the data
sampleCorrMatrix_global_SN <- read.delim2("sampleCorrelationMatrix_global.tsv")

# Define the names map
names_map_global <- c(
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_1.raw" = "WT_Endogenous_Rep1",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_2.raw" = "WT_Endogenous_Rep2",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_3.raw" = "WT_Endogenous_Rep3",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_4.raw" = "WT_Rescue_Rep1",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_5.raw" = "WT_Rescue_Rep2",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_6.raw" = "WT_Rescue_Rep3",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_13.raw" = "DTU_Endogenous_Rep1",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_14.raw" = "DTU_Endogenous_Rep2",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_15.raw" = "DTU_Endogenous_Rep3",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_16.raw" = "DTU_Rescue_Rep1",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_17.raw" = "DTU_Rescue_Rep2",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_18.raw" = "DTU_Rescue_Rep3",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_25.raw" = "CS_Endogenous_Rep1",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_26.raw" = "CS_Endogenous_Rep2",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_27.raw" = "CS_Endogenous_Rep3",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_28.raw" = "CS_Rescue_Rep1",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_29.raw" = "CS_Rescue_Rep2",
  "X20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_30.raw" = "CS_Rescue_Rep3"
)

# Rename the columns
colnames(sampleCorrMatrix_global_SN) <- names_map_global[colnames(sampleCorrMatrix_global_SN)]
sampleCorrMatrix_global_SN <- sampleCorrMatrix_global_SN[,-1]

# Convert the character matrix to a numeric matrix
sampleCorrMatrix_global_SN_numeric <- apply(sampleCorrMatrix_global_SN, 2, as.numeric)

# Check the structure of the new matrix
str(sampleCorrMatrix_global_SN_numeric)

# If it's now a numeric matrix, you can plot it with corrplot
if (is.numeric(sampleCorrMatrix_global_SN_numeric)) {
  corrplot(sampleCorrMatrix_global_SN_numeric, method = "color")
}

col <- colorRampPalette(c(rgb(0,0,1, alpha=0.5), rgb(1,0,0, alpha=0.5)))(200)
rownames(sampleCorrMatrix_global_SN_numeric) <- colnames(sampleCorrMatrix_global_SN_numeric)

pdf("CorrplotProteome.pdf",width = 4, height = 4)
corrplot(sampleCorrMatrix_global_SN_numeric, method = "color", type = "upper", order = "original", 
         tl.col = "black", tl.srt = 45, tl.cex = 0.6, cl.cex = 0.6, is.corr = FALSE, col = col, 
         title = "Total Protein Levels Correlation")
dev.off()

sampleCorrMatrix_phos_SN <- read.delim2("sampleCorrelationMatrix_phospho.tsv")

# Remove the first column
sampleCorrMatrix_phos_SN <- sampleCorrMatrix_phos_SN[,-1]

# Define the names map
names_map_phos <- c(
  "X" = "X",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_1_phospho.raw" = "WT_Endogenous_Rep1",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_2_phospho.raw" = "WT_Endogenous_Rep2",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_3_phospho.raw" = "WT_Endogenous_Rep3",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_4_phospho.raw" = "WT_Rescue_Rep1",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_5_phospho.raw" = "WT_Rescue_Rep2",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_6_phospho.raw" = "WT_Rescue_Rep3",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_13_phospho.raw" = "DTU_Endogenous_Rep1",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_14_phospho.raw" = "DTU_Endogenous_Rep2",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_15_phospho.raw" = "DTU_Endogenous_Rep3",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_16_phospho.raw" = "DTU_Rescue_Rep1",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_17_phospho.raw" = "DTU_Rescue_Rep2",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_18_phospho.raw" = "DTU_Rescue_Rep3",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_25_phospho.raw" = "CS_Endogenous_Rep1",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_26_phospho.raw" = "CS_Endogenous_Rep2",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_27_phospho.raw" = "CS_Endogenous_Rep3",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_28_phospho.raw" = "CS_Rescue_Rep1",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_29_phospho.raw" = "CS_Rescue_Rep2",
  "X20221127_VC_140min_noFAIMS_1ug_HRMS1_DIA_sample_30_phospho.raw" = "CS_Rescue_Rep3"
)

# Convert the character matrix to a numeric matrix
sampleCorrMatrix_phos_SN_numeric <- apply(sampleCorrMatrix_phos_SN, 2, as.numeric)

# Rename the columns
colnames(sampleCorrMatrix_phos_SN_numeric) <- names_map_phos[colnames(sampleCorrMatrix_phos_SN_numeric)]

# Create the color palette
col <- colorRampPalette(c(rgb(0,0,1, alpha=0.5), rgb(1,0,0, alpha=0.5)))(200)
rownames(sampleCorrMatrix_phos_SN_numeric) <- colnames(sampleCorrMatrix_phos_SN_numeric)

# Create correlation plots

```

###PieCharts
PieChart for S/T/Y and for multiple phosphorylated  peptide
```{r}
# Create a new column that indicates whether PTM_collapse_key contains "S", "T", or "Y"
renamed_df_test_pie <- renamed_df_test %>%
  mutate(PTM_type = case_when(
    str_detect(PTM_collapse_key, "S") ~ "S",
    str_detect(PTM_collapse_key, "T") ~ "T",
    str_detect(PTM_collapse_key, "Y") ~ "Y",
    TRUE ~ "Other"
  ))

# renamed_df_test_pie <- renamed_df_test_pie %>%
#   filter(!str_detect(PTM_collapse_key, "M[23]"))
renamed_df_test_pie <- renamed_df_test_pie %>%
  group_by(PTM_type) %>%
  summarise(n = n())

## Compute the position of labels
renamed_df_test_pie <- renamed_df_test_pie %>%
  arrange(desc(PTM_type)) %>%
  mutate(prop = n / sum(n) * 100) %>%
  mutate(ypos = cumsum(prop) - 0.5 * prop)

# Create a pie chart for S/T/Y
# Create a pie chart

pSTY = ggplot(renamed_df_test_pie, aes(x = "", y = prop, fill = PTM_type)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +
  theme(legend.position = "bottom") +
  geom_text(aes(y = ypos, label = n), color = "white", size = 6) +
  scale_fill_brewer(palette = "Set2") +
  ggtitle("S/T/Y Relevant Phosphorylation Site") +
  theme(plot.title = element_text(size = 20))


#### Multiple phosphorylated peptides

# Filter the data
filtered_df <- renamed_df_test%>%
  mutate(PTM_collapse_key = str_extract(PTM_collapse_key, "M[123]$")) %>%
  filter(!is.na(PTM_collapse_key))

# Compute the position of labels
filtered_df <- filtered_df %>%
  group_by(PTM_collapse_key) %>%
  summarise(n = n()) %>%
  arrange(desc(PTM_collapse_key)) %>%
  mutate(prop = n / sum(n) * 100) %>%
  mutate(ypos = cumsum(prop) - 0.5 * prop)


# Create a pie chart
pPHOS = ggplot(filtered_df, aes(x = "", y = prop, fill = PTM_collapse_key)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +
  theme(legend.position = "bottom") +
  geom_text(aes(y = ypos, label = n), color = "white", size = 6) +
  scale_fill_brewer(palette = "Set2", labels = c("M1" = "Single Phosphorylated \nPeptides", "M2" = "Double Phosphorylated \nPeptides", "M3" = "Multiple Phosphorylated \nPeptides")) +
  ggtitle("Single/Double/Multiple Phosphorylated Peptides") +
  theme(plot.title = element_text(size = 20)) +
  labs(fill = "Phosphorylation \nMultiplicity")

```

### Venn-Diagram
Venn diagram Phos and proteome. Do the diagrams on quantified phos-sites. Also on the proteome
ppe_filtered is the one with 0.7 in min 1 samples. Number is 14774 in both endogenous and rescue samples.

Another approach. make the venn diagram with Keratinocyte_Phosphoproteome_2024 which has 15607 quantified phos sites.
```{r}

# Convert the columns to numeric
Keratinocyte_Phosphoproteome_2024[, c(1:3, 7:9, 13:15)] <- lapply(Keratinocyte_Phosphoproteome_2024[, c(1:3, 7:9, 13:15)], as.numeric)

# Identify the p-sites in each condition
endogenous_p_sites <- list(
  WT = which(!is.na(rowMeans(Keratinocyte_Phosphoproteome_2024[, c(1:3)], na.rm = TRUE))),
  KO_DTU = which(!is.na(rowMeans(Keratinocyte_Phosphoproteome_2024[, c(7:9)], na.rm = TRUE))),
  KO_CS = which(!is.na(rowMeans(Keratinocyte_Phosphoproteome_2024[, c(13:15)], na.rm = TRUE)))
)
names(endogenous_p_sites) <- ifelse(names(endogenous_p_sites) == "WT", "DMKN αβγ WT",
                                    ifelse(names(endogenous_p_sites) == "KO_DTU", "DMKN βγ-/-",
                                           ifelse(names(endogenous_p_sites) == "KO_CS", "DMKN αβ-/-", names(endogenous_p_sites))))


# Convert the columns to numeric
Keratinocyte_Phosphoproteome_2024[, c(4:6, 10:12, 16:18)] <- lapply(Keratinocyte_Phosphoproteome_2024[, c(4:6, 10:12, 16:18)], as.numeric)

# Identify the p-sites in each condition
treated_p_sites <- list(
  WT = which(!is.na(rowMeans(Keratinocyte_Phosphoproteome_2024[, c(4:6)], na.rm = TRUE))),
  KO_DTU = which(!is.na(rowMeans(Keratinocyte_Phosphoproteome_2024[, c(10:12)], na.rm = TRUE))),
  KO_CS = which(!is.na(rowMeans(Keratinocyte_Phosphoproteome_2024[, c(16:18)], na.rm = TRUE)))
)
names(treated_p_sites) <- ifelse(names(treated_p_sites) == "WT", "DMKN αβγ WT",
                                    ifelse(names(treated_p_sites) == "KO_DTU", "DMKN βγ-/-",
                                           ifelse(names(treated_p_sites) == "KO_CS", "DMKN αβ-/-", names(treated_p_sites))))
# Create the Venn diagrams
# Create the Venn diagrams
# ggVennDiagram(endogenous_p_sites, fill = c("transparent", "transparent", "transparent")) +
#   ggtitle("Endogenous Conditions")
# 
# ggVennDiagram(treated_p_sites, fill = c("transparent", "transparent", "transparent")) +
#   ggtitle("Treated Conditions")
colors <- c("red", "green", "blue")
endogenous_setsVENNS = ggvenn(endogenous_p_sites, fill_color = colors, stroke_size = 1, set_name_size = 4) +
  ggtitle("Endogenous Conditions") 
treated_setsVENNS = ggvenn(treated_p_sites, fill_color = colors, stroke_size = 1, set_name_size = 4) +
  ggtitle("Treated Conditions") 



# Define a list of sets
endogenous_sets <- list(
  WT_Endogenous = which(!is.na(rowMeans(global_PG_QUANT_test[, c("WT_Endogenous_1", "WT_Endogenous_2", "WT_Endogenous_3")], na.rm = TRUE))),
  DTU_Endogenous = which(!is.na(rowMeans(global_PG_QUANT_test[, c("DTU_Endogenous_1", "DTU_Endogenous_2", "DTU_Endogenous_3")], na.rm = TRUE))),
  CS_Endogenous = which(!is.na(rowMeans(global_PG_QUANT_test[, c("CS_Endogenous_1", "CS_Endogenous_2", "CS_Endogenous_3")], na.rm = TRUE)))
)
names(endogenous_sets) <- ifelse(names(endogenous_sets) == "WT_Endogenous", "DMKN αβγ WT",
                                    ifelse(names(endogenous_sets) == "DTU_Endogenous", "DMKN βγ-/-",
                                           ifelse(names(endogenous_sets) == "CS_Endogenous", "DMKN αβ-/-", names(endogenous_sets))))

# Define a list of sets
treated_sets <- list(
  WT_Treated = which(!is.na(rowMeans(global_PG_QUANT_test[, c("WT_Treated_1", "WT_Treated_2", "WT_Treated_3")], na.rm = TRUE))),
  DTU_Treated = which(!is.na(rowMeans(global_PG_QUANT_test[, c("DTU_Treated_1", "DTU_Treated_2", "DTU_Treated_3")], na.rm = TRUE))),
  CS_Treated = which(!is.na(rowMeans(global_PG_QUANT_test[, c("CS_Treated_1", "CS_Treated_2", "CS_Treated_3")], na.rm = TRUE)))
)

# Rename the sets
names(treated_sets) <- ifelse(names(treated_sets) == "WT_Treated", "DMKN αβγ WT",
                              ifelse(names(treated_sets) == "DTU_Treated", "DMKN βγ-/-",
                                     ifelse(names(treated_sets) == "CS_Treated", "DMKN αβ-/-", names(treated_sets))))




endogenous_setsVENNS = ggvenn(endogenous_sets, fill_color = colors, stroke_size = 1, set_name_size = 4) +
  ggtitle("Endogenous Conditions") 

# Create the Venn diagrams
treated_setsVENNS = ggvenn(treated_sets, fill_color = colors, stroke_size = 1, set_name_size = 4) +
  ggtitle("Treated Conditions")


```

### Number Bargraph
```{r}
# Create a data frame
df_numbers <- data.frame(
  Names = c("Phosphosites after loc. prob. > 0.75", "Phosphosites > 0.7 in min. n > 1", "Fully Quantified Phosphosites"),
  Values = c(nrow(Keratinocyte_Phosphoproteome_2024[complete.cases(Keratinocyte_Phosphoproteome_2024$PTM_collapse_key), ]), nrow(ppe_filtered), nrow(ppe_filter_log))
)
df_numbers$Names <- fct_reorder(df_numbers$Names, df_numbers$Values, .desc = TRUE)

# Create a bar graph
# Create a bar graph

# Create a bar graph
# Create a bar graph
BarNumberS= ggplot(df_numbers, aes(x = Names, y = Values, fill = Names)) +
  geom_bar(stat = "identity", color = "black") +
  geom_text(aes(label = Values), vjust = -0.3, size = 2) +
  scale_fill_manual(values = c("black", "darkgrey", "grey")) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 6, face = "bold"),
    axis.text.y = element_text(size = 6, face = "bold"),
    axis.title = element_text(size = 6, face = "bold"),
    panel.background = element_blank(),
    plot.background = element_blank()
  ) +
  xlab("") +
  ylab("Number of Phosphosites")

```

```{r}
process_signalomes_results <- function(Signalomes_results_DTU_Up) {
  # Convert the character vector into a data frame
  signalomes_results_DTU_Up_df <- data.frame(gene_and_phos_site = names(Signalomes_results_DTU_Up$proteinModules),
                                             module_number = ifelse(Signalomes_results_DTU_Up$proteinModules == "noModule", NA, as.numeric(Signalomes_results_DTU_Up$proteinModules)),
                                             stringsAsFactors = FALSE)

  # Remove rows with NA module_number
  signalomes_results_DTU_Up_df <- signalomes_results_DTU_Up_df[!is.na(signalomes_results_DTU_Up_df$module_number), ]

  # Create a list to store the new data frames
  module_dfs <- list()

  # Iterate through the unique module numbers and create a data frame for each module
  for (module_number in unique(signalomes_results_DTU_Up_df$module_number)) {
    module_subset <- signalomes_results_DTU_Up_df[signalomes_results_DTU_Up_df$module_number == module_number, "gene_and_phos_site"]
    module_dfs[[paste0("module_", module_number)]] <- data.frame(gene_and_phos_site = module_subset)
  }

  convert_to_entrez <- function(gene_and_phos_site) {
    # Extract gene names
    gene_names <- gsub(" .*", "", gene_and_phos_site)
  
    # Convert gene names to Entrez IDs
    entrez_ids <- mapIds(org.Hs.eg.db,
                         keys = gene_names,
                         column = "ENTREZID",
                         keytype = "SYMBOL",
                         multiVals = "first")
  
    # Remove NA values
    entrez_ids <- entrez_ids[!is.na(entrez_ids)]
  
    return(entrez_ids)
}
  # Create a new list to store the Entrez IDs as character vectors
  module_entrez_ids_chr <- list()

  # Iterate through each module and convert gene names to Entrez IDs
  for (module_name in names(module_dfs)) {
    module_entrez_ids_chr[[module_name]] <- as.character(convert_to_entrez(gsub(" .*", "", module_dfs[[module_name]]$gene_and_phos_site)))
  }

  return(module_entrez_ids_chr)
}
```

## Signalomics
```{r warning=FALSE}
ppe = ppe_noSerum 
phosphoL6 = (SummarizedExperiment::assay(ppe, "Quantification")) # IS 3997 sites! If not iterate the flanking annotation
# Define the desired order
desired_order <- c("WT_Endogenous_Rep1", "WT_Endogenous_Rep2", "WT_Endogenous_Rep3", 
                   "WT_Rescue_Rep1", "WT_Rescue_Rep2", "WT_Rescue_Rep3",
                   "DTU_Endogenous_Rep1", "DTU_Endogenous_Rep2", "DTU_Endogenous_Rep3",
                   "DTU_Rescue_Rep1", "DTU_Rescue_Rep2", "DTU_Rescue_Rep3",
                   "CS_Endogenous_Rep1", "CS_Endogenous_Rep2", "CS_Endogenous_Rep3",
                   "CS_Rescue_Rep1", "CS_Rescue_Rep2", "CS_Rescue_Rep3")

# Reorder the columns
phosphoL6 <- phosphoL6[, desired_order]
grps = gsub("_Rep[0-9]", "", colnames(ppe))

# Fit the model and contrasts
design = model.matrix(~ grps - 1)
colnames(design) <- c("KO_CS_NoSerum_Control", "KO_CS_NoSerum_Treated", "KO_DTU_NoSerum_Control", "KO_DTU_NoSerum_Treated", "WT_NoSerum_Control", "WT_NoSerum_Treated")
# Update the contrasts for NoSerum data
contrasts <- makeContrasts(
  KO_WT_CS_NoSerum_fold_change = WT_NoSerum_Control- KO_CS_NoSerum_Control,
  KO_WT_DTU_NoSerum_fold_change = WT_NoSerum_Control- KO_DTU_NoSerum_Control,
  KO_CS_NoSerum_fold_change = KO_CS_NoSerum_Treated - KO_CS_NoSerum_Control,
  KO_DTU_NoSerum_fold_change = KO_DTU_NoSerum_Treated - KO_DTU_NoSerum_Control,
  KO_CS_control_WT_control_foldchange = KO_CS_NoSerum_Control - WT_NoSerum_Control,
  KO_DTU_control_WT_control_foldchange = KO_DTU_NoSerum_Control - WT_NoSerum_Control,
  TreatmentEffect_NoSerum_WT = WT_NoSerum_Treated - WT_NoSerum_Control,
  GenotypeTreatmentEffect_NoSerum_DTU = KO_DTU_NoSerum_Treated - WT_NoSerum_Control,
  GenotypeTreatmentEffect_NoSerum_CS = KO_CS_NoSerum_Treated - WT_NoSerum_Control,
  InteractionEffect_CS = (KO_CS_NoSerum_Treated - WT_NoSerum_Treated) - (KO_CS_NoSerum_Control - WT_NoSerum_Control),
  InteractionEffect_DTU = (KO_DTU_NoSerum_Treated - WT_NoSerum_Treated) - (KO_DTU_NoSerum_Control - WT_NoSerum_Control),
  WT_NoSerum_Control = WT_NoSerum_Control - WT_NoSerum_Control,
  levels = design
)


fit <- lmFit(SummarizedExperiment::assay(ppe, "Quantification"), design)
fit2 <- contrasts.fit(fit, contrasts)
fit2 <- eBayes(fit2)

# Updated tables
table_names <- colnames(coef(fit2))
tables <- lapply(table_names, function(x) topTable(fit2, number=Inf, coef=x))

# Without relevant Fold change and p value filters
idx_Up = fit2$coefficients[,c( "KO_WT_CS_NoSerum_fold_change")] > -Inf


# Subset 'ppe' based on 'idx_Up' and 'idx_Down'

phosphoL6.reg_Up <- (SummarizedExperiment::assay(ppe[idx_Up, ], "Quantification"))

desired_order <- c("WT_Endogenous_Rep1", "WT_Endogenous_Rep2", "WT_Endogenous_Rep3", 
                   "WT_Rescue_Rep1", "WT_Rescue_Rep2", "WT_Rescue_Rep3",
                   "DTU_Endogenous_Rep1", "DTU_Endogenous_Rep2", "DTU_Endogenous_Rep3",
                   "DTU_Rescue_Rep1", "DTU_Rescue_Rep2", "DTU_Rescue_Rep3",
                   "CS_Endogenous_Rep1", "CS_Endogenous_Rep2", "CS_Endogenous_Rep3",
                   "CS_Rescue_Rep1", "CS_Rescue_Rep2", "CS_Rescue_Rep3")

# Reorder the columns
phosphoL6.reg_Up <- phosphoL6.reg_Up[, desired_order]

L6.phos.std_Up <- standardise(phosphoL6.reg_Up)
#L6.phos.std_Down <- standardise(phosphoL6.reg_Down)

rownames(L6.phos.std_Up) <- paste0(GeneSymbol(ppe), ";", Residue(ppe), Site(ppe), ";")[idx_Up]
#rownames(L6.phos.std_Down) <- paste0(GeneSymbol(ppe), ";", Residue(ppe), Site(ppe), ";")[idx_Down]

L6.phos.seq_Up <- Sequence(ppe)[idx_Up]
#L6.phos.seq_Down <- Sequence(ppe)[idx_Down]

# Check for empty or missing sequences in L6.phos.seq; absolutely necessary to run. There is a missing seq somewhere
empty_or_missing_or_H1_seqs_Up <- sapply(L6.phos.seq_Up, function(x) x == "" || is.na(x) || grepl("S[0-9]", x))
L6.phos.seq_Up <- L6.phos.seq_Up[!empty_or_missing_or_H1_seqs_Up]
L6.phos.std_Up <- L6.phos.std_Up[!empty_or_missing_or_H1_seqs_Up,]



L6.matrices_Up_CS <- kinaseSubstrateScore(substrate.list = PhosphoSite.human, 
                                    mat = L6.phos.std_Up, seqs = L6.phos.seq_Up, 
                                    numMotif = 5, numSub = 1, verbose = FALSE, species = "human")


rownames(L6.matrices_Up_CS$combinedScoreMatrix) = gsub(";", " ", rownames(L6.matrices_Up_CS$combinedScoreMatrix))
rownames(L6.matrices_Up_CS$profileScoreMatrix) = gsub(";", " ", rownames(L6.matrices_Up_CS$profileScoreMatrix))
rownames(L6.matrices_Up_CS$motifScoreMatrix) = gsub(";", " ", rownames(L6.matrices_Up_CS$motifScoreMatrix))
rownames(L6.matrices_Up_CS$ksActivityMatrix) = gsub(";", " ", rownames(L6.matrices_Up_CS$ksActivityMatrix))

library(PhosR)
data("KinaseFamily", package = "PhosR")

kinaseHeatmap_Up_CS = (kinaseSubstrateHeatmap_modified(L6.matrices_Up_CS, top =1))


motifScore_Up_CS <- L6.matrices_Up_CS$motifScoreMatrix
profileScore_Up_CS <- L6.matrices_Up_CS$profileScoreMatrix
combinedScore_Up_CS <- L6.matrices_Up_CS$combinedScoreMatrix
kinaseActivityScore_Up_CS <- L6.matrices_Up_CS$ksActivityMatrix


L6.predMat_Up_CS <- kinaseSubstratePred(L6.matrices_Up_CS, cs = 0.5, top = 50, inclusion = 20, iter= 5, verbose = FALSE)


# ksActivityScore violin plots
reshaped_data <- melt(L6.matrices_Up_CS$ksActivityMatrix, variable.name = "Condition", value.name = "Activity")
# Convert Var2 to character type and split into two parts: Genotype and Treatment
reshaped_data$Var2 <- as.character(reshaped_data$Var2)
reshaped_data$Genotype <- sapply(strsplit(reshaped_data$Var2, "_"), function(x) {
  if (x[1] == "WT") {
    return(x[1])
  } else {
    return(x[1])
  }
})
reshaped_data$Treatment <- sapply(strsplit(reshaped_data$Var2, "_"), function(x) {
  if (x[2] %in% c("Endogenous", "Rescue")) {
    return(x[2])
  } else {
    return(x[2])
  }
})
# Replace the values in the Genotype and Treatment columns
reshaped_data$Genotype[reshaped_data$Genotype == "WT"] <- "WT"
reshaped_data$Genotype[reshaped_data$Genotype == "DTU"] <- "DMKN \U03B2\U03B3-/-"
reshaped_data$Genotype[reshaped_data$Genotype == "CS"] <- "DMKN \U03B1\U03B2-/-"

reshaped_data$Treatment[reshaped_data$Treatment == "Control"] <- "Endogenous"
reshaped_data$Treatment[reshaped_data$Treatment == "Treated"] <- "Rescue"
reshaped_data$Genotype <- factor(reshaped_data$Genotype, levels = c("WT", "DMKN \U03B2\U03B3-/-", "DMKN \U03B1\U03B2-/-"))
reshaped_data$Treatment <- as.factor(reshaped_data$Treatment)

ggplot(reshaped_data, aes(x = Genotype, y = Activity, fill = Treatment)) +
  geom_violin() +
  facet_wrap(~ Var1)  # Var1 is the kinase

# Create the plot including ANOVA and pairwise t-tests
ggplot(reshaped_data, aes(x = Genotype, y = Activity, fill = Treatment)) +
  geom_violin() +
  facet_wrap(~ Var1) +
  stat_compare_means(method = "anova", label.y = 3) +      # Add global p-value
  stat_compare_means(label = "p.signif", method = "t.test",
                     ref.group = ".all.")    

# Pairwise comparison against each treatment plus KRUSKAL WALIS test for genotype
ggplot(reshaped_data, aes(x = Genotype, y = Activity, fill = Treatment)) +
    geom_violin(width = 0.7, alpha = 0.9, color = "black") +
    ggforce::geom_sina() +
    facet_wrap(~ Var1) +
    stat_compare_means(aes(group = Genotype), method = "kruskal.test", label.y = 4.5, label.size = 6) +
    stat_compare_means(aes(group = Treatment), method = "t.test", label.y = 3.5, label.size = 6, label = "p.signif") +  # For p-value labels

    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
          axis.text.y = element_text(size = 12),
          strip.text = element_text(size = 14, face = "bold"),
          legend.title = element_text(size = 14, face = "bold"),
          legend.text = element_text(size = 12)) +
    labs(x = "Genotype", y = "Kinase Activity Score", fill = "Treatment")

# Perform pairwise t-tests for each Genotype and Kinase
kruskal_results <- reshaped_data %>%
  group_by(Var1) %>%
  do({
    data.frame(p_value = kruskal.test(.$Activity ~ .$Genotype)$p.value)
  })
anova_results <- reshaped_data %>%
  group_by(Var1) %>%
  do({
    data.frame(p_value = summary(aov(.$Activity ~ .$Genotype))[[1]]["Pr(>F)"][1,])
  })
# Perform pairwise t-test for each Treatment and Kinase
ttest_results <- reshaped_data %>%
  group_by(Var1) %>%
  do({
    p_matrix <- pairwise.t.test(.$Activity, .$Treatment, p.adjust.method = "BH")$p.value
    data.frame(Treatment1 = rownames(p_matrix), Treatment2 = colnames(p_matrix), p_value = as.vector(p_matrix))
  })


# Filter the kinases where the p-value is significant in either test
significant_kinases <- anova_results %>% 
  filter(p_value < 0.05) %>% 
  .$Var1 %>% 
  unique()

# Filter the reshaped_data to include only the significant kinases
reshaped_data <- reshaped_data %>%
  filter(Var1 %in% significant_kinases)



ksActivityScore = ggplot(reshaped_data, aes(x = Genotype, y = Activity, fill = Treatment)) +
    geom_violin(width = 0.7, alpha = 0.9, color = "black", size =0.2)+
    ggforce::geom_sina(size = 0.1)+
    facet_wrap(~ Var1) +
    stat_compare_means(aes(group = Genotype), method = "aov", label.y = 2.5, size = 1.2) +
    stat_compare_means(aes(group = Treatment), method = "t.test", label.y = 1.8, size = 2, label = "p.signif", hide.ns = T) +  # For p-value labels

    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6),
          axis.text.y = element_text(size = 6),
          strip.text = element_text(size = 6, face = "bold"),
          legend.title = element_text(size = 6, face = "bold"),
          legend.text = element_text(size = 6),
          text = element_text(size = 6),
          legend.position = "bottom") +  # Move the legend to the bottom
    labs(x = "Genotype", y = "Kinase Activity Score", fill = "Treatment") 

print(ksActivityScore)




L6.matrices_Up_CS_filter= L6.matrices_Up_CS

# Filter the columns of L6.matrices_Up_CS$combinedScoreMatrix to include only the significant kinases
L6.matrices_Up_CS_filter$combinedScoreMatrix <- L6.matrices_Up_CS_filter$combinedScoreMatrix[, colnames(L6.matrices_Up_CS_filter$combinedScoreMatrix) %in% significant_kinases]
L6.matrices_Up_CS_filter$profileScoreMatrix <- L6.matrices_Up_CS_filter$profileScoreMatrix[, colnames(L6.matrices_Up_CS_filter$profileScoreMatrix) %in% significant_kinases]
L6.matrices_Up_CS_filter$motifScoreMatrix <- L6.matrices_Up_CS_filter$motifScoreMatrix[, colnames(L6.matrices_Up_CS_filter$motifScoreMatrix) %in% significant_kinases]
L6.matrices_Up_CS_filter$ksActivityMatrix <- L6.matrices_Up_CS_filter$ksActivityMatrix[, colnames(L6.matrices_Up_CS_filter$ksActivityMatrix) %in% significant_kinases]

# Filter the columns of L6.predMat_Up_CS to include only the significant kinases
filtered_L6.pred_matrix <- kinaseSubstratePred(L6.matrices_Up_CS_filter, cs = 0.5, top = 50, inclusion = 20, iter= 5, verbose = FALSE)


# Remove rows with missing names from L6.predMat_Up_CS
filtered_L6.pred_matrix <- filtered_L6.pred_matrix[!is.na(rownames(filtered_L6.pred_matrix)), ]
filtered_L6.pred_matrix <- filtered_L6.pred_matrix[!duplicated(rownames(filtered_L6.pred_matrix)), ]



PhosR:::.kinaseNetwork(filtered_L6.pred_matrix, L6.matrices_Up_CS_filter, threskinaseNetwork=0.5, kinase_signalome_color)
PhosR:::.phosphositeClusters(L6.matrices_Up_CS_filter, verbose=T)


Signalomes_results_ENDO_CS_Up_filtered <- Signalomes(KSR=L6.matrices_Up_CS_filter, 
                                predMatrix=filtered_L6.pred_matrix, filter =T,
                                exprsMat=L6.phos.std_Up, module_res = 8,threskinaseNetwork= 0.95,
                                signalomeCutoff = 0.5, KOI = "SRC", verbose = T)



moduleUp_entrez <- process_signalomes_results(Signalomes_results_ENDO_CS_Up_filtered)
max_length <- max(sapply(moduleUp_entrez, length))
module_df <- as.data.frame(matrix(NA, nrow = max_length, ncol = length(moduleUp_entrez)))
colnames(module_df) <- names(moduleUp_entrez)

# Fill the data frame with the IDs from each module
for (module_name in names(moduleUp_entrez)) {
  module_df[1:length(moduleUp_entrez[[module_name]]), module_name] <- moduleUp_entrez[[module_name]]
}


# Convert the wide data frame to a long format
long_module_df <- module_df %>%
  gather(module, Entrez, everything(), na.rm = TRUE)
library(clusterProfiler) ; library(enrichplot) ; library(org.Hs.eg.db)

# Use compareCluster with the reshaped data frame
ENDO_CS_UP_cluster_significant_GO <- compareCluster(Entrez ~ module, data = long_module_df, fun = "enrichGO", OrgDb = org.Hs.eg.db,
                                 ont = "ALL", pAdjustMethod = "fdr", pvalueCutoff = 0.01,
                                 qvalueCutoff = 0.05, minGSSize = 20, readable = TRUE)

# Rename the modules; adjust depending on howm any clusters were generated
new_module_names <- c("1", "2", "3","4", "5", "6", "7", "8")
# Update the Cluster column in the compare_result object
ENDO_CS_UP_cluster_significant_GO@compareClusterResult <- ENDO_CS_UP_cluster_significant_GO@compareClusterResult %>%
  mutate(Cluster = str_replace(Cluster, "module_", ""))

ENDO_CS_UP_cluster_significant_clusterPLOT = dotplot(ENDO_CS_UP_cluster_significant_GO, font.size = 6, size = NULL, x = "GeneRatio",label_format =50, showCategory=3,includeAll = T,split="ONTOLOGY", shape =T)  +
  scale_size_continuous(range = c(1, 4)) + 
   theme( strip.text = element_text(face="bold"), axis.text.x = element_text(face="bold", size =6),
          axis.title.x = element_text(size=6,face="bold" ), 
           legend.key.size = unit(0.5, "cm"),
    legend.text=element_text(size=6),
    legend.position = "bottom",
    legend.box = "vertical",
    text = element_text(size=6),
    strip.background = element_rect()) + labs(x="Gene Ratio") +facet_grid(ONTOLOGY~.,scales = "free")


```

## Connecting kinases to GO
```{r}

# Filter rows where 'Description' contains any of the terms
filtered_GO_terms <- ENDO_CS_UP_cluster_significant_GO@compareClusterResult[grep("cadherin binding|adherens junction", ENDO_CS_UP_cluster_significant_GO@compareClusterResult$Description), ]

# Split 'geneID' column into lists of genes
gene_lists_per_term <- strsplit(filtered_GO_terms$geneID, "/")

# Find the intersecting genes
intersecting_genes_among_terms <- Reduce(intersect, gene_lists_per_term)
all_genes <- unlist(gene_lists_per_term)

# Count the frequency of each gene
gene_frequency <- table(all_genes)

# Convert the table to a data frame and sort by frequency
gene_frequency_df <- data.frame(Gene = names(gene_frequency), Frequency = as.integer(gene_frequency))
gene_frequency_df <- gene_frequency_df[order(-gene_frequency_df$Frequency, gene_frequency_df$Gene), ]
# Get the column names from gene_frequency
all_genes <- names(gene_frequency)

# Filter rows of L6.matrices_Up_CS_filter$combinedScoreMatrix based on all_genes
filtered_score_matrix <- L6.matrices_Up_CS_filter$combinedScoreMatrix[grep(paste(all_genes, collapse="|"), rownames(L6.matrices_Up_CS_filter$combinedScoreMatrix)), ]

# Extract the phosphosite part from the row names of filtered_score_matrix
phosphosites <- sapply(strsplit(rownames(filtered_score_matrix), " "), `[`, 2)
# Create a new data frame to store the results
kinase_sites_df <- data.frame()

# Create phosphosite_df from filtered_score_matrix
phosphosite_df <- data.frame(
  Gene = sapply(strsplit(rownames(filtered_score_matrix), " "), `[`, 1),
  Phosphosite = phosphosites,
  
  stringsAsFactors = FALSE
)
# Loop over the kinaseSubstrates list
for (kinase in names(Signalomes_results_ENDO_CS_Up_filtered$kinaseSubstrates)) {
  # Get the substrates for the current kinase
  kinase_substrates <- Signalomes_results_ENDO_CS_Up_filtered$kinaseSubstrates[[kinase]]
  
  # Loop over the rows of phosphosite_df
  for (i in 1:nrow(phosphosite_df)) {
    # Create a string that matches the format in kinaseSubstrates
    phosphosite_string <- paste0(phosphosite_df$Gene[i], " ", phosphosite_df$Phosphosite[i], " ")
    
    # Check if phosphosite_string is in kinase_substrates
    if (phosphosite_string %in% kinase_substrates) {
      # If it is, add a row to kinase_sites_df
      kinase_sites_df <- rbind(kinase_sites_df, data.frame(Kinase=kinase, Gene=phosphosite_df$Gene[i], Phosphosite=phosphosite_df$Phosphosite[i]))
    }
  }
}
# Get the cluster information
clusters <- Signalomes_results_ENDO_CS_Up_filtered$proteinModules

# Split the names of clusters into Gene and Phosphosite
cluster_info <- data.frame(Gene = sapply(strsplit(names(clusters), " "), `[`, 1), 
                           Phosphosite = sapply(strsplit(names(clusters), " "), `[`, 2), 
                           Cluster = as.character(clusters))
# Function to annotate phosphosites with clusters
annotate_with_clusters <- function(row) {
  phosphosites <- strsplit(row$Phosphosite, ", ")[[1]]
  clusters <- sapply(phosphosites, function(phosphosite) {
    cluster <- cluster_info$Cluster[cluster_info$Gene == row$Gene & cluster_info$Phosphosite == phosphosite]
    if (length(cluster) > 0) {
      return(paste0(phosphosite, " (Cluster ", cluster, ")"))
    } else {
      return(phosphosite)
    }
  })
  return(paste(clusters, collapse = ", "))
}

# Merge phosphosite_df with cluster_info
phosphosite_df_with_clusters <- merge(phosphosite_df, cluster_info, by = c("Gene", "Phosphosite"), all.x = TRUE)

# Merge phosphosite_df_with_clusters with kinase_sites_df
phosphosite_df_with_clusters <- merge(phosphosite_df_with_clusters, kinase_sites_df, by = c("Gene", "Phosphosite"), all.x = TRUE)

# Annotate phosphosites with clusters and kinases
phosphosite_df_with_clusters$Phosphosite <- paste(phosphosite_df_with_clusters$Phosphosite, " (", phosphosite_df_with_clusters$Cluster, "|", phosphosite_df_with_clusters$Kinase, ")", sep="")

# Aggregate phosphosites for each gene
aggregated_phosphosites <- aggregate(Phosphosite ~ Gene, phosphosite_df_with_clusters, paste, collapse = ", ")

# Merge gene_frequency_df with aggregated_phosphosites
merged_df_with_clusters <- merge(gene_frequency_df, aggregated_phosphosites, by = "Gene")
merged_df_with_clusters <- rename(merged_df_with_clusters, Protein = Gene, `Phosphosite (Cluster|Kinase)` = Phosphosite)
# Sort merged_df by Frequency and select the top 10 rows
top_10_merged_df <- head(merged_df_with_clusters[order(-merged_df_with_clusters$Frequency), ], 10)

# Select the first 10 phosphosites in the `Phosphosite (Cluster|Kinase)` column
top_10_merged_df <- top_10_merged_df %>%
  mutate(`Phosphosite (Cluster|Kinase)` = sapply(strsplit(`Phosphosite (Cluster|Kinase)`, ", "), function(x) str_c(head(x, 10), collapse = ", ")))

# Convert top_10_merged_df to a LaTeX table
latex_table <- xtable(top_10_merged_df)

# Print the LaTeX table
print(latex_table, type = "latex", include.rownames=FALSE)


# Create a copy of the data frame for export
export <- L6.matrices_Up_CS$combinedScoreMatrix
export <- as.data.frame(export)

# Add row names as a new column
export <- cbind(Phosphosite = rownames(export), export)
reshaped_data_for_export <- rename(reshaped_data, Kinases = Var1, Sample = Var2)
merged_df_with_clusters_export = rename(merged_df_with_clusters, 'Frequency among Clusters and GO Terms'= Frequency)
# Install the writexl package if not already installed
if (!require(writexl)) {
  install.packages("writexl")
}


kinases_dataframe <- aggregated_phosphosites %>%
    mutate(PhosphositeList = strsplit(Phosphosite, ", ")) %>%
    unnest(PhosphositeList) %>%
    separate(PhosphositeList, into = c("Phosphosite", "ClusterKinase"), sep = " \\(") %>%
    separate(ClusterKinase, into = c("Cluster", "Kinase"), sep = "\\|") %>%
    mutate(Kinase = sub("\\)", "", Kinase))


kinases_dataframe <- kinases_dataframe %>%
  group_by(Gene, Kinase) %>%
  mutate(AffectedSites = paste(Phosphosite, collapse = ", ")) %>%
  ungroup()

kinase_counts_per_protein <- kinases_dataframe %>%
  group_by(Gene, Kinase, AffectedSites) %>%
  summarise(KinaseCount = n())

# Sort the dataframe by the KinaseCount column in descending order
sorted_kinase_counts_per_protein <- kinase_counts_per_protein %>%
  arrange(desc(KinaseCount))

# Convert the dataframe to a LaTeX table
latex_table_kinases <- xtable(top_5_kinase_counts_per_protein <- kinase_counts_per_protein %>%
  arrange(desc(KinaseCount)) %>%
  head(5))
print(latex_table_kinases, type = "latex", include.rownames=FALSE)

```



## Heatmap
```{r}
ppe_volcano = ppe_noSerum
rownames(ppe_volcano) <- gsub("(.*?);(.*?);([A-Z])([0-9]+);([A-Z]+)", "\\2 \\3\\4 ", rownames(ppe_volcano))


# Extract the Quantification assay
quantification <- assays(ppe_volcano)$Quantification
original_colnames <- colnames(quantification)

new_colnames <- gsub("CS", "DMKN αβ-/-", gsub("DTU", "DMKN βγ-/-", gsub("WT", "WT DMKN αβγ", gsub("_", " ", gsub("Rep", "", gsub("Endogenous", "Endogenous", gsub("Rescue", "Rescue", gsub("NoSerum_", "", original_colnames))))))))
colnames(quantification) <- new_colnames

# Apply Z-score standardization
z_scores <- t(apply(quantification, 1, scale))
# Convert the matrix to a data frame
z_scores_df <- as.data.frame(z_scores)

# Set the column names
colnames(z_scores_df) <- new_colnames
# Define the new order
new_order <- c(grep("WT DMKN αβγ Endogenous", colnames(z_scores_df), value = TRUE),
               grep("DMKN βγ-/- Endogenous", colnames(z_scores_df), value = TRUE),
               grep("DMKN αβ-/- Endogenous", colnames(z_scores_df), value = TRUE),
               grep("WT DMKN αβγ Rescue", colnames(z_scores_df), value = TRUE),
               grep("DMKN βγ-/- Rescue", colnames(z_scores_df), value = TRUE),
               grep("DMKN αβ-/- Rescue", colnames(z_scores_df), value = TRUE))

# Reorder the columns
z_scores_df <- z_scores_df[, new_order]


# Create an annotation data frame
annotation_df <- data.frame(
  Condition = factor(rep(c("WT DMKN αβγ Endogenous", "DMKN βγ-/- Endogenous", "DMKN αβ-/- Endogenous", 
                           "WT DMKN αβγ Rescue", "DMKN βγ-/- Rescue", "DMKN αβ-/- Rescue"), each = 3))
)
rownames(annotation_df) <- colnames(z_scores_df)

# Define colors for the annotation
annotation_colors = list(
  Condition = c("WT DMKN αβγ Endogenous" = "blue", "DMKN βγ-/- Endogenous" = "green", 
                "DMKN αβ-/- Endogenous" = "red", "WT DMKN αβγ Rescue" = "cyan", 
                "DMKN βγ-/- Rescue" = "magenta", "DMKN αβ-/- Rescue" = "yellow")
)



```

```{r}

# Import the long to wide OG df that was created in the previous section with a 0 loc filter in perseus
phos_quant_afterPerseus_Qvaluefilter0_01_Wide <- read_delim("20221127_HRMS1_DIA_DMKN_KO_ENDO_RESCUE_Rstudio_Vcan_report_WO_PeakShape_PeptideCollapse_Wide.tsv", 
    delim = "\t", escape_double = FALSE, 
    comment = "#", trim_ws = TRUE)

# Import the long to wide MS1 peak shape filter df that was created in the previous section with a 0 loc filter in perseus
phos_quant_afterPerseus_Qvaluefilter0_01_W_PeakShape_Wide <- read_delim("20221127_HRMS1_DIA_DMKN_KO_ENDO_RESCUE_Rstudio_Vcan_report_W_PeakShape_PeptideCollapse_Wide.tsv", 
    delim = "\t", escape_double = FALSE, 
    comment = "#", trim_ws = TRUE)


phos_quant_afterPerseus_Qvaluefilter0_01_Wide_truncated = phos_quant_afterPerseus_Qvaluefilter0_01_Wide %>%
  mutate(across(where(is.character), substr, start = 1, stop = 32767))
phos_quant_afterPerseus_Qvaluefilter0_01_W_PeakShape_Wide_truncated = phos_quant_afterPerseus_Qvaluefilter0_01_W_PeakShape_Wide %>%
  mutate(across(where(is.character), substr, start = 1, stop = 32767))
phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4_truncated = phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4 %>%
  mutate(across(where(is.character), substr, start = 1, stop = 32767))
# Get the second data frame and convert it to a data frame
ppe_quantification <- data.frame(assay(ppe, "Quantification"))

# Add row names as a new column
ppe_quantification$RowNames <- rownames(assay(ppe, "Quantification"))
# Combine data frames in a list
data_list <- list("Phos_Peptides" = phos_quant_afterPerseus_Qvaluefilter0_01_Wide_truncated, 
                  "Phos_Peptides_PeakFilter" = phos_quant_afterPerseus_Qvaluefilter0_01_W_PeakShape_Wide_truncated, 
                  "Phos_Sites" = phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4_truncated, 
                  "Phos_Sites_FullQuant" = ppe_quantification)

#
```

```{r}

# Extract the phosphosite from the first data frame
phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4_truncated$phosphosite <- sapply(strsplit(as.character(phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4_truncated$PTM_collapse_key), "_"), `[`, 2)

# Extract the phosphosite from the second data frame
ppe_quantification$phosphosite <- sapply(strsplit(as.character(rownames(assay(ppe, "Quantification"))), ";"), `[`, 3)

# Now find the common phosphosites
common_phosphosites <- intersect(phos_quant_afterPerseus_Qvaluefilter0_01peakfilter0_6_localizationFilter0_75_V4_truncated$phosphosite, df2$phosphosite)

# Filter both data frames to only keep the common phosphosites
df1_filtered <- df1[df1$phosphosite %in% common_phosphosites, ]
df2_filtered <- df2[df2$phosphosite %in% common_phosphosites, ]
```

##2D Proteome
```{r}

# Import the 2D proteome data heatmap data
proteome_2D <- read.delim2("heatmap_proteome_fromSN.tsv")

# Remove the 'X' column
proteome_2D <- proteome_2D[,-1]

# Define the new order of the columns
new_order <- c("WT.Endo.R1", "WT.Endo.R2", "WT.Endo.R3", "DTU.Endo.R1", "DTU.Endo.R2", "DTU.Endo.R3", 
               "CS.Endo.R2", "CS.Endo.R3", "CS.Endo.R1", "WT.Rescue.R1", "WT.Rescue.R2", "WT.Rescue.R3", 
               "DTU.Rescue.R1", "DTU.Rescue.R2", "DTU.Rescue.R3", "CS.Rescue.R1", "CS.Rescue.R2", "CS.Rescue.R3")

# Reorder the columns
proteome_2D <- proteome_2D[, new_order]
# Assuming proteome_2D is your new heatmap data
original_colnames <- colnames(proteome_2D)

# Use the same renaming scheme as in the first heatmap
new_colnames <- gsub("CS", "DMKN αβ-/-", gsub("DTU", "DMKN βγ-/-", gsub("WT", "WT DMKN αβγ", gsub("_", " ", gsub("Rep", "", gsub("Endogenous", "Endogenous", gsub("Rescue", "Rescue", gsub("NoSerum_", "", original_colnames))))))))
colnames(proteome_2D) <- new_colnames

# Create an annotation data frame
annotation_df <- data.frame(
  Condition = factor(rep(c("WT DMKN αβγ Endogenous", "DMKN βγ-/- Endogenous", "DMKN αβ-/- Endogenous", 
                           "WT DMKN αβγ Rescue", "DMKN βγ-/- Rescue", "DMKN αβ-/- Rescue"), each = 3))
)
rownames(annotation_df) <- colnames(proteome_2D)

# Define colors for the annotation
annotation_colors = list(
  Condition = c("WT DMKN αβγ Endogenous" = "blue", "DMKN βγ-/- Endogenous" = "green", 
                "DMKN αβ-/- Endogenous" = "red", "WT DMKN αβγ Rescue" = "cyan", 
                "DMKN βγ-/- Rescue" = "magenta", "DMKN αβ-/- Rescue" = "yellow")
)

# Plot the heatmap


# Load the necessary library
library(ggplot2)

# Create a data frame
df <- data.frame(
  Model = c("Dmkn βγ-/-", "Dmkn αβ-/-", "Dmkn αβ-/- Rescue", "Dmkn βγ-/- Rescue"),
  Decreased = c(194, 514, 368, 668),
  Increased = c(294, 422, 302, 332)
)

# Melt the data frame to long format
df_long <- reshape2::melt(df, id.vars = "Model")

# Create the bar plot
ggplot(df_long, aes(x = Model, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Model", y = "Number of Proteins", fill = "Change") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Create a data frame
df <- data.frame(
  Condition = factor(c("Dmkn αβ-/- vs WT", "Rescue vs Endogenous (Dmkn αβ-/-)", "Dmkn βγ-/- vs WT", "Rescue vs Endogenous (Dmkn βγ-/-)"), 
                     levels = c("Dmkn αβ-/- vs WT", "Rescue vs Endogenous (Dmkn αβ-/-)", "Dmkn βγ-/- vs WT", "Rescue vs Endogenous (Dmkn βγ-/-)")),  # Specify the order of conditions
  Decreased = c(-514, -368, -194, -668),  # Make Decreased negative
  Increased = c(422, 302, 294, 332)
)

# Add a Total column
df$Total <- abs(df$Decreased) + df$Increased

# Melt the data frame to long format
df_long <- reshape2::melt(df, id.vars = c("Condition", "Total"))

# Create the diverging stacked bar plot
ggplot(df_long, aes(x = Condition, y = value, fill = variable)) +
  geom_bar(stat = "identity") +
  geom_text(data = subset(df_long, variable == "Increased"), aes(label = Total, y = 600), vjust = -0.5, hjust = 0.5, color = "black") +  # Display total number at a fixed position
  scale_y_continuous(labels = abs) +  # Make y-axis labels positive
  labs(x = "Condition", y = "Number of Significantly Differential Proteins", fill = "Change") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


# Figure 

## log2FC Average
```{r}


renamed_df_test <- renamed_df 

# Rename columns in the second dataframe
# names(renamed_df_test)[1:3] <- paste0("WT_Endogenous_", 1:3)
# names(renamed_df_test)[4:6] <- paste0("WT_Treated_", 1:3)
# names(renamed_df_test)[7:9] <- paste0("DTU_Endogenous_", 1:3)
# names(renamed_df_test)[10:12] <- paste0("DTU_Treated_", 1:3)
# names(renamed_df_test)[13:15] <- paste0("CS_Endogenous_", 1:3)
# names(renamed_df_test)[16:18] <- paste0("CS_Treated_", 1:3)
# Split the strings by "/"

# Filter rows where 'Description' contains any of the terms
filtered_GO_terms <- ENDO_CS_UP_cluster_significant_GO@compareClusterResult[grep("adherens junction|cadherin binding", ENDO_CS_UP_cluster_significant_GO@compareClusterResult$Description), ]
split_geneIDs <- strsplit(filtered_GO_terms$geneID, "/")

# Unlist and extract unique gene IDs
unique_geneIDs <- unique(unlist(split_geneIDs))

names <- c("CTNND1", "PTPRK", "EGFR", "ERBB2", "PTPN1", "CTNNB1", "CTNNA1", "PLEC", "SCRIB", "TNKS1BP1", "PKP3", "PKP4")

renamed_df_test <- renamed_df_test %>%
  mutate(across(starts_with(c("CS_", "WT_", "DTU_")), as.numeric))

# Now calculate the row means
result <- renamed_df_test %>%
  filter(PG.Genes %in% unique_geneIDs) %>%
  mutate(
    CS_Avg_Endogenous = select(., starts_with("CS_Endogenous_")) %>% 
                                   keep(is.numeric) %>% 
                                   rowMeans(na.rm = TRUE),
    WT_Avg_Endogenous = select(., starts_with("WT_Endogenous_")) %>% 
                                keep(is.numeric) %>% 
                                rowMeans(na.rm = TRUE),
    DTU_AVG_Endogenous = select(., starts_with("DTU_Endogenous_")) %>% 
                             keep(is.numeric) %>% 
                             rowMeans(na.rm = TRUE),
    Log2_Ratio_CS_Endogenous = log2(WT_Avg_Endogenous / CS_Avg_Endogenous),
    Log2_Ratio_DTU_Endogenous = log2(WT_Avg_Endogenous / DTU_AVG_Endogenous),
    CS_Avg_Rescue = select(., starts_with("CS_Rescue_")) %>% 
                                keep(is.numeric) %>% 
                                rowMeans(na.rm = TRUE),
    DTU_AVG_Rescue = select(., starts_with("CS_Rescue_")) %>% 
                          keep(is.numeric) %>% 
                          rowMeans(na.rm = TRUE),
    WT_Endogenous_Avg_Rescue = select(., matches("WT_Rescue_")) %>% 
                             keep(is.numeric) %>% 
                             rowMeans(na.rm = TRUE),
    Log2_Ratio_CS_Rescue = log2(CS_Avg_Rescue/CS_Avg_Endogenous),
    Log2_Ratio_DTU_Rescue = log2(DTU_AVG_Rescue/DTU_AVG_Endogenous),
    Log2_Ratio_WT_Rescue = log2(WT_Endogenous_Avg_Rescue / WT_Avg_Endogenous))  %>%
  select(PTM_collapse_key, PEP.StrippedSequence, Log2_Ratio_CS_Endogenous, Log2_Ratio_DTU_Endogenous, Log2_Ratio_CS_Rescue, Log2_Ratio_WT_Rescue,  Log2_Ratio_DTU_Rescue)

global_PG_QUANT_test <-global_PG_QUANT
global_PG_QUANT_test = global_PG_QUANT_V2
# Define the names map
names_map_global <- c(
  "PG.ProteinGroups" = "PG.ProteinGroups",
  "PG.Genes"="PG.Genes",
  "X.1..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_1.raw.PG.MS1Quantity" = "WT_Endogenous_1",
  "X.2..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_2.raw.PG.MS1Quantity" = "WT_Endogenous_2",
  "X.3..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_3.raw.PG.MS1Quantity" = "WT_Endogenous_3",
  "X.4..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_4.raw.PG.MS1Quantity" = "WT_Rescue_1",
  "X.5..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_5.raw.PG.MS1Quantity" = "WT_Rescue_2",
  "X.6..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_6.raw.PG.MS1Quantity" = "WT_Rescue_3",
  "X.7..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_13.raw.PG.MS1Quantity" = "DTU_Endogenous_1",
  "X.8..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_14.raw.PG.MS1Quantity" = "DTU_Endogenous_2",
  "X.9..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_15.raw.PG.MS1Quantity" = "DTU_Endogenous_3",
  "X.10..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_16.raw.PG.MS1Quantity" = "DTU_Rescue_1",
  "X.11..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_17.raw.PG.MS1Quantity" = "DTU_Rescue_2",
  "X.12..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_18.raw.PG.MS1Quantity" = "DTU_Rescue_3",
  "X.13..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_25.raw.PG.MS1Quantity" = "CS_Endogenous_1",
  "X.14..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_26.raw.PG.MS1Quantity" = "CS_Endogenous_2",
  "X.15..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_27.raw.PG.MS1Quantity" = "CS_Endogenous_3",
  "X.16..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_28.raw.PG.MS1Quantity" = "CS_Rescue_1",
  "X.17..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_29.raw.PG.MS1Quantity" = "CS_Rescue_2",
  "X.18..20221215_MK_EVO_VC_noFAIMS_15cm_WHISPER100_20SPD_global_Ntert_DMKN_KO_30.raw.PG.MS1Quantity" = "CS_Rescue_3"
)


# Rename the columns
colnames(global_PG_QUANT_test) <- names_map_global[colnames(global_PG_QUANT_test)]


# Check if the length of new names matches with the length of current names
if (length(new_names) == length(current_names)) {
  # Set the new column names
  colnames(global_PG_QUANT_test) <- new_names
} else {
  print("The lengths of current and new column names do not match.")
}

global_PG_QUANT_test$CS_Endogenous_1 <- as.numeric(gsub(",", ".", global_PG_QUANT_test$CS_Endogenous_1))


global_PG_QUANT_test = global_PG_QUANT_test %>%
  mutate(across(starts_with(c("CS_", "WT_", "DTU_")), as.numeric))
global_PG_QUANT_test = na.omit(global_PG_QUANT_test)

# Convert to scientific notation
global_PG_QUANT_test$CS_Endogenous_1 <- formatC(global_PG_QUANT_test$CS_Endogenous_1, format = "e", digits = 2)

# Update subsequent functions
result_global <- global_PG_QUANT_test %>% 
  filter(PG.Genes %in% unique_geneIDs) %>% 
  mutate( 
    WT_Control_Avg_Endogenous = select(., matches("WT_Endogenous_\\d+")) %>% keep(is.numeric) %>% rowMeans(na.rm = TRUE),
    DTU_Avg_Endogenous = select(., matches("DTU_Endogenous_\\d+")) %>% keep(is.numeric) %>% rowMeans(na.rm = TRUE),
    CS_Avg_Endogenous = select(., matches("CS_Endogenous_\\d+")) %>% keep(is.numeric) %>% rowMeans(na.rm = TRUE),
    Log2_Ratio_CS_Endogenous = log2(WT_Control_Avg_Endogenous / CS_Avg_Endogenous),
    Log2_Ratio_DTU_Endogenous = log2(WT_Control_Avg_Endogenous / DTU_Avg_Endogenous),
    WT_Control_Avg_Rescue = select(., matches("WT_Rescue_\\d+")) %>% keep(is.numeric) %>% rowMeans(na.rm = TRUE),
    DTU_Avg_Rescue = select(., matches("DTU_Rescue_\\d+")) %>% keep(is.numeric) %>% rowMeans(na.rm = TRUE),
    CS_Avg_Rescue = select(., matches("CS_Rescue_\\d+")) %>% keep(is.numeric) %>% rowMeans(na.rm = TRUE),
    Log2_Ratio_CS_Rescue = log2(CS_Avg_Rescue / CS_Avg_Endogenous),
    Log2_Ratio_DTU_Rescue = log2(DTU_Avg_Rescue / DTU_Avg_Endogenous),
    Log2_Ratio_WT_Rescue = log2(WT_Control_Avg_Rescue / WT_Control_Avg_Endogenous) 
  ) %>% 
  select(PG.ProteinGroups, PG.Genes, Log2_Ratio_CS_Endogenous, Log2_Ratio_DTU_Endogenous, Log2_Ratio_CS_Rescue, Log2_Ratio_DTU_Rescue, Log2_Ratio_WT_Rescue)


# Assuming the first dataframe is named result and the second dataframe is result_global
# Make sure both dataframes have the same number of rows and are in the same order
# Extract the protein part of PTM_collapse_key
protein <- stringr::str_extract(result$PTM_collapse_key, "^[^_]*")

# Find the rows in result_global where PG.Genes matches the protein
matching_rows <- result_global$PG.Genes %in% protein

# Subset result_global using the matching rows
result_global_matched <- result_global[matching_rows, ]

# Define the matching columns
matching_cols <- intersect(names(result), names(result_global_matched))

# Initialize an empty data frame for df_diff
df_diff <- data.frame()

# Iterate over the rows of result
for (i in 1:nrow(result)) {
  # Find the matching row in result_global_matched
  matching_row <- which(result_global_matched$PG.Genes == protein[i])
  
  # If there's a match
  if (length(matching_row) > 0) {
    # Subtract the global protein value from the phospho-site
    diff <- (result[i, matching_cols] - (result_global_matched[matching_row, matching_cols]))
    
    # Add the PTM_collapse_key to the difference
    diff <- cbind(result[i, "PTM_collapse_key"], diff)
    
    # Bind the difference to df_diff
    df_diff <- rbind(df_diff, diff)
  }
}

# Set the row names of df_diff to the protein names
rownames(df_diff) <- df_diff$PTM_collapse_key



# Assuming df_diff is your dataframe
df_long <- df_diff %>%
  pivot_longer(cols = -PTM_collapse_key, names_to = "Ratio", values_to = "Value")

non_ctnnd1_keys <- df_diff$PTM_collapse_key[!grepl("^CTNND1|PTPRK|EGFR", df_diff$PTM_collapse_key)]

# keys <- c("CTNND1_S268_M2", "CTNND1_S269_M1",  "CTNND1_S288_M1", "CTNND1_T310_M1", "CTNND1_T906_M1", "CTNND1_T916_M1", "PTPRK_Y858_M1","EGFR_S1039_M1", "EGFR_S991_M1","EGFR_T693_M1",non_ctnnd1_keys)

# Assuming df_diff is your dataframe
df_long <- df_diff %>% na.omit() %>%
  filter(str_detect(PTM_collapse_key, "CTNND1")) %>%
  pivot_longer(cols = -PTM_collapse_key, names_to = "Ratio", values_to = "Value")

# Define the order of the levels
levels_order <- c("Log2_Ratio_DTU_Endogenous","Log2_Ratio_CS_Endogenous", "Log2_Ratio_CS_Rescue", "Log2_Ratio_DTU_Rescue", "Log2_Ratio_WT_Rescue")

# Convert Ratio to a factor with the specified order of levels
df_long$Ratio <- factor(df_long$Ratio, levels = levels_order)
#df_long$PTM_collapse_key <- gsub("_", " ", sub("_M[12]$", "", df_long$PTM_collapse_key))
# Rename the levels of the Ratio variable
df_long <- df_long %>%
  mutate(Ratio = recode(Ratio,
                        "Log2_Ratio_CS_Endogenous" = "Endogenous WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous DMKN \U03B1\U03B2 -/-",
                        "Log2_Ratio_DTU_Endogenous" = "Endogenous WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous DMKN \U03B2\U03B3 -/-",
                        "Log2_Ratio_CS_Rescue" = "Rescue DMKN \U03B1\U03B2 -/- vs\nEndogenous DMKN \U03B1\U03B2 -/-",
                        "Log2_Ratio_DTU_Rescue" = "Rescue DMKN \U03B2\U03B3 -/- vs\nEndogenous DMKN \U03B2\U03B3 -/-",
                        "Log2_Ratio_WT_Rescue" = "Rescue WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous WT DMKN \U03B1\U03B2\U03B3"))
# Create dot plot

df_long <- df_long %>%
  filter(Ratio != "Rescue WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous WT DMKN \U03B1\U03B2\U03B3")

#df_long$Ratio <- str_wrap(df_long$Ratio, width = 10)
# Define a vector of colors
colors <- c("#377eb8", "#ff7f00", "#4daf4a", "#f781bf", "#a65628")
# Find the middle category
middle_position <- (length(unique(df_long$Ratio)) + 1) / 2

p <- ggplot(df_long, aes(x = Ratio, y = Value, color = Ratio)) +
  geom_point(size = 3) +
  geom_hline(yintercept = abs(log2(1.5)), linetype = "dashed", color = "red") +
  geom_hline(yintercept = -abs(log2(1.5)), linetype = "dashed", color = "red") +
  facet_wrap(~ PTM_collapse_key, scales = "free_y", nrow = 2) +
  coord_cartesian(ylim = c(-3, 3)) +
  theme_bw() +
  theme(text = element_text(size = 8),  # Set global font size to 6
        axis.text.x = element_blank(),  # Remove x-axis labels
        axis.ticks.x = element_blank(),  # Remove x-axis ticks
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +  # Move legend to bottom
  labs(title = "Protein-Normalized p-Sites for Cell-Cell Adhesion Related Proteins", y = "Difference in Log2 Fold Change Coefficients of Phosphorylated Peptide and Protein Abundance", x = NULL) +  # Remove x-axis label
  scale_color_manual(values = colors)  +# Add this line
  theme(text = element_text(family = "Arial")) + geom_vline(xintercept = middle_position, linetype = "dashed", color = "black")

p_seperately 
p_average = p
```

## log2FC Replicates
```{r}
# Calculate the log2 fold change for each replicate individually for each condition
# Calculate the log2 fold change for each replicate individually for each condition
result <- renamed_df_test %>%
  filter(PG.Genes %in% unique_geneIDs) %>%
  mutate(Log2_Ratio_CS_Endogenous_1 = log2(WT_Endogenous_Rep1 / CS_Endogenous_Rep1),
         Log2_Ratio_CS_Endogenous_2 = log2(WT_Endogenous_Rep2 / CS_Endogenous_Rep2),
         Log2_Ratio_CS_Endogenous_3 = log2(WT_Endogenous_Rep3 / CS_Endogenous_Rep3),
         Log2_Ratio_DTU_Endogenous_1 = log2(WT_Endogenous_Rep1 / DTU_Endogenous_Rep1),
         Log2_Ratio_DTU_Endogenous_2 = log2(WT_Endogenous_Rep2 / DTU_Endogenous_Rep2),
         Log2_Ratio_DTU_Endogenous_3 = log2(WT_Endogenous_Rep3 / DTU_Endogenous_Rep3),
         Log2_Ratio_CS_Rescue_1 = log2(CS_Rescue_Rep1 / CS_Endogenous_Rep1),
         Log2_Ratio_CS_Rescue_2 = log2(CS_Rescue_Rep2 / CS_Endogenous_Rep2),
         Log2_Ratio_CS_Rescue_3 = log2(CS_Rescue_Rep3 / CS_Endogenous_Rep3),
         Log2_Ratio_DTU_Rescue_1 = log2(DTU_Rescue_Rep1 / DTU_Endogenous_Rep1),
         Log2_Ratio_DTU_Rescue_2 = log2(DTU_Rescue_Rep2 / DTU_Endogenous_Rep2),
         Log2_Ratio_DTU_Rescue_3 = log2(DTU_Rescue_Rep3 / DTU_Endogenous_Rep3),
         Log2_Ratio_WT_Rescue_1 = log2(WT_Rescue_Rep1 / WT_Endogenous_Rep1),
         Log2_Ratio_WT_Rescue_2 = log2(WT_Rescue_Rep2 / WT_Endogenous_Rep2),
         Log2_Ratio_WT_Rescue_3 = log2(WT_Rescue_Rep3 / WT_Endogenous_Rep3)) %>%
  select(PTM_collapse_key, PEP.StrippedSequence, starts_with("Log2_Ratio_"))

# Calculate the log2 fold change for each replicate individually for each condition
result_global <- global_PG_QUANT_test %>%
  filter(PG.Genes %in% unique_geneIDs) %>%
  mutate(Log2_Ratio_CS_Endogenous_1 = log2(WT_Endogenous_1 / CS_Endogenous_1),
         Log2_Ratio_CS_Endogenous_2 = log2(WT_Endogenous_2 / CS_Endogenous_2),
         Log2_Ratio_CS_Endogenous_3 = log2(WT_Endogenous_3 / CS_Endogenous_3),
         Log2_Ratio_DTU_Endogenous_1 = log2(WT_Endogenous_1 / DTU_Endogenous_1),
         Log2_Ratio_DTU_Endogenous_2 = log2(WT_Endogenous_2 / DTU_Endogenous_2),
         Log2_Ratio_DTU_Endogenous_3 = log2(WT_Endogenous_3 / DTU_Endogenous_3),
         Log2_Ratio_CS_Rescue_1 = log2(CS_Rescue_1 / CS_Endogenous_1),
         Log2_Ratio_CS_Rescue_2 = log2(CS_Rescue_2 / CS_Endogenous_2),
         Log2_Ratio_CS_Rescue_3 = log2(CS_Rescue_3 / CS_Endogenous_3),
         Log2_Ratio_DTU_Rescue_1 = log2(DTU_Rescue_1 / DTU_Endogenous_1),
         Log2_Ratio_DTU_Rescue_2 = log2(DTU_Rescue_2 / DTU_Endogenous_2),
         Log2_Ratio_DTU_Rescue_3 = log2(DTU_Rescue_3 / DTU_Endogenous_3),
         Log2_Ratio_WT_Rescue_1 = log2(WT_Rescue_1 / WT_Endogenous_1),
         Log2_Ratio_WT_Rescue_2 = log2(WT_Rescue_2 / WT_Endogenous_2),
         Log2_Ratio_WT_Rescue_3 = log2(WT_Rescue_3 / WT_Endogenous_3)) %>%
  select(PG.ProteinGroups, PG.Genes, starts_with("Log2_Ratio_"))



# Assuming the first dataframe is named result and the second dataframe is result_global
# Make sure both dataframes have the same number of rows and are in the same order
# Extract the protein part of PTM_collapse_key
protein <- stringr::str_extract(result$PTM_collapse_key, "^[^_]*")

# Find the rows in result_global where PG.Genes matches the protein
matching_rows <- result_global$PG.Genes %in% protein

# Subset result_global using the matching rows
result_global_matched <- result_global[matching_rows, ]

# Define the matching columns
matching_cols <- intersect(names(result), names(result_global_matched))

# Initialize an empty data frame for df_diff
df_diff <- data.frame()

# Iterate over the rows of result
for (i in 1:nrow(result)) {
  # Find the matching row in result_global_matched
  matching_row <- which(result_global_matched$PG.Genes == protein[i])
  
  # If there's a match
  if (length(matching_row) > 0) {
    # Subtract the global protein value from the phospho-site
    diff <- result[i, matching_cols] - (result_global_matched[matching_row, matching_cols])
    
    # Add the PTM_collapse_key to the difference
    diff <- cbind(result[i, "PTM_collapse_key"], diff)
    
    # Bind the difference to df_diff
    df_diff <- rbind(df_diff, diff)
  }
}

# Set the row names of df_diff to the protein names
rownames(df_diff) <- df_diff$PTM_collapse_key


# Assuming df_diff is your dataframe
df_long <- df_diff %>%
  pivot_longer(cols = -PTM_collapse_key, names_to = "Ratio", values_to = "Value")

keys <- df_diff$PTM_collapse_key[grepl("^ADD1|ANXA2|BAIAP2|CTNNA1|CTNND1|MYH9|PARD3|PKP3|PTPRK|SCRIB|TJP1", df_diff$PTM_collapse_key)]

#keys <- c("CTNND1_S268_M2", "CTNND1_S269_M1",  "CTNND1_S288_M1", "CTNND1_T310_M1", "CTNND1_T906_M1", "CTNND1_T916_M1", "PTPRK_Y858_M1","EGFR_S1039_M1", "EGFR_S991_M1","EGFR_T693_M1",non_ctnnd1_keys)

# Assuming df_diff is your dataframe
df_long <- df_diff %>% na.omit() %>%
  #filter(str_detect(PTM_collapse_key, "CTNND1|CTNNA1|CTNNB1|PTPRK|EGFR|SRC")) %>%
  pivot_longer(cols = -PTM_collapse_key, names_to = "Ratio", values_to = "Value")
# 
# # Define the order of the levels
# levels_order <- c("Log2_Ratio_DTU_Endogenous","Log2_Ratio_CS_Endogenous", "Log2_Ratio_CS_Rescue", "Log2_Ratio_DTU_Rescue", "Log2_Ratio_WT_Rescue")
# 
# # Convert Ratio to a factor with the specified order of levels
# df_long$Ratio <- factor(df_long$Ratio, levels = levels_order)
# #df_long$PTM_collapse_key <- gsub("_", " ", sub("_M[12]$", "", df_long$PTM_collapse_key))
# # Rename the levels of the Ratio variable
# df_long <- df_long %>%
#   mutate(Ratio = recode(Ratio,
#                         "Log2_Ratio_CS_Endogenous" = "Endogenous WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous DMKN \U03B1\U03B2 -/-",
#                         "Log2_Ratio_DTU_Endogenous" = "Endogenous WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous DMKN \U03B2\U03B3 -/-",
#                         "Log2_Ratio_CS_Rescue" = "Rescue DMKN \U03B1\U03B2 -/- vs\nEndogenous DMKN \U03B1\U03B2 -/-",
#                         "Log2_Ratio_DTU_Rescue" = "Rescue DMKN \U03B2\U03B3 -/- vs\nEndogenous DMKN \U03B2\U03B3 -/-",
#                         "Log2_Ratio_WT_Rescue" = "Rescue WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous WT DMKN \U03B1\U03B2\U03B3"))
# # Create dot plot
# 
# df_long <- df_long %>%
#   filter(Ratio != "Rescue WT DMKN \U03B1\U03B2\U03B3 vs\nEndogenous WT DMKN \U03B1\U03B2\U03B3")

# Split the Var2 variable into two parts
df_long <- df_long %>%
  tidyr::separate(Ratio, into = c("Term1", "Term2", "Genotype", "Treatment"), sep = "_")

# Replace the values in the Genotype and Treatment columns
df_long$Genotype[df_long$Genotype == "WT"] <- "WT"
df_long$Genotype[df_long$Genotype == "DTU"] <- "WT DMKN \U03B1\U03B2\U03B3 vs\n DMKN \U03B2\U03B3 -/-"
df_long$Genotype[df_long$Genotype == "CS"] <- "WT DMKN \U03B1\U03B2\U03B3 vs\n DMKN \U03B1\U03B2 -/-"

df_long$Treatment[df_long$Treatment == "Control"] <- "Endogenous"
df_long$Treatment[df_long$Treatment == "Treated"] <- "Rescue"

df_long <- df_long %>%
  filter(Genotype  != "WT")


# Convert Genotype to a factor with a specific order of levels
df_long$Genotype <- factor(df_long$Genotype)
#df_long <- df_long %>% rename("Fold Change" = Genotype)

df_long$Treatment <- as.factor(df_long$Treatment)
#df_long$Ratio <- str_wrap(df_long$Ratio, width = 10)
# Define a vector of colors
colors <- c("#377eb8", "#ff7f00", "#4daf4a", "#f781bf", "#a65628")
# Find the middle category
middle_position <- (length(unique(df_long$Treatment)) + 1) / 2

p <- ggplot(df_long, aes(x = Ratio, y = Value, color = Ratio)) +
  geom_point(size = 3) +
  geom_hline(yintercept = abs(log2(1.5)), linetype = "dashed", color = "red") +
  geom_hline(yintercept = -abs(log2(1.5)), linetype = "dashed", color = "red") +
  facet_wrap(~ PTM_collapse_key, scales = "free_y", nrow = 2) +
  #coord_cartesian(ylim = c(-3, 3)) +
  theme_bw() +
  theme(text = element_text(size = 8),  # Set global font size to 6
        axis.text.x = element_blank(),  # Remove x-axis labels
        axis.ticks.x = element_blank(),  # Remove x-axis ticks
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position = "bottom") +  # Move legend to bottom
  labs(title = "Protein-Normalized p-Sites for Cell-Cell Adhesion Related Proteins", y = "Difference in Log2 Fold Change Coefficients of Phosphorylated Peptide and Protein Abundance", x = NULL) +  # Remove x-axis label
 # scale_color_manual(values = colors)  +# Add this line
  theme(text = element_text(family = "Arial")) + geom_vline(xintercept = middle_position, linetype = "dashed", color = "black")

p_violin = ggplot(df_long, aes(x = Treatment, y = Value, fill = Genotype)) +
    geom_violin(width = 0.7, alpha = 0.9, color = "black") +
    ggforce::geom_sina() +
    facet_wrap(~ PTM_collapse_key) +
    stat_compare_means(aes(group = Treatment), method = "aov", label.y = 3.5, size = 3) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
          axis.text.y = element_text(size = 8),
          strip.text = element_text(size = 8, face = "bold"),
          legend.title = element_text(size = 8, face = "bold"),
          legend.text = element_text(size = 8),
          legend.position = "bottom") +
    labs(x = "Treatments", y = "Difference in Log2 Fold Change Coefficients of Phosphorylated Peptide and Protein Abundance", fill = "Genotype")

#### Only significant genes from adherens junction and cadherin binding

# Perform pairwise t-tests for each Genotype and Kinase
kruskal_results <- df_long %>%
  group_by(PTM_collapse_key) %>%
  do({
    data.frame(p_value = kruskal.test(.$Value ~ .$Genotype)$p.value)
  })

# Perform ANOVA for each Treatment and Kinase
anova_results <- df_long %>%
  group_by(PTM_collapse_key) %>%
  do({
    data.frame(p_value = summary(aov(.$Value ~ .$Treatment))[[1]]["Pr(>F)"][1,])
  })
two_way_anova_results <- df_long %>%
  group_by(PTM_collapse_key) %>%
  do({
    data.frame(p_value = summary(aov(.$Value ~ .$Genotype * .$Treatment))[[1]]["Pr(>F)"][1,])
  })
# Perform pairwise t-test for each Treatment and Kinase
ttest_results <- df_long %>%
  group_by(PTM_collapse_key) %>%
  do({
    p_matrix <- pairwise.t.test(.$Value, .$Genotype, p.adjust.method = "BH")$p.value
    data.frame(Genotype1 = rownames(p_matrix), Genotype2 = colnames(p_matrix), p_value = as.vector(p_matrix))
  })

# Filter the kinases where the p-value is significant in either test
significant_PhosSites_anova <- anova_results %>% 
  filter(p_value < 0.05) %>% 
  .$PTM_collapse_key %>% 
  unique()
# Get significant PhosSites from t-test
significant_PhosSites_ttest <- ttest_results %>% 
  filter(p_value < 0.05) %>% 
  .$PTM_collapse_key %>% 
  unique()
significant_PhosSites <- union(significant_PhosSites_ttest, significant_PhosSites_anova)


# Filter the df_long to include only the significant kinases
df_long <- df_long %>%
  filter(PTM_collapse_key %in% significant_PhosSites_anova)
df_long$PTM_collapse_key <- gsub("_", " ", sub("_M[12]$", "", df_long$PTM_collapse_key))

df_long_unique <- df_long %>%
  filter(str_detect(PTM_collapse_key, ("ADD1 S358|ANXA2 S12|BAIAP2 S454|CTNNA1 S655|CTNND1 S268|CTNND1 S288|CTNND1 S320|MYH9 S1943|PARD3 S144|PKP3 S285|SCRIB S1378|TJP1 S168")))
# df_long_unique <- df_long %>%
#   filter(str_detect(PTM_collapse_key, ("ADD1 S358|ANXA2 S12|BAIAP2 S454|CTNNA1 S655|CTNND1 S268|CTNND1 S288|CTNND1 S320|MYH9 S1943|PARD3 S144|PKP3 S285|PTPRK S856|SCRIB S1378|TJP1 S168")))
colors <- c("#377eb8", "#ff7f00", "#4daf4a", "#f781bf", "#a65628")
middle_position <- (length(unique(df_long_unique$Treatment)) + 1) / 2

p_violin_raw = ggplot(df_long_unique, aes(x = Treatment, y = Value, fill = interaction(Genotype, Treatment))) +
    geom_violin(width = 0.7, alpha = 0.9, color = "black", size =0.2)+
    ggforce::geom_sina(size = 0.1)+
    facet_wrap(~ PTM_collapse_key,scales = "free_y", nrow = 2) +
    #stat_compare_means(aes(group = Genotype), method = "t.test", label.y = 1.8, size = 2, label = "p.signif", hide.ns = T) +
    stat_compare_means(aes(group = Treatment), method = "aov", label.y = 1.5, size = 2,) +
    theme_bw() +
    coord_cartesian(ylim = c(-3, 3)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6),
          axis.text.y = element_text(size = 6),
          strip.text = element_text(size = 6, face = "bold"),
          legend.title = element_text(size = 6, face = "bold"),
          legend.text = element_text(size = 6),
          legend.position = "bottom",text = element_text(size = 8)) +
    labs(x = "Treatments", y = "Difference in Log2 Fold Change Coefficients of Phosphorylated Peptide and Protein Abundance", fill = "Genotype",
         title = "Violin Plot with ANOVA Test Results (p < 0.01)") +
    scale_fill_manual(values = colors)  # Add this line

p_violin = ggplot(df_long_unique, aes(x = Treatment, y = Value, fill = interaction(Genotype, Treatment))) +
    facet_wrap(~ PTM_collapse_key, scales = "free_y", nrow = 2) +
    stat_compare_means(aes(group = Treatment), method = "aov", label.y = 2.8, size = 2.5,) +
    #geom_hline(yintercept = c(log2(1.5), -log2(1.5)), linetype = "dashed", color = "red") +  # Add dashed lines at abs(log2(1.5))
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +  # Add dashed line at 0 in black color
    geom_vline(xintercept = middle_position, linetype = "dashed", color = "black")  +# Add vertical dashed line at middle_position 
    geom_violin(width = 1, alpha = 2, color = "black", size =0.2,adjust=2,draw_split=TRUE)+
    ggforce::geom_sina(size = 0.8)+ coord_cartesian(ylim = c(-5, 3)) +
    theme_bw() +
    theme(axis.text.x = element_blank(),  # Remove x-axis labels
          axis.ticks.x = element_blank(), 
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_blank(),, # Remove y-axis ticks
          axis.text.y = element_text(size = 6),
          strip.text = element_text(size = 6, face = "bold"),
          legend.title = element_text(size = 6, face = "bold"),
          legend.text = element_text(size = 6),
          legend.position = "bottom",
          text = element_text(size = 6, family = "Arial"))  +  # Remove minor y grid lines
    labs(y = "Difference in Log2 Fold Change Coefficients of Phosphorylated Peptide and Protein Abundance", fill = "Genotype-Treatment") +
    scale_fill_manual(values = colors)   # Use defined colors
    

```
# Import data
```{r cars}

Proteome_protein_quant <- read_delim("20240730_143924_20220201_VC_3D_PROTEOME_BG_AB_WT_v2_Report.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

# Define the new names
new_names_cells <- c("[1] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_B11_1_1.raw.PG.MS1Quantity" = "DMKN_BG_KO_1",
               "[2] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_B11_2_1.raw.PG.MS1Quantity" = "DMKN_BG_KO_2",
               "[3] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_B11_3_1.raw.PG.MS1Quantity" = "DMKN_BG_KO_3",
               "[4] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_D2_1_1.raw.PG.MS1Quantity" = "DMKN_AB_KO_1",
               "[5] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_D2_2_1.raw.PG.MS1Quantity" = "DMKN_AB_KO_2",
               "[6] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_D2_3_1.raw.PG.MS1Quantity" = "DMKN_AB_KO_3",
               "[7] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_WT_1_1.raw.PG.MS1Quantity" = "WT_1",
               "[8] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_WT_2_1.raw.PG.MS1Quantity" = "WT_2",
               "[9] 20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_WT_3_1.raw.PG.MS1Quantity" = "WT_3"
               )

# Convert the MS1 columns into numeric format
MS1_columns_cells <- grep("raw", names(Proteome_protein_quant), value = TRUE)
Proteome_protein_quant[MS1_columns_cells] <- lapply(Proteome_protein_quant[MS1_columns_cells], function(x) as.numeric(gsub(",", ".", x)))
#Cells_protein_quant = Cells_protein_quant %>%
#  mutate(across(ends_with("Quantity"), log10))

# Rename the columns
# Get the current column names
current_names <- colnames(Proteome_protein_quant)
for (i in seq_along(current_names)) {
  if (current_names[i] %in% names(new_names_cells)) {
    colnames(Proteome_protein_quant)[i] <- new_names_cells[current_names[i]]
  }
}
```
# Volcano Plot
```{r}
Proteome_protein_quant <- Proteome_protein_quant[complete.cases(Proteome_protein_quant[, grep("WT", colnames(Proteome_protein_quant))]), ]

# Convert the data to a DGEList for use with edgeR/limma
df <- Proteome_protein_quant
df <- df[complete.cases(df[, grep("WT", colnames(df))]), ]

df <- as.data.frame(df)
df <- df[!is.na(df$PG.ProteinGroups), ]


names(df) <- gsub(" ", ".", names(df))
names(df) <- gsub("/", ".", names(df))
df = na.omit(df)

#df$unique_genes <- make.names(df$PG.Genes, unique = TRUE)
#rownames(df) <- df$unique_genes

counts <- df[, -(1:3)]
rownames(counts) <- make.unique(df$PG.Genes)
#counts = log2(counts)
dge <- DGEList(counts = counts)

# Normalize the data
dge <- calcNormFactors(dge)

# Design matrix
#group <- factor(gsub(\\s\\d+$, "", colnames(dge))) This is if I dont change the names 

group <- factor(gsub("(\\.KO)?\\_\\d+$", "", colnames(dge))) # THis is if I change the naming above
design <- model.matrix(~0 + group)
colnames(design) <- levels(group)

# Estimate dispersion
dge <- estimateDisp(dge, design)
v <- voom(dge, design, plot=FALSE)

contrasts <- makeContrasts(
  BG_vs_WT = DMKN_BG_KO - WT,
  AB_vs_WT = DMKN_AB_KO - WT,
  levels = design
)
# Fit the model and perform the tests
fit <- lmFit(v, design)
fit2  = contrasts.fit(fit, contrasts)
fit2 <- eBayes(fit2)

# Extract the p-values and log fold changes (contrasts) from your fit2 object
p_values <- fit2$p.value
logFC <- fit2$coefficients
# 
# # Create a data frame to hold the p-values and log fold changes
# df_plot <- data.frame(Contrast = colnames(logFC),
#                  Gene = rownames(logFC),
#                  logFC = as.vector(logFC),
#                  p_value = as.vector(p_values))

# Calculate -log10 of the p-values for the y-axis
#df_plot$logp <- -log10(df_plot$p_value)

# Create a list to hold the plots
volcano_plots <- list()

# Define thresholds
pvalue_threshold <- -log10(0.05)
logFC_threshold <- log2(1.5)


# Convert the row names into a column
df_plot <- data.frame(Gene = rownames(logFC), logFC = as.vector(logFC), p_value = as.vector(p_values))

# Make sure the contrasts are properly assigned to each row
df_plot$Contrast <- rep(colnames(logFC), each = nrow(logFC))


# Convert matrices to long format data frames
df_logFC <- as.data.frame(as.table(logFC))
df_p_values <- as.data.frame(as.table(p_values))

# Rename columns for clarity
colnames(df_logFC) <- c("Gene", "Contrast", "logFC")
colnames(df_p_values) <- c("Gene", "Contrast", "p_value")


# Merge the two data frames by Gene and Contrast
df_plot <- merge(df_logFC, df_p_values, by = c("Gene", "Contrast"))


# Calculate -log10 of the p-values for the y-axis
df_plot$logp <- -log10(df_plot$p_value)
genes_to_highlight <- c("DMKN", "DSG1", "FLG2", "KRT10", "KRT14","ASPRV1", "KLK6","KLK7", "EGFR", "ITGA6","KRTDAP", "SBSN", "BLMH", "CDH1", "DSC1", "CTNND1", "CTNNB1")

for (contrast in unique(df_plot$Contrast)) {
    # Subset the data for the current contrast
    df_sub <- df_plot[df_plot$Contrast == contrast, ]
    
    # Create a new column for color based on logFC
    df_sub$color <- ifelse(df_sub$logp > pvalue_threshold & df_sub$logFC > logFC_threshold, "red", ifelse(df_sub$logp > pvalue_threshold & df_sub$logFC < -logFC_threshold, "blue", "grey"))
    
    # Create the volcano plot
    Volcano_p <- ggplot(df_sub, aes(x = logFC, y = logp, color = color)) +
        geom_point(alpha = 0.4, size = 1.75) +
        geom_hline(yintercept = pvalue_threshold, linetype = "dashed") +
        geom_vline(xintercept = c(-logFC_threshold, logFC_threshold), linetype = "dashed") +
        theme_minimal() +
        scale_color_identity() + 
        geom_label_repel(data = subset(df_sub, Gene %in% genes_to_highlight), aes(label = Gene), size = 3, color = "black",label.size = NA, fill = NA, segment.color = "black",segment.size = 0.5,box.padding = 1.5, fontface = "bold", nudge_x = c(-3,3)) +
        ggtitle(paste("Volcano plot for", contrast)) +
        xlab("Log2 fold change") +
        ylab("-Log10 p-value") +
        coord_cartesian(xlim = c(min(df_plot$logFC), max(df_plot$logFC)), ylim = c(0, max(df_plot$logp)))
    
    # Add the plot to the list
    volcano_plots[[contrast]] <- Volcano_p
}


```
# Extract sig Hits from LIMMA
```{r}
# Define the thresholds
pvalue_threshold <- -log10(0.05) # Adjust the p-value threshold as needed
logFC_threshold <- 0.58 # Adjust the log fold change threshold as needed

# Initialize lists to store the top candidates
top_sig_increase <- list()
top_sig_decrease <- list()

for (contrast in unique(df_plot$Contrast)) {
  # Subset the data for the current contrast
  df_sub <- df_plot[df_plot$Contrast == contrast, ]
  
  # Sort by logp value in descending order to get the most significant genes on top
  df_sub <- df_sub[order(-df_sub$logp),]
  
  # Extract top 20 genes with significant increase
  top_sig_increase[[contrast]] <- head(df_sub$Gene[df_sub$logp > pvalue_threshold & df_sub$logFC > logFC_threshold], 20)
  
  # Extract top 20 genes with significant decrease
  top_sig_decrease[[contrast]] <- head(df_sub$Gene[df_sub$logp > pvalue_threshold & df_sub$logFC < -logFC_threshold], 20)
}

# Now you have two lists: top_sig_increase and top_sig_decrease
# containing the top 20 candidates for each contrast


sig_increase <- list()
A <- list()

# Loop through each contrast
for (contrast in unique(df_plot$Contrast)) {
    # Subset the data for the current contrast
    df_sub <- df_plot[df_plot$Contrast == contrast, ]
    
    # Extract genes with significant increase and decrease
    sig_increase[[contrast]] <- df_sub$Gene[df_sub$logp > pvalue_threshold & df_sub$logFC > logFC_threshold]
    sig_decrease[[contrast]] <- df_sub$Gene[df_sub$logp > pvalue_threshold & df_sub$logFC < -logFC_threshold]
}


sig_increase <- lapply(sig_increase, as.character)

# Map gene symbols to Entrez IDs
sig_increase_entrez <- lapply(sig_increase, function(genes) {
  suppressWarnings(
    mapIds(org.Hs.eg.db,
           keys = genes,
           column = "ENTREZID",
           keytype = "SYMBOL",
           multiVals = "first")
  )
})


sig_decrease <- lapply(sig_decrease, as.character)

# Map gene symbols to Entrez IDs
sig_decrease_entrez <- lapply(sig_decrease, function(genes) {
  suppressWarnings(
    mapIds(org.Hs.eg.db,
           keys = genes,
           column = "ENTREZID",
           keytype = "SYMBOL",
           multiVals = "first")
  )
})
# Transform each character vector in the list and collapse into a comma-separated string
sig_increase_entrez_transformed <- lapply(sig_increase_entrez, function(x) {
  x <- gsub(",", " ", x)  # Replace commas with spaces
  x <- gsub(";", " ", x)  # Replace semicolons with spaces
  paste(x, collapse = ", ")  # Collapse the vector into a comma-separated string
})
# Convert the list to a data frame with 'Name' and 'Genes' columns
df_sig_increase <- data.frame(Name = names(sig_increase_entrez_transformed), 
                 Genes = sig_increase_entrez_transformed, 
                 stringsAsFactors = F)

# Write the DataFrame to a text file



# Transform each character vector in the list and collapse into a comma-separated string
sig_decrease_entrez_transformed <- lapply(sig_decrease_entrez, function(x) {
  x <- gsub(",", " ", x)  # Replace commas with spaces
  x <- gsub(";", " ", x)  # Replace semicolons with spaces
  paste(x, collapse = ", ")  # Collapse the vector into a comma-separated string
})

# Convert the list to a data frame with 'Name' and 'Genes' columns
df_sig_decrease <- data.frame(Name = names(sig_decrease_entrez_transformed), 
                 Genes = sig_decrease_entrez_transformed, 
                 stringsAsFactors = FALSE)


#Convert to excel
output_for_GO_increased = t(do.call(rbind, sig_increase))
output_for_GO_decreased = t(do.call(rbind, sig_decrease))

```


# Heatmap
```{r}
# Convert the data to a DGEList for use with edgeR/limma
df_V2 <- Proteome_protein_quant
df_V2 <- df_V2[complete.cases(df_V2[, grep("WT", colnames(df_V2))]), ]

df_V2 <- as.data.frame(df_V2)
df_V2 <- df_V2[!is.na(df_V2$PG.Genes), ]
names(df_V2) <- gsub(" ", ".", names(df_V2))
names(df_V2) <- gsub("/", ".", names(df_V2))
df_V2 = na.omit(df_V2)
#df_V2$unique_genes <- make.names(df_V2$PG.Genes, unique = TRUE)
#rownames(df_V2) <- df_V2$unique_genes

counts <- df_V2[, -(1:3)]
rownames(counts) <- make.unique(df_V2$PG.Genes)
#counts = log2(counts)
dge_v2 <- DGEList(counts = counts)

# Normalize the data
dge_v2 <- calcNormFactors(dge_v2)

# Design matrix
#group <- factor(gsub(\\s\\d+$, "", colnames(dge))) This is if I dont change the names 
# Define your factor
group_v2 <- factor(gsub("(\\.KO)?\\_\\d+$", "", colnames(dge_v2))) # This is if you change the naming above

# Create the design matrix
design_v2 <- model.matrix(~0 + group_v2)
colnames(design_v2) <- levels(group_v2)

# Estimate dispersion
dge_v2 <- estimateDisp(dge_v2, design_v2)
v_v2 <- voom(dge_v2, design_v2, plot=FALSE)

# Define contrasts
contrasts_v2 <- makeContrasts(
  BG_vs_WT = DMKN_BG_KO - WT,
  AB_vs_WT = DMKN_AB_KO - WT,
  levels = design
)

# Fit the model and perform the tests
fit_v2 <- lmFit(v_v2, design_v2)
fit2_v2  = contrasts.fit(fit_v2, contrasts_v2)
fit2_v2 <- eBayes(fit2_v2)

# Extract the p-values and log fold changes (contrasts) from your fit2 object
p_values_v2 <- fit2_v2$p.value
logFC_v2 <- fit2_v2$coefficients

# Get the top genes for each contrast
top_genes_v2 <- topTable(fit2_v2, adjust="BH")


# Create a Venn diagram showing numbers of genes significant in each comparison
#vennDiagram(results)

# Find the top 30 genes which vary between the three  targets in any way
#top_30_genes <- topTable(fit2_v2, number=30)


# Convert t-statistics to z-scores

significant_genes <- which(fit2_v2$F.p.value < 0.05)
fit2_significant <- fit2_v2[significant_genes, ]
z_scores <- zscoreT(fit2_significant$t, df=fit2_significant$df.residual)

# Get the gene names from z_scores
z_score_genes <- rownames(z_scores)

Proteome_protein_quant_V2_filtered <- Proteome_protein_quant[Proteome_protein_quant$PG.Genes %in% z_score_genes, ]
Proteome_protein_quant_V2_filtered = as.data.frame(Proteome_protein_quant_V2_filtered)
rownames(Proteome_protein_quant_V2_filtered) = Proteome_protein_quant_V2_filtered$PG.Genes
Proteome_protein_quant_V2_filtered = Proteome_protein_quant_V2_filtered[4:12]
original_colnames <- colnames(Proteome_protein_quant_V2_filtered)
Proteome_protein_quant_V2_filtered_zscore <-t(apply(Proteome_protein_quant_V2_filtered,1,scale))
colnames(Proteome_protein_quant_V2_filtered_zscore) <- original_colnames


annotation_colors = list(
  Condition = c("WT" = "blue", 
                "DMKN BG KO" = "green", 
                "DMKN AB KO" = "red"))
annotation_df <- data.frame(
  Condition = factor(rep(c("WT", "DMKN BG KO", "DMKN AB KO"), each = 3))
)
rownames(annotation_df) <- colnames(Proteome_protein_quant_V2_filtered_zscore)




#Extract cluster
heatmap_obj <- pheatmap(Proteome_protein_quant_V2_filtered_zscore, 
                        cluster_rows = TRUE, 
                        cluster_cols = FALSE, 
                        show_rownames = FALSE,
                        show_colnames = FALSE, 
                        legend = TRUE, 
                        legend_breaks = c(max(Proteome_protein_quant_V2_filtered_zscore), -2, -1, 0, 1, 2, 3),
                        legend_labels = c("Z-Score", "-2", "-1", "0", "1", "2", "3"),
                        clustering_method = "ward.D2",
                        angle_col = 45, 
                        fontsize = 10,
                        show_col_dendrogram = FALSE,
                        show_row_dendrogram = FALSE,
                        annotation_col = annotation_df,
                        annotation_colors = annotation_colors)

# Extract row clusters
row_clusters <- cutree(heatmap_obj$tree_row, k = 6)  # Replace 'number_of_clusters' with the actual number

# Create a list to store data frames for each cluster
cluster_tables <- list()

# Loop through each cluster and create a table
for (i in unique(row_clusters)) {
  cluster_tables[[paste0("Cluster_", i)]] <- Proteome_protein_quant_V2_filtered_zscore[row_clusters == i, ]
}

# Define the order of clusters based on your column names
ordered_cluster_names <- paste0("Cluster_", seq_len(max(row_clusters)))

# Define the order within each cluster
column_order <- c("WT_1", "WT_2", "WT_3", "DMKN_BG_KO_1", "DMKN_BG_KO_2", "DMKN_BG_KO_3", "DMKN_AB_KO_1", "DMKN_AB_KO_2", "DMKN_AB_KO_3")

# Print each cluster table in the specified order
for (cluster_name in ordered_cluster_names) {
  cat("\n", cluster_name, "\n")
  cluster_data <- cluster_tables[[paste0("Cluster_", which(ordered_cluster_names == cluster_name))]]
  ordered_data <- cluster_data[, column_order[column_order %in% colnames(cluster_data)]]
  print(ordered_data)
  pheatmap(ordered_data, cluster_cols = F)
}

library(openxlsx)

# Create a new workbook
wb <- createWorkbook()

# Add a worksheet
addWorksheet(wb, "Cluster Row Names")

# Initialize a list to store row names
row_names_list <- list()

# Loop through each cluster and collect row names
for (i in seq_along(ordered_cluster_names)) {
  cluster_name <- ordered_cluster_names[i]
  cluster_data <- cluster_tables[[paste0("Cluster_", which(ordered_cluster_names == cluster_name))]]
  row_names <- rownames(cluster_data)
  
  # Store row names in the list
  row_names_list[[paste0("Cluster ", i)]] <- row_names
}

# Find the maximum number of rows
max_rows <- max(sapply(row_names_list, length))

# Write row names to the worksheet
for (i in seq_along(row_names_list)) {
  col_name <- names(row_names_list)[i]
  writeData(wb, "Cluster Row Names", col_name, startCol = i, startRow = 1)
  writeData(wb, "Cluster Row Names", row_names_list[[i]], startCol = i, startRow = 2)
}

# Save the workbook

```

CoRRPLOT
###CorrPlot
Quality control 1. Corrplot phos 2. Corrplot proteome
```{r}

# Read the data
sampleCorrMatrix_global_SN_3D <- read.delim2("sampleCorrelationMatrix_3DProteome.tsv")

# Define the names map
names_map_global <- c(
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_WT_1_1.raw" = "WT_Rep1",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_WT_2_1.raw" = "WT_Rep2",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_WT_3_1.raw" = "WT_Rep3",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_B11_1_1.raw" = "DTU_Rep1",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_B11_2_1.raw" = "DTU_Rep2",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_B11_3_1.raw" = "DTU_Rep3",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_D2_1_1.raw" = "CS_Rep1",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_D2_2_1.raw" = "CS_Rep2",
  "X20220201_MK_Evo_FAIMS_VC_3CV_DIA_global_D2_3_1.raw" = "CS_Rep3"
)

# Rename the columns
colnames(sampleCorrMatrix_global_SN_3D) <- names_map_global[colnames(sampleCorrMatrix_global_SN_3D)]
sampleCorrMatrix_global_SN_3D <- sampleCorrMatrix_global_SN_3D[,-1]

# Convert the character matrix to a numeric matrix
sampleCorrMatrix_global_SN_numeric <- apply(sampleCorrMatrix_global_SN_3D, 2, as.numeric)

# Check the structure of the new matrix
str(sampleCorrMatrix_global_SN_numeric)

# If it's now a numeric matrix, you can plot it with corrplot
if (is.numeric(sampleCorrMatrix_global_SN_numeric)) {
  corrplot(sampleCorrMatrix_global_SN_numeric, method = "color")
}

col <- colorRampPalette(c(rgb(0,0,1, alpha=0.5), rgb(1,0,0, alpha=0.5)))(200)
rownames(sampleCorrMatrix_global_SN_numeric) <- colnames(sampleCorrMatrix_global_SN_numeric)
smooth_colors <- colorRampPalette(c("lightcoral", "white", "red"))(200)

```


